\subsection[Adept]{The Adept}
\label{sec:Adept}
\begin{quote}
\emph{``Here, here. Bring me your hand. I can tell much about a person from the lines in their palms.}
-Amma, human Adept
\end{quote}

Although less powerful than a Cleric, Sorcerer, or Wizard, an Adept nevertheless possesses enough knowledge and magical ability to take up the role of the quintessential shaman, wise woman, or witch in small settlements or among primitive cultures.
\paragraph{Hit Die:} d6
\paragraph{Class skills:}
The adept's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Handle Animal (Cha), Heal (Wis), Knowledge (all skills, taken individually) (Int), Profession (Wis), Spellcraft (Int), and Survival (Wis).

\paragraph{Skill Points at 1st Level:} (4 + Int modifier) $\times$ 4.
\paragraph{Skill Points at each additional Level:} 4 + Int modifier.
\begin{table*}
\caption{The Adept}
\label{tab:Adept}
%\rowcolors{1}{white}{lightgray}
\makebox[\textwidth]{
\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Level}}&\multirow{2}{*}{\textbf{BAB}}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\multirow{2}{*}{\textbf{Special}}&\multirow{2}{*}{\textbf{SP/day}}&\textbf{Spells}&\textbf{Max}\\
&&\textbf{save}&\textbf{save}&\textbf{save}&&&\textbf{known}&\textbf{level}\\
\hline
1st &+0			&+0 &+0 &+2	&-		&0 &1&1st\\
2nd &+1 		&+0 &+0 &+3 	&Familiar	&1 &2 &1st\\
3rd &+1 		&+1 &+1 &+3 	&-		&3 &3 &1st\\
4th &+2 		&+1 &+1 &+4 	&-		&5 &4 &1st\\
5th &+2 		&+1 &+1 &+4 	&-		&7 &5 &2nd\\
6th &+3 		&+2 &+2 &+5 	&-		&11 &6 &2nd\\
7th &+3 		&+2 &+2 &+5 	&-		&15 &7 &2nd\\
8th &+4 		&+2 &+2 &+6 	&-		&19 &8 &2nd\\
9th &+4 		&+3 &+3 &+6 	&-		&23 &9 &3rd\\
10th &+5		&+3 &+3 &+7 	&-		&27 &10 &3rd\\
11th &+5		&+3 &+3 &+7 	&-		&35 &11 &3rd\\
12th &+6/+1		&+4 &+4 &+8 	&-		&43 &12 &3rd\\
13th &+6/+1		&+4 &+4 &+8 	&-		&51 &13 &4th\\
14th &+7/+2		&+4 &+4 &+9 	&-		&59 &14 &4th\\
15th &+7/+2		&+5 &+5 &+9 	&-		&67 &15 &4th\\
16th &+8/+3		&+5 &+5 &+10 	&-		&79 &16 &4th\\
17th &+8/+3		&+5 &+5 &+10 	&-		&91 &17 &5th\\
18th &+9/+4		&+6 &+6 &+11 	&-		&103 &18 &5th\\
19th &+9/+4		&+6 &+6 &+11 	&-		&115 &19 &5th\\
20th &+10/+5		&+6 &+6 &+12 	&-		&127 &20 &5th\\
\hline
\end{tabular}}
\end{table*}
\subsubsection{Class Features}
All the following are class features of the Adept.

\paragraph{Weapon and Armor Proficiency:} 
Adepts are proficient with all simple weapons. Adepts are not proficient with any type of armor nor with shields.

\paragraph{Spell Points/Day:} An Adept's ability to cast spells is limited by the spell points he has available. 
His base daily allotment of spell points is given on \nameref{tab:Adept} table. 
In addition, he receives bonus spell points per day if he has a high Wisdom score.
His race may also provide bonus spell points per day, as may certain feats and items.

\paragraph{Spells Known:} An Adept begins play knowing one Adept spell of your choice. 
Each time he achieves a new level, he unlocks the knowledge of a new spell.
Choose the spells known from the Adept spell list (Exception: The feats Expanded Knowledge and Epic Expanded Knowledge do allow an Adept to learn spells of other classes, even specialist Wizard spells.).
An Adept can cast any spell he knows that has a spell point cost equal to or lower than his caster level.
The number of times an Adept can cast spells in a day is limited only by his daily spell points. 
An Adept simply knows his spells; they are ingrained in his mind, though he must get a good night's sleep each day to regain all his spent spell points.
The Difficulty Class for saving throws against Adept spells is 10 + one-half the number of spell points spent on the spell (round up) + the Adept's Wisdom modifier. 

Spells learned via the Adept class are divine spells.
\paragraph{Maximum Spell Level Known:} An Adept begins play with the ability to learn 1st-level spells. 
As he attains higher levels, an Adept may gain the ability to master more complex spells, as shown on the \nameref{tab:Adept} table.
To learn or cast a spell, an Adept must have a Wisdom score of at least 10 + the spell's level.

\paragraph{Familiar:}
At second level, an Adept gains the \nameref{Feat:Familiar} feat as a bonus feat, if he qualifies for it.
If he does not qualify at second level but does at a later point, he immediately gains it at that point.

\subsubsection{Adept Spell List}
\paragraph{1st-Level Adept Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item \nameref{Spell:Bless}: Allies gain +1 on attack rolls and +1 on saves against fear.
\item \nameref{Spell:Command}: One subject obeys selected command for 1 round.
\item \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
\item \nameref{Spell:Chiromancy}*: Determine mundane facts about subject's future by studying its palm.
\item \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item \nameref{Spell:Fog}: Fog surrounds you.
\item \nameref{Spell:ShockingGrasp}: Touch delivers 1d6 energy damage.
\item \nameref{Spell:DetectMagic}: Reveals the presence, strength, and school of magical auras.
\item \nameref{Spell:Fear}: One creature flees for 1d4 rounds.
\item \nameref{Spell:Light}: Causes object to shine like a torch.
\item \nameref{Spell:Repair}: Makes repairs on an object or construct.
\item \nameref{Spell:ScorchingRay}: Deal 1d6 energy damage with a ranged touch attack.
\item \nameref{Spell:Sleep}: Puts 4 HD of creatures into magical slumber.
\item \nameref{Spell:TouchOfFatigue}: Touch fatigues subject.
\item \nameref{Spell:Ventriloquism}: Makes sounds appear out of nowhere.
\end{list}
\paragraph{2nd-Level Adept Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Aid}: +1 on attack rolls, +1 on saves against fear, 1d8 temporary hp +1/level.
\item \nameref{Spell:Antipoison}: Stops poison from harming subject for 1 hour/level.
\item \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
\item \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
\item \nameref{Spell:FormScout}: Subject gains the form of a nimble creature.
\item \nameref{Spell:MirrorImage}: Creates decoy duplicates of you.
\item \nameref{Spell:Pattern}: Twisting colors fascinate creatures.
\item \nameref{Spell:SeeInvisibility}: Reveals invisible creatures or objects.
\item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item \nameref{Spell:Restoration}: Dispels magical ability penalty or repairs 1d4 ability damage.
\item \nameref{Spell:Web}: Creates sticky spiderwebs between two anchor points.
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\paragraph{3rd-Level Adept Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:AnimateDead}: Creates undead skeletons and zombies.
 \item \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
 \item \nameref{Spell:Contagion}: Infects subject with chosen disease. %Instead of Remove Disease
 \item \nameref{Spell:FormAvian}: Subject gains the form of a bird.
 \item \nameref{Spell:FormFish}: Subject gains the form of a water-dwelling creature.
 \item \nameref{Spell:LightningBolt}: Deal 3d6 energy damage in a line.
 \item \nameref{Spell:Medium}*: You transform yourself into a conduit to communicate with a deceased individual.
 \item \nameref{Spell:RemoveCurse}: Frees object or person from curse.
 \item \nameref{Spell:RemoveDisease}: Cures all diseases affecting subject.
\end{list}
\paragraph{4th-Level Adept Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:FormVermin}: Subject gains the form of a vermin.
 \item \nameref{Spell:FormViper}: Subject gains the form of a snake.
 \item \nameref{Spell:MatterCreation}: Creates one cloth or wood object.
 \item \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
 \item \nameref{Spell:WallOfFire}: Deals 2d4 fire damage out to 10 ft. Passing through wall deals 7d6 damage.
\end{list}
\paragraph{5th-Level Adept Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:BalefulPolymorph}: Transforms subject into harmless animal.
 \item \nameref{Spell:Commune}: Deity answers three yes-or-no questions.
 \item \nameref{Spell:FormCarnivore}: Subject gains the form of a dangerous beast.
 \item \nameref{Spell:FormTreant}: Subject gains the form of a plant creature.
 \item \nameref{Spell:Heal}: Cures great amounts of of damage, all diseases and mental conditions.
 \item \nameref{Spell:RaiseDead}: Brings a creature back from the dead.
 \item \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
 \item \nameref{Spell:WallOfStone}: Creates a stone wall that can be shaped.
\end{list}

\subsubsection{Chiromancy}
\label{Spell:Chiromancy}
Divination
\\ \textbf{Level:} Adept 1
\\ \textbf{Components:} V, S
\\ \textbf{Casting Time:} 10 minutes
\\ \textbf{Range:} Touch
\\ \textbf{Target:} One willing humanoid, with one or more hands
\\ \textbf{Duration:} Instantaneous
\\ \textbf{Saving Throw:} Will negates (harmless)
\\ \textbf{Spell Resistance:} Yes (harmless)
\\ \textbf{Spell Points:} 1

\emph{By studying the lines in the subject's hand, you gain an insight into the future.}

You receive an answer to one or more (as desired) of the following questions:
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item The number of children the subject will have (including current children)
 \item The number of marriages the subject will have in its lifetime
 \item Whether the subject's relationship status will change in the next year
 \item Whether the subject will undertake a major journey in the next year, and whether the journey will result in a benefit, danger, disappointment, and/or loss
 \item Whether the subject's lifestyle will change greatly in the next year
 \item Whether the subject will die of natural causes
 \item Whether the subject will assume a position of great power in the next year
 \item Whether the subject will witness death in the next year
\end{list}
All of these questions are answered by the GM, as deemed most probable at the time of casting. Subsequent castings will return the same results, unless something happens between the castings that changes the most probable outcome.

\subsubsection{Medium}
\label{Spell:Medium}
Necromancy
\\ \textbf{Level:} Adept 3
\\ \textbf{Components:} V, S
\\ \textbf{Casting Time:} 10 minutes
\\ \textbf{Range:} Personal
\\ \textbf{Target:} You
\\ \textbf{Duration:} 1 min./level (D)
\\ \textbf{Spell points:} 5

\emph{The voice of the witch suddenly changes.}

By casting this spell, you reach out to the soul of a creature who has been dead for at least 26 weeks in an attempt to communicate with it.
You must be able to unambiguously identify the creature. If the creature is correctly identified, the chance of successfully establishing contact is 70\% + 1\% per caster level. In addition, the creature knows your name, alignment, and a message chosen by you (length up to 10 words), and may refuse to communicate based on that information. If contact is not established, the spell fails. 

If the contact is successful, you effectively allow the creature to possess your body for the duration of the spell. However, the only action it can take is to speak. The only action you can take for the spell's duration is to dismiss the spell. Although you can not speak yourself, you maintain awareness and memory throughout the duration.

The contacted creature possesses all knowledge it did in life, but will speak of its current situation in only the vaguest terms. If at any point the contacted creature wishes to break off the communication, it can do so immediately.

\paragraph{Augment:} For every additional spell point you spend, you can contact a creature that has been dead for one week less, to a minimum of one week.