\subsection{Arcane Archer}
\begin{quote}
\emph{``P'TwAnG!''}
- Sambo, drow Arcane Archer
\end{quote}
An Arcane Archer is an elf who has learned to combine two of the iconic elven disciplines - archery and arcane magic.
\paragraph{Hit Die:} d8
\paragraph{Requirements:}
To qualify to become an Arcane Archer, a character must fulfill all the following criteria.
\subparagraph{Race:}
Elf or half-elf.
\subparagraph{Feats:}
Point Blank Shot, Precise Shot, Weapon Focus (longbow or shortbow).
\subparagraph{Spells:}
Ability to cast \nameref{Spell:MagicWeapon} as an Arcane Spell.
\subparagraph{Special:}
Base Attack Bonus +6 OR Knowledge (arcana) 9 ranks.
\paragraph{Class Skills}
The Arcane Archer's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Escape Artist (Dex), Hide (Dex), Jump (Str), Knowledge (arcana) (Int), Listen (Wis), Move Silently (Dex), Ride (Dex), Spot (Wis), Survival (Wis), and Use Rope (Dex).
\paragraph{Skill Points at Each Level}
4 + Int modifier.

\begin{table*}
\centering
\caption{The Arcane Archer}
\label{tab:ArcaneArcher}
\makebox[\textwidth]{
\begin{tabular}{|l|l|c|c|c|l|l|}
\hline
\multirow{2}{*}{\textbf{Level}}&\multirow{2}{*}{\textbf{BAB}}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\multirow{2}{*}{\textbf{Special}}&\textbf{Spell points/day and}\\
&&\textbf{save}&\textbf{save}&\textbf{save}&&\textbf{max spell level}\\
\hline
1st	&+1	&+2	&+2	&+0	&Magic Arrows				&+1 level of existing class\\
2nd	&+2	&+3	&+3	&+0	&Advanced Learning, Imbue Arrow		&+1 level of existing class\\
3rd	&+3	&+3	&+3	&+1	&Enhance Arrows (Energy)		&+1 level of existing class\\
4th	&+4	&+4	&+4	&+1	&Advanced Learning			&+1 level of existing class\\
5th	&+5	&+4	&+4	&+1	&Enhance Arrows (Distance)		&+1 level of existing class\\
6th	&+6	&+5	&+5	&+2	&Advanced Learning			&+1 level of existing class\\
7th	&+7	&+5	&+5	&+2	&Enhance Arrows (Elemental Burst)	&+1 level of existing class\\
8th	&+8	&+6	&+6	&+2	&Advanced Learning			&+1 level of existing class\\
9th	&+9	&+6	&+6	&+3	&Enhance Arrows (Aligned)		&+1 level of existing class\\
10th	&+10	&+7	&+7	&+3	&Advanced Learning			&+1 level of existing class\\
\hline
\end{tabular}
}
\end{table*}

\subsubsection{Class Features}
All the following are Class Features of the Arcane Archer prestige class.

\paragraph{Weapon and Armor Proficiency:} Arcane Archers gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} When a new Arcane Archer level is gained, the character gains spell points per day, and an increase in caster level and maximum available spell level as if he had also gained a level in whatever arcane spellcasting class in which he could cast the \nameref{Spell:MagicWeapon} spell before he added the prestige class level. 
He does not, however, gain any other benefit a character of that class would have gained, nor does he gain spells known (but see the Advanced Learning class feature, below). 
If a character had more than one arcane spellcasting class in which he could cast \nameref{Spell:MagicWeapon} before he became a Arcane Archer, he must decide to which class he adds each level of Arcane Archer for the purpose of determining what spellcasting class gains the benefit of the spellcasting advancement.

\paragraph{Magic Arrows (Su):}
An arcane Archer never wants for arrows.
By making the motion of drawing a bowstring, an Arcane Archer can create a temporary arrow of pure magic.
These Magic Arrows cannot be stored or removed from the bow, they last only from the time the bow is drawn and until it is fired.
Magic Arrows bypass DR/magic, even if the bow does not have an enhancement bonus.
They otherwise function as normal arrows.

\paragraph{Advanced Learning:}
At 2nd level, and again at Arcane Archer levels 4th, 6th, 8th, and 10th, the Arcane Archer gains a bonus spell known, chosen from the following list: \nameref{Spell:ArrowOfDeath}, \nameref{Spell:BloodlettingArrow}, \nameref{Spell:HailOfArrows}, \nameref{Spell:ParalyzingArrow}, \nameref{Spell:PhaseArrow}, \nameref{Spell:SeekerArrow}, and \nameref{Spell:StunningArrow}.

When so learned, he adds the spell to his list of spells known from whatever arcane spellcasting class in which he could cast the \nameref{Spell:MagicWeapon} spell before he added the prestige class level. If more than one arcane spellcasting class would qualify, choose one. He must be able to cast spells of the appropriate level in the class before adding the spell. If he qualifies for none of the listed spells, he gains one immediately if he qualifies at some point in the future.

\paragraph{Imbue Arrow (Su):}
At 2nd level, an Arcane Archer gains the ability to place an area spell upon an arrow.
The spell may not have a casting time longer than one standard action, and may be of a level no higher than your Arcane Archer class level -1.
When the arrow is fired, the spell's area is centered on where the arrow lands, even if the spell could normally be centered only on the caster. If the arrow misses its intended target, the spell still goes off. Treat the arrow as a splash weapon that missed when determining the center of the spell's effect in such a case.

It takes a standard action to cast the spell and fire the arrow. 
The arrow must be fired in the round the spell is cast, or the spell is wasted.
Effects that allow you to fire more than one arrow as part of a single standard action work as normal, but only one of the arrows fired carries the spell, not all of them.
\paragraph{Enhance Arrows (Su):}
At 3rd level, every arrow fired by an Arcane Archer gains one of the following elemental themed weapon qualities: \emph{flaming}, \emph{frost}, or \emph{shock}. Unlike magic weapons created by normal means, the archer need not spend gold pieces to accomplish this task. However, an archer's magic arrows only function for him.

At 5th level, every arrow fired by an Arcane Archer gains the \emph{distance} weapon quality.

At 7th level, every arrow fired by an Arcane Archer gains one of the following elemental burst weapon qualities: \emph{flaming burst}, \emph{icy burst}, or \emph{shocking burst}. This ability replaces the ability gained at 3rd level.

At 9th level, every arrow fired by an Arcane Archer gains one of the following aligned weapon qualities: \emph{anarchic}, \emph{axiomatic}, \emph{holy} or \emph{unholy}. The Arcane Archer cannot choose an ability that is the opposite of his alignment (for example, a lawful good Arcane Archer could not choose anarchic or unholy as his weapon quality).

The bonuses granted by a magic bow (or magic arrows) apply as normal to arrows that have been enhanced with this ability. Duplicate abilities do not stack.





