\subsection{Archmage}
\begin{quote}
\emph{I have survived many adventures, but my ongoing study of magic is truly the greatest of them all.}
- Thelonius, elven Archmage
\end{quote}
An Archmage is a powerful spellcaster who has begun to delve into the most fundamental workings of magic.
\paragraph{Hit Die:} d4
\paragraph{Requirements:}
To qualify to become an Archmage, a character must fulfill all the following criteria.
\subparagraph{Skills:} Knowledge (arcana) 15 ranks, Spellcraft 15 ranks.
\subparagraph{Feats:} Magical Endowment, Expanded Knowledge, Skill Focus (Spellcraft).
\subparagraph{Spells:} Ability to cast 7th-level arcane spells, knowledge of 4th-level or higher spells from at least five schools.
\paragraph{Class Skills}
The Archmage's class skills (and the key ability for each skill) are Concentration (Con), Craft (alchemy) (Int), 
Intimidate (Cha), Knowledge (all skills taken individually) (Int), Profession (Wis), Search (Int), and Spellcraft (Int). 
\paragraph{Skill Points at each level:} 2 + Int modifier.
\begin{table*}
\centering
\caption{The Archmage}
\label{tab:Archmage}
\makebox[\textwidth]{
%\makebox[\textwidth]{\resizebox{1.2\textwidth}{!}{
\begin{tabular}{|l|l|c|c|c|c|l|}
\hline
\textbf{Level}&\textbf{BAB}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\textbf{Special}&\textbf{Spellcasting}\\
\hline
1st	&+0	&+0	&+0	&+2	&High Arcana	&+1 level of existing class\\
2nd	&+1	&+0	&+0	&+3	&High Arcana	&+1 level of existing class\\
3rd	&+1	&+1	&+1	&+3	&High Arcana	&+1 level of existing class\\
4th	&+2	&+1	&+1	&+4	&High Arcana	&+1 level of existing class\\
5th	&+2	&+1	&+1	&+4	&High Arcana	&+1 level of existing class\\
\hline
\end{tabular}
%}}
}
\end{table*}
\subsubsection{Class Features}
All the following are Class Features of the Archmage prestige class.

\paragraph{Weapon and Armor Proficiency:} Archmages gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} When a new Archmage level is gained, 
the character gains spell points per day, an increase in caster level, spells known and maximum available spell level
as if he had also gained a level in whatever arcane spellcasting class in which he could cast 7th-level spells before he added the prestige class level. 
He does not, however, gain any other benefit a character of that class would have gained. 
If a character had more than one arcane spellcasting class in which he could cast 7th-level spells before he became an Archmage, 
he must decide to which class he adds each level of Archmage for the purpose of determining what spellcasting class gains the benefit of the spellcasting advancement.

\paragraph{High Arcana:}
An Archmage gains the opportunity to select a special ability from among those described below by permanently eliminating a specific number of Spell Points.
These spell points are subtracted from the final number of spell points he Archmage would otherwise have.
Effectively, these spell points are spent on ``fueling'' the High Arcana.
When a High Arcana refers to an Archmage's ``caster level'', it means his highest caster level.

\subparagraph{Arcane Fire (Su):}
As a standard action, an Archmage may expend his magical focus to manifest a bolt of raw magical energy. 
The bolt is a ranged touch attack with long range (400 feet + 40 feet/caster level of the Archmage) 
that deals 1d6 points of damage per caster level of the Archmage, with no saving throw. 
Learning this High Arcana removes 15 spell points from the Archmage's pool.

\subparagraph{Arcane Reach (Su):}
The Archmage can use spells with a range of touch on a target up to 30 feet away. 
In the case of a spell that would ordinarily require a touch attack, the Archmage must make a ranged touch attack instead.
Arcane reach can be selected a second time as a High Arcana (paying the cost again), in which case the range increases to 60 feet. 
Learning this High Arcana removes 13 spell points from the Archmage's pool.

\subparagraph{Mastery of Counterspelling (Ex):}
When the Archmage counterspells a spell, it is turned back upon the caster as if it were fully affected by a \nameref{Spell:SpellTurning} spell. 
If the spell cannot be affected by spell turning, then it is merely counterspelled. 
Learning this High Arcana removes 13 spell points from the Archmage's pool.

\subparagraph{Mastery of Elements:}
The Archmage can alter an arcane spell when cast so that it utilizes a different element from the one it normally uses, 
even if the spell normally does not allow more than one element to be selected. 
This ability can only alter a spell with the acid, cold, fire, electricity, or sonic descriptor. 
All characteristics of the spell, except for its energy type descriptor and damage type remain unchanged.
The caster decides whether to alter the spell's energy type and chooses the new energy type when he begins casting. 
Learning this High Arcana removes 3 spell points from the Archmage's pool.

\subparagraph{Mastery of Shaping:}
The Archmage can alter area and effect spells that use one of the following shapes: burst, cone, cylinder, emanation, or spread. 
The alteration consists of creating spaces within the spell's area or effect that are not subject to the spell.
The minimum dimension for these spaces is a 5-foot cube. Furthermore, any shapeable spells have a minimum dimension of 5 feet instead of 10 feet. 
Learning this High Arcana removes 11 spell points from the Archmage's pool.

\subparagraph{Spell Power:}
This ability provides the Archmage with a +1 inherent bonus to one of his mental ability scores. 
Spell Power can be selected more than once as a High Arcana (paying the cost each time). 
Each additional time it is selected, he gains a +1 inherent bonus to another mental ability score, or one of his existing inherent bonuses to a mental ability score increases by one.
However, an inherent bonus may not exceed +5 for a single ability score.
Learning this High Arcana removes 9 spell points from the Archmage's pool.

\subparagraph{Spell-Like Ability (Sp):}
An Archmage who selects this High Arcana can use one of his spells known as a spell-like ability twice per day.
The caster level for this spell-like ability is equal to the Archmage's hit dice.
The activation of the spell-like ability requires the same action as casting the spell itself.
If this High Arcana is selected more than once, it can apply to the same spell chosen the first time (increasing the number of times per day it can be used) or to a different spell.
Learning this High Arcana removes a number of spell points equal to the minimum amount required to cast the spell in question from the Archmage's pool.