\subsection{Blackguard}
\label{sec:Blackguard}
\begin{quote}
\emph{I was once like you. So full of hope. But the world doesn't reward hope, pup.}
- Torgar, human Blackguard
\end{quote}
A Blackguard is usually a Paladin who has not only fallen from grace, but become what he once fought. Whether they made a conscious choice to turn from the path of good or were slowly corrupted, Blackguards are some of the most vile foes a mortal will face.
\paragraph{Hit Die:} d10
\paragraph{Requirements:}
To qualify to become a Blackguard, a character must fulfill all the following criteria.
\subparagraph{Alignment:} Any evil.
\subparagraph{Base Attack Bonus:} +6
\subparagraph{Skills:} Intimidate 9 ranks, Knowledge (religion) 2 ranks.
\subparagraph{Feat:} Power Attack
\paragraph{Class Skills}
The Blackguard's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Disguise (Cha), Forgery (Cha), Gather Information (Cha), Intimidate (Cha), Hide (Dex), Knowledge (Arcana) (Int), Knowledge (local) (Int), Knowledge (religion) (Int), Knowledge (the planes) (Int), Move Silently (Dex), Profession (Wis), Ride (Dex), Sense Motive (Wis), and Spellcraft (Int).

\paragraph{Skill Points at each additional Level:} 4 + Int modifier. 
\begin{table*}
\centering
\caption{The Blackguard}
\label{tab:Blackguard}
\makebox[\textwidth]{
\begin{tabular}{|l|l|c|c|c|l|l|}
\hline
\textbf{Level}&\textbf{BAB}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\textbf{Special}&\textbf{Spellcasting}\\
\hline
1st	&+1	&+2	&+0	&+0	&Aura of Evil, Dark Blessing	&+1 level of Paladin\\
2nd	&+2	&+3	&+0	&+0	&Unholy Gift			&+1 level of Paladin\\
3rd	&+3	&+3	&+1	&+1	&				&+1 level of Paladin\\
4th	&+4	&+4	&+1	&+1	&				&+1 level of Paladin\\
5th	&+5	&+4	&+1	&+1	&Unholy Gift			&+1 level of Paladin\\
6th	&+6	&+5	&+2	&+2	&				&+1 level of Paladin\\
7th	&+7	&+5	&+2	&+2	&				&+1 level of Paladin\\
8th	&+8	&+6	&+2	&+2	&Unholy Gift			&+1 level of Paladin\\
9th	&+9	&+6	&+3	&+3	&				&+1 level of Paladin\\
10th	&+10	&+7	&+3	&+3	&				&+1 level of Paladin\\
11th	&+11	&+7	&+3	&+3	&Unholy Gift			&+1 level of Paladin\\
12th	&+12	&+8	&+4	&+4	&				&+1 level of Paladin\\
13th	&+13	&+8	&+4	&+4	&				&+1 level of Paladin\\
14th	&+14	&+9	&+4	&+4	&Unholy Gift			&+1 level of Paladin\\
\hline
\end{tabular}
}
\end{table*}
\subsubsection{Class Features}
All the following are Class Features of the Blackguard prestige class.

\paragraph{Weapon and Armor Proficiency:} Blackguards are proficient with all simple and martial weapons, with all types of armor, and with shields.

\paragraph{Spellcasting:} When a new Blackguard level is gained, the character gains spell points per day, an increase in caster level, spells known and maximum available spell level as if he had also gained a level in the Paladin class. However, instead of using the Paladin spell list, a Blackguard uses the Blackguard spell list, and does not receive the \nameref{Spell:TouchOfVitality} spell as a bonus spell known. A character with no Paladin levels starts gaining spellcasting as a 1st level Paladin (but again, using the Blackguard spell list, and without the \nameref{Spell:TouchOfVitality} spell as a bonus spell known). See also the \nameref{sec:DarkBlessing} class feature, below.

\paragraph[Aura of Evil]{Aura of Evil: (Su)}
\label{sec:AuroOfEvil} 
At will, as a free action, a Blackguard can project an unholy aura.
While the aura is active, the Blackguard gains a +4 profane bonus on Intimidate checks, and a -4 penalty on Diplomacy checks.
All sapient creatures become instinctively aware of the Blackguard's evil alignment while the aura is active.
The Blackguard can project this aura indefinitely, or until he dismisses it (another free action). 

\paragraph[Dark Blessing]{Dark Blessing (Su):} 
\label{sec:DarkBlessing}
The alignment requirements of the Blackguard class are incompatible with those of the Paladin class, requiring a Paladin entrant to become an Ex-Paladin. However, the malignant powers that support Blackguards are fully capable of restoring a fallen Paladin's prowess. This has the following consequences:
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item All spells a Paladin entrant knows as a Paladin must be switched out for Blackguard spells of the same level, except for those spells that appear on both the Paladin and Blackguard lists. The \nameref{Spell:TouchOfVitality} spell is lost, with no replacement.
 \item All Holy Gifts other than Additional Feats selected by a Paladin entrant must be switched out for Unholy Gifts (see below).
 \item A Paladin entrant's Smite and Divine Grace abilities are re-activated, using a sum of the character's Blackguard and Ex-Paladin levels to calculate the appropriate bonuses. A Blackguard's Divine Grace is usually referred to as Dark Grace.
\end{list}

\paragraph[Unholy Gift]{Unholy Gift:}
\label{sec:UnholyGift}
At 2nd level, and at every third level beyond that (5th, 8th, 11th, and 14th), the dark powers the Blackguard serves reward him with a gift of new abilities. Unless otherwise noted, a gift can only be selected once. Some gifts have specific prerequisites.

\subparagraph{Additional Feat:}
You gain a bonus feat from the list of feats noted as Fighter bonus feats.
This gift may be selected more than once.

\subparagraph{Aura of Despair (Su):}
A Blackguard with this gift radiates a malign aura that causes enemies within 10 feet of him to take a -2 penalty on all saving throws. This is a supernatural ability that functions continuously. You must be a 2nd-level Blackguard to select this gift.

\subparagraph{Brutal Smite (Su):}
Your contempt toward the weak augments your smites against them with dark power, making them especially horrifying.
When you perform a smite attack against a good creature, it must succeed on a Fortitude save (DC 10 + $1/2$ your HD + your Charisma modifier) or be \emph{nauseated} by pain for 1 round. You must have the \nameref{sec:Smite} ability and be a 2nd-level Blackguard to select this gift.

\subparagraph{Fiendish Mount}
\label{sec:FiendishMountListing}
You gain the service of a hellish animal. See the \nameref{sec:FiendishMount} creature description. You must be a 5th-level Blackguard to select this gift. If you have the \nameref{Feat:AnimalCompanion} feat, \nameref{sec:CelestialMountListing} ability, the \nameref{Feat:Familiar} feat, or the \nameref{Feat:SpellstaffUser} feat, you may not select this gift.

\subparagraph{Frightful Presence (Ex):}
The very presence of a Blackguard with this gift is unsettling to his foes. 
It takes effect automatically when you charge, make a full attack, or cast a spell. 
Opponents within 30 feet who witness the action are \emph{shaken} for 1 minute.
This ability affects only opponents with fewer Hit Dice or levels than you have. 
An affected opponent can resist the effects with a successful Will save (DC 10 + $1/2$ your HD + your Charisma modifier). 
An opponent that succeeds on the saving throw is immune to your frightful presence for 24 hours.

\subparagraph{Master of Fear (Su):}
A Blackguard with this gift is a master in every form of intimidation, capable of shaking even creatures to whom the feeling is alien. Your Fear spells and demoralize attempts can affect creatures normally immune to fear. The creatures' other defenses (such as saving throws) work normally. This is a supernatural ability activated as part of the activity in question.
You must be a 5th-level Blackguard to select this gift.

\subparagraph{No Mercy (Ex):}
You know how to strike when your opponent is at his most vulnerable. You may add your sneak attack damage when attacking a target that is \emph{prone}, even if the attack would not otherwise qualify for sneak attack. You must have the sneak attack ability to select this gift.

\subparagraph{Pale Knight (Ex):}
Though associating with the forces of darkness has taken a toll on your body, it has numbed you to some of their most debilitating attacks. A Blackguard with this gift gains immunity to energy drain and negative levels. 

\subparagraph{Poison Use (Ex):}
A Blackguard with this gift never risks accidentally poisoning himself when applying poison to a weapon or using a poisoned weapon.

\subparagraph{Sneak Attack:}
This gift functions as the Rogue class feature of the same name. 
The extra damage is +2d6. 
This qualifies as the Sneak Attack class feature for the purposes of meeting prerequisites.
If a Blackguard gets a sneak attack bonus from another source, the bonuses on damage stack.
This gift may be selected a total number of times equal to your character level divided by four, increasing the damage by +2d6 each additional time it is taken.

\subparagraph{Unholy Toughness (Ex):}
Being constantly suffused with dark energies has forced your body to develop unusual resilience. You gain damage reduction equal to one-half your Blackguard level, minimum 1 (if you have Ex-Paladin levels, use the sum of your Blackguard levels and Ex-Paladin levels instead). This damage reduction is overcome by good-aligned weapons.

\subsubsection{Ex-Blackguards:}
A Blackguard who changes to a nonevil alignment cannot advance further as a Blackguard, although he retains all Blackguard class features.

\subsubsection{Blackguard Spell List}
\label{sec:BlackguardSpellList}
\paragraph{1st-Level Blackguard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item \nameref{Spell:Bane}: Enemies take -1 on attack rolls and saves against fear.% Instead of Bless
\item \nameref{Spell:Blackfire}*: Fires shed light for you only. %Instead of Zone of Truth
\item \nameref{Spell:CorruptWeapon}: Weapon bypasses the defenses of good foes. % Instead of Bless Weapon
\item \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item \nameref{Spell:CursedBlade}*: Wounds caused by weapon refuse to heal. %Instead of Armaments of Faith
\item \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item \nameref{Spell:DetectUndead}: Reveals the presence and strength and of undead creatures.
\item \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item \nameref{Spell:DivineFavor}: You gain a luck bonus on attack and damage rolls.
\item \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item \nameref{Spell:Fear}: One creature flees for 1d4 rounds. %Instead of Remove Fear
\item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
\item \nameref{Spell:UncannyAccuracy}*: Your underhanded attacks are surprisingly effective. %Instead of True Strike
\item \nameref{Spell:SummonWeapon}*: Summons bonded weapon to your hand.
\item \nameref{Spell:SurgeOfStrength}*: Gain temporary strength and hit points.
\end{list}
\paragraph{2nd-Level Blackguard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlignWater}*: Vial of water is imbued with the power of an alignment.
\item \nameref{Spell:Blindness}: Negates one of the subject's senses. %Instead of Remove Blindness/Deafness
\item \nameref{Spell:CommandUndead}: Undead creature obeys your commands. %Instead of Aid
\item \nameref{Spell:Darkvision}: See 30 ft. in total darkness. %Instead of Light
\item \nameref{Spell:FalseLife}: Gain 1d10 temporary hp. %Instead of Virtue
\item \nameref{Spell:DeathKnell}: Kill dying creature and gain 1d8 temporary hp, and +2 to Str and your key ability score. %Instead of Divine Footstep
\item \nameref{Spell:GhoulTouch}: Paralyzes one subject, which exudes stench that makes those nearby sickened. %Instead of Restoration
\item \nameref{Spell:LionsCharge}*: You can make full attack in same round you charge.
\item \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
\item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item \nameref{Spell:StrikeOfPain}*: Attack deals additional damage, and sneak attack damage if you have it. %Instead of Searing Blade
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\paragraph{3rd-Level Blackguard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:Contagion}: Infects subject with chosen disease. %Instead of Remove Disease
 \item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
 \item \nameref{Spell:FiendishFlight}*: Subject sprouts wings and flies at speed of 40 ft. %Instead of Celestial Flight
 \item \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
 \item \nameref{Spell:GelugonsSpear}*: Creatures struck by your weapon must save or be slowed. %In place of Mace of the Astral Deva
 \item \nameref{Spell:HealMount}: As Heal on your special mount.
 \item \nameref{Spell:KeenEdge}: Doubles normal weapon's threat range.
 \item \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
 \item \nameref{Spell:Poison}: Creates a temporary batch of poison. %In place of Delay Poison
 \item \nameref{Spell:Question}*: Victim is compelled to answer questions truthfully. %Instead of Comprehend Languages
 \item \nameref{Spell:ShieldSelf}*: Subject takes half of your damage.
 \item \nameref{Spell:UnnaturalEdge}*: Critical hits by weapon become more dangerous. %Instead of Blade of the Sun
\end{list}
\paragraph{4th-Level Blackguard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action. %Instead of Remove Curse
 \item \nameref{Spell:DeathWard}: Grants immunity to death spells and negative energy effects.
 \item \nameref{Spell:DimensionDoor}: Teleports you short distance.
 \item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
 \item \nameref{Spell:DenialOfDeathsEmbrace}*: Subject cannot die from hit point damage.
\end{list}
\paragraph{5th-Level Blackguard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:Atonement}: Removes burden of misdeeds from subject.
 \item \nameref{Spell:BanishingWeapon}*: Melee weapon banishes outsiders.
 \item \nameref{Spell:Commune}: Deity answers three yes-or-no questions.
 \item \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away.
 \item \nameref{Spell:FormHorror}: Subject gains the form of a tentacled monstrosity. %Instead of Form of the Celestial.
 \item \nameref{Spell:WidowmakerBlade}*: Melee weapon culls out the weak. %Instead of Disruping Weapon
 \item \nameref{Spell:AlignedSword}: Weapon becomes +5, deals +2d6 damage against one alignment.
 \item \nameref{Spell:RighteousMight}: Your size increases, and you gain combat bonuses.
 \item \nameref{Spell:SlayLiving}: Touch attack kills subject. %Instead of Heal
 \item \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\end{list}
\paragraph{6th-Level Blackguard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:CrushingOnsetOfAge}*: Subject ages, withers, and dies before your eyes. %Instead of Assault of the Sevenfold Heaven
 \item \nameref{Spell:DweomerBlockade}*: You cut a creature off from all magic.%Instead of Bow of the Solar
 \item \nameref{Spell:FormFiend}*: You assume the form of a terrifying fiend.
 \item \nameref{Spell:PersonalMindBlank}*: You are immune to scrying and mental effects.
 \item \nameref{Spell:PlaneShift}: As many as eight subjects travel to another plane.
 \item \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\end{list}