\subsection[Dread Knight]{The Dread Knight}
\begin{quote}
\emph{Corny and angsty quote}
-Name, race Dread Knight
\end{quote}

Dread Knights are spellcasters born with the magical spark in them - but in a dark and twisted form.
Some embrace it, becoming merciless killers, antipaladins.
Others try to turn their powers towards good, becoming dark avengers of sorts.
The thing all Dread Knights have in common is that when one shows up, things are about to go horribly wrong for someone.
\paragraph{Alignment:} Any nongood
\paragraph{Hit Die:} d10
\paragraph{Class skills:}
The Dread Knight's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Disguise (Cha), Forgery (Cha), Gather Information (Cha), Intimidate (Cha), Hide (Dex) Knowledge (Arcana) (Int), Knowledge (local) (Int), Knowledge (religion) (Int), Knowledge (the planes) (Int), Move Silently (Dex), Profession (Wis), Ride (Dex), Sense Motive (Wis), and Spellcraft (Int).

\paragraph{Skill Points at 1st Level:} (4 + Int modifier) $\times$ 4.
\paragraph{Skill Points at each additional Level:} 4 + Int modifier.
\begin{table*}
%\centering
\caption{The Dread Knight}
\small
\label{tab:DreadKnight}
%\rowcolors{1}{white}{lightgray}
\makebox[\textwidth]{%\resizebox{1.2\textwidth}{!}{
\begin{tabular}{|l|l|c|c|c|l|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Level}}&\multirow{2}{*}{\textbf{BAB}}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\multirow{2}{*}{\textbf{Special}}&\multirow{2}{*}{\textbf{SP/day}}&\textbf{Spells}&\textbf{Max}\\
&&\textbf{save}&\textbf{save}&\textbf{save}&&&\textbf{known}&\textbf{level}\\
\hline
1st &+1			&+2 &+0 &+2 	&Bonus Feat, Dark Grace			&0 &1 &1st\\
2nd &+2 		&+3 &+0 &+3 	&Bonus Feat 				&1 &2 &1st\\
3rd &+3 		&+3 &+1 &+3 	&-    					&3 &3 &1st\\
4th &+4 		&+4 &+1 &+4 	&-    					&5 &4 &2nd\\
5th &+5 		&+4 &+1 &+4 	&Bonus Feat   				&7 &5 &2nd\\
6th &+6/+1 		&+5 &+2 &+5 	&-    					&11 &6 &2nd\\
7th &+7/+2 		&+5 &+2 &+5 	&-    					&15 &7 &3rd\\
8th &+8/+3 		&+6 &+2 &+6 	&Bonus Feat   				&19 &8 &3rd\\
9th &+9/+4 		&+6 &+3 &+6 	&-    					&23 &9 &3rd\\
10th &+10/+5		&+7 &+3 &+7 	&-    					&27 &10 &4th\\
11th &+11/+6/+1		&+7 &+3 &+7 	&Bonus Feat   				&35 &11 &4th\\
12th &+12/+7/+2 	&+8 &+4 &+8 	&-    					&43 &12 &4th\\
13th &+13/+8/+3 	&+8 &+4 &+8 	&-    					&51 &13 &5th\\
14th &+14/+9/+4 	&+9 &+4 &+9 	&Bonus Feat   				&59 &14 &5th\\
15th &+15/+10/+5	&+9 &+5 &+9 	&-    					&67 &15 &5th\\
16th &+16/+11/+6/+1 	&+10 &+5 &+10 	&-    					&79 &16 &6th\\
17th &+17/+12/+7/+2 	&+10 &+5 &+10 	&Bonus Feat   				&91 &17 &6th\\
18th &+18/+13/+8/+3 	&+11 &+6 &+11 	&-    					&103 &18 &6th\\
19th &+19/+14/+9/+4 	&+11 &+6 &+11 	&-    					&115 &19 &6th\\
20th &+20/+15/+10/+5	&+12 &+6 &+12 	&Bonus Feat   				&127 &20 &6th\\
\hline
\end{tabular}}%}
\end{table*}
\subsubsection{Class Features}
All the following are class features of the Dread Knight.

\paragraph{Weapon and Armor Proficiency:} 
Dread Knights are proficient with all simple and martial weapons, 
with all types of armor (heavy, medium, and light, but not exotic armors),
and with shields (except tower shields and exotic shields).

\paragraph{Spell Points/Day:} A Dread Knight's ability to cast spells is limited by the spell points he has available. 
His base daily allotment of spell points is given on \nameref{tab:DreadKnight} table. 
In addition, he receives bonus spell points per day if he has a high Charisma score.
His race may also provide bonus spell points per day, as may certain feats and items.

\paragraph{Spells Known:} A Dread Knight begins play knowing one Dread Knight spell of your choice. 
Each time he achieves a new level, he unlocks the knowledge of new spells.
Choose the spells known from the Dread Knight spell list
(Exception: The feats Expanded Knowledge and Epic Expanded Knowledge do allow a Dread Knight to learn spells of other classes, even specialist Wizard spells.).
A Dread Knight can cast any spell he knows that has a spell point cost equal to or lower than his caster level.
The number of times a Dread Knight can cast spells in a day is limited only by his daily spell points. 
A Dread Knight simply knows his spells; they are ingrained in his mind, though he must get a good night's sleep each day to regain all his spent spell points.
The Difficulty Class for saving throws against Dread Knight spells is 10 + one-half the number of spell points spent on the spell (round up) + the Dread Knight's Charisma modifier. 

Spells learned via the Dread Knight class are arcane spells.
\paragraph{Maximum Spell Level Known:} A Dread Knight begins play with the ability to learn 1st-level spells. 
As he attains higher levels, a Dread Knight may gain the ability to master more complex spells, as shown on the \nameref{tab:DreadKnight} table.
To learn or cast a spell, a Dread Knight must have a Charisma score of at least 10 + the spell's level.

\paragraph{Bonus Feats:}
At 1st level, a Dread Knight gets a bonus feat in addition to the feat that any 1st level character gets and the bonus feat granted to a human character.
The Dread Knight gains an additional bonus feat at 2nd level and every three levels thereafter (5th, 8th, 11th, 14th, 17th, and 20th). 
These bonus feats must be drawn from the feats noted as fighter bonus feats, or those feats which have one or more Dread Knight levels as a prerequisite\footnote{
The feats that require Dread Knight levels to take are \nameref{Feat:BastardsStrike}, \nameref{Feat:CurseOfTheDreadKnight}.}. 
The Dread Knight must still meet all prerequisites for the bonus feat, 
including ability score and base attack bonus minimums as well as class requirements. 
A Dread Knight cannot choose feats that specifically require levels in the fighter class 
unless he is a multiclass character with the requisite levels in the fighter class.

These bonus feats are in addition to the feats that a character of any class gains every three levels. 
A Dread Knight is not limited to fighter bonus feats and feats with Dread Knight levels as a requirement when choosing these other feats.

\paragraph{Dark Grace: (Su)} 
A Dread Knight gains a bonus on all saving throws equal to his Charisma modifier or his Dread Knight level, whichever is lower.
This is a Supernatural ability that functions continuously.
\subsubsection{Ex-Dread Knights:}
A Dread Knight who changes to a good alignment loses his ability to cast Dread Knight spells, 
the Dark Grace class feature, 
and all supernatural feats that have one or more Dread Knight levels as a prerequisite.
The spellcasting and other abilities remain dormant until he atones (see the \nameref{Spell:Atonement} spell description).

\subsubsection[Bastard's Strike]{Bastard's Strike [Magical]}
Your blows are more lethal than they have any right to be.
\label{Feat:BastardsStrike}

\paragraph{Prerequisite:} Dread Knight level 1st.

\paragraph{Benefit:}
By expending your magical focus, you can automatically confirm a critical threat you have just rolled.

This is a supernatural ability whose activation is part of the attack.
\subsubsection[Curse of the Dread Knight]{Curse of the Dread Knight [Magical]}
\label{Feat:CurseOfTheDreadKnight}
You can lay down a weakening curse upon your enemies.

\paragraph{Prerequisite:} Dread Knight level 1st.

\paragraph{Benefit:}
By expending your magical focus as a swift action, 
you can call upon dark powers to target one or more creatures within 30' with a curse.
Each individual targeted creature must succeed on a Will save (DC 10 + $1/2$ your character level + your Charisma modifier) 
or take a -2 penalty on all attack rolls, saving throws, ability checks and skill checks for one hour.

At Dread Knight level 7th, the penalty increases to -4. At 14th level, it increases to -6.

This is a supernatural ability.
\subsubsection{Bleeding Edge}
Makes a weapon cause wounds that bleed over time. Con damage?
\subsubsection{Cerebral Disturbance}
Touch attack, no-save slow.
\subsubsection{Darkbolt}
Single-target damage + stun.
\subsubsection{Rotting Curse}
Con damage per hour.

\subsubsection{Dread Knight Spell List}
\paragraph{1st-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
%\item \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item \nameref{Spell:Bane}: Enemies take -1 on attack rolls and saves against fear.% Instead of Bless
\item \nameref{Spell:Blackfire}*: Fires shed light for you only. %Instead of Zone of Truth
\item \nameref{Spell:CorruptWeapon}: Weapon bypasses the defenses of good foes. % Instead of Bless Weapon
%\item \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item \nameref{Spell:CursedBlade}*: Wounds caused by weapon refuse to heal. %Instead of Armaments of Faith
\item \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
%\item \nameref{Spell:DetectUndead}: Reveals the presence and strength and of undead creatures.
%\item \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
%\item \nameref{Spell:DivineFavor}: You gain a luck bonus on attack and damage rolls.
%\item \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item \nameref{Spell:Fear}: One creature flees for 1d4 rounds. %Instead of Remove Fear
\item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
\item \nameref{Spell:UncannyAccuracy}*: Your underhanded attacks are surprisingly effective. %Instead of True Strike
\item \nameref{Spell:SummonWeapon}*: Summons bonded weapon to your hand.
\item \nameref{Spell:SurgeOfStrength}*: Gain temporary strength and hit points.
\end{list}
\paragraph{2nd-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
%\item \nameref{Spell:AlignWater}*: Vial of water is imbued with the power of an alignment.
\item \nameref{Spell:Blindness}: Negates one of the subject's senses. %Instead of Remove Blindness/Deafness
%\item \nameref{Spell:CommandUndead}: Undead creature obeys your commands. %Instead of Aid
\item \nameref{Spell:Darkvision}: See 30 ft. in total darkness. %Instead of Light
%\item \nameref{Spell:FalseLife}: Gain 1d10 temporary hp. %Instead of Virtue
%\item \nameref{Spell:DeathKnell}: Kill dying creature and gain 1d8 temporary hp, and +2 to Str and your key ability score. %Instead of Divine Footstep
%\item \nameref{Spell:GhoulTouch}: Paralyzes one subject, which exudes stench that makes those nearby sickened. %Instead of Restoration
%\item \nameref{Spell:LionsCharge}*: You can make full attack in same round you charge.
%\item \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
%\item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item \nameref{Spell:StrikeOfPain}*: Attack deals additional damage, and sneak attack damage if you have it. %Instead of Searing Blade
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\paragraph{3rd-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
%\item \nameref{Spell:Contagion}: Infects subject with chosen disease. %Instead of Remove Disease
\item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
%\item \nameref{Spell:FiendishFlight}*: Subject sprouts wings and flies at speed of 40 ft. %Instead of Celestial Flight
%\item \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
%\item \nameref{Spell:GelugonsSpear}*: Creatures struck by your weapon must save or be slowed. %In place of Mace of the Astral Deva
%\item \nameref{Spell:HealMount}: As Heal on your special mount.
\item \nameref{Spell:KeenEdge}: Doubles normal weapon's threat range.
\item \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
%\item \nameref{Spell:Poison}: Creates a temporary batch of poison. %In place of Delay Poison
%\item \nameref{Spell:Question}: Victim is compelled to answer questions truthfully. %Instead of Comprehend Languages
\item \nameref{Spell:ShieldSelf}*: Subject takes half of your damage.
\item \nameref{Spell:UnnaturalEdge}*: Critical hits by weapon become more dangerous. %Instead of Blade of the Sun
\end{list}
\paragraph{4th-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action. %Instead of Remove Curse
%\item \nameref{Spell:DeathWard}: Grants immunity to death spells and negative energy effects.
\item \nameref{Spell:DimensionDoor}: Teleports you short distance.
%\item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
\item \nameref{Spell:DenialOfDeathsEmbrace}*: Subject cannot die from hit point damage.
\end{list}
\paragraph{5th-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
%\item \nameref{Spell:Atonement}: Removes burden of misdeeds from subject.
%\item \nameref{Spell:BanishingWeapon}*: Melee weapon banishes outsiders.
%\item \nameref{Spell:Commune}: Deity answers three yes-or-no questions.
%\item \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away.
\item \nameref{Spell:FormHorror}: Subject gains the form of a tentacled monstrosity. %Instead of Form of the Celestial.
\item \nameref{Spell:WidowmakerBlade}*: Melee weapon culls out the weak. %Instead of Disruping Weapon
%\item \nameref{Spell:AlignedSword}: Weapon becomes +5, deals +2d6 damage against one alignment.
%\item \nameref{Spell:RighteousMight}: Your size increases, and you gain combat bonuses.
\item \nameref{Spell:SlayLiving}: Touch attack kills subject. %Instead of Heal
\item \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\end{list}
\paragraph{6th-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:CrushingOnsetOfAge}*: Subject ages, withers, and dies before your eyes. %Instead of Assault of the Sevenfold Heaven
\item \nameref{Spell:DweomerBlockade}*: You cut a creature off from all magic.%Instead of Bow of the Solar
%\item \nameref{Spell:FormFiend}*: You assume the form of a terrifying fiend.
\item \nameref{Spell:PersonalMindBlank}*: You are immune to scrying and mental effects.
%\item \nameref{Spell:PlaneShift}: As many as eight subjects travel to another plane.
%\item \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\end{list}