\subsection{Loremaster}
\begin{quote}
\emph{``Why, this reminds me of a story I once heard...''}
- Veyr, human Loremaster
\end{quote}
A Loremaster is a spellcaster whose magic is a means to collect ever more information about the world.
\paragraph{Hit Die:} d4
\paragraph{Requirements:}
To qualify to become a Loremaster, a character must fulfill all the following criteria.
\subparagraph{Skills:} Knowledge (any two) 10 ranks in each.
\subparagraph{Feats:} Any three metamagic or item creation feats, plus Skill Focus (Knowledge [any individual Knowledge skill]).
\subparagraph{Spells:} Able to cast three different divination spells, one of which must be 3rd level or higher.
\paragraph{Class Skills}
The Loremaster's class skills (and the key ability for each skill) are Appraise (Int), Concentration (Con), Craft (alchemy) (Int), Decipher Script (Int), Gather Information (Cha), Handle Animal (Cha), Heal (Wis), Knowledge (all skills taken individually) (Int), Perform (Cha), Profession (Wis), Speak Language (None), Spellcraft (Int), and Use Magic Device (Cha).
\paragraph{Skill Points at each level:} 4 + Int modifier.
\begin{table*}
\centering
\caption{The Loremaster}
\label{tab:Loremaster}
%\makebox[\textwidth]{
\begin{tabular}{|l|l|c|c|c|l|l|}
\hline
\textbf{Level}&\textbf{BAB}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\textbf{Special}&\textbf{Spellcasting}\\
\hline
1st	&+0	&+0	&+0	&+2	&Secret		&+1 level of existing class\\
2nd	&+1	&+0	&+0	&+3	&Lore		&+1 level of existing class\\
3rd	&+1	&+1	&+1	&+3	&Secret		&+1 level of existing class\\
4th	&+2	&+1	&+1	&+4	&Bonus language	&+1 level of existing class\\
5th	&+2	&+1	&+1	&+4	&Secret		&+1 level of existing class\\
6th	&+3	&+2	&+2	&+5	&Greater lore	&+1 level of existing class\\
7th	&+3	&+2	&+2	&+5	&Secret		&+1 level of existing class\\
8th	&+4	&+2	&+2	&+6	&Bonus language	&+1 level of existing class\\
9th	&+4	&+3	&+3	&+6	&Secret		&+1 level of existing class\\
10th	&+5	&+3	&+3	&+7	&True lore	&+1 level of existing class\\
\hline
\end{tabular}
%}
\end{table*}
\subsubsection{Class Features}
All the following are Class Features of the Loremaster prestige class.

\paragraph{Weapon and Armor Proficiency:} Loremasters gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} When a new Loremaster level is gained, the character gains spell points per day, an increase in caster level, spells known and maximum available spell level as if he had also gained a level in whatever spellcasting class in which he could cast sufficient divination spells to enter before he added the prestige class level. 
He does not, however, gain any other benefit a character of that class would have gained. 
If a character had more than one applicable spellcasting class before he became a Loremaster, 
he must decide to which class he adds each level of Loremaster for the purpose of determining what spellcasting class gains the benefit of the spellcasting advancement.

\paragraph{Secret:}
At 1st level and every two levels higher than 1st (3rd, 5th, 7th, and 9th), the Loremaster chooses one secret from the following list.
He can't choose the same secret twice.

\subparagraph{Instant Mastery:}
You gain 4 ranks in a skill in which you previously had no ranks.\\
\subparagraph{Secret Health (Ex):}
You gain a number of hit points equal to your current number of Hit Dice. 
Each time you gain a Hit Die (such as by gaining a level), you gain 1 additional hit point. 
If you lose a Hit Die, you permanently lose 1 hit point.
\subparagraph{Secrets of Inner Strength (Ex):}
You gain a +2 bonus on Will saves.
\subparagraph{The Lore of True Stamina (Ex):}
You gain a +2 bonus on Fortitude saves.
\subparagraph{Secret Knowledge of Avoidance (Ex):}
You gain a +2 bonus on Reflex saves.
\subparagraph{Weapon Trick (Ex):}
You gain a +1 bonus on all attack rolls.
\subparagraph{Dodge Trick (Ex):}
You gain a +1 dodge bonus to AC. Unless otherwise noted, dodge bonuses stack.
\subparagraph{Applicable Knowledge:}
You gain a bonus feat for which you meet the prerequisites.
\subparagraph{Newfound Arcana:}
You gain \nameref{Feat:MagicallyGifted} as a bonus feat.

\paragraph{Lore (Ex):}
At 2nd level, a Loremaster gains the ability to know legends or information regarding various topics. This ability is identical to the \nameref{sec:Bard}'s Bardic Knowledge class feature, using your Loremaster level in place of the Bard level. This counts as Bardic Knowledge for all purposes, including those of prerequisites. If you have Bard levels, you do not use the abilities separately, but your Loremaster and Bard levels stack for purposes of determining your bonus on the check.

\paragraph{Bonus Languages:}
A Loremaster can choose any new language at 4th and 8th level.

\paragraph{Greater Lore (Sp):}
At 6th level, a Loremaster gains the ability to use \nameref{Spell:Identify} as a spell-like ability at will.
Caster level equals your number of Hit Dice.

\paragraph{True Lore (Sp):}
At 10th level, once per day a Loremaster can use her knowledge to use \nameref{Spell:LegendLore} as a spell-like ability.