\subsection{Metamage}
\begin{quote}
\emph{I was once like you. So full of hope. But the world doesn't reward hope, pup.}
- Torgar, human Blackguard
\end{quote}
A Blackguard is usually a Paladin who has not only fallen from grace, but become what he once fought. Whether they made a conscious choice to turn from the path of good or were slowly corrupted, Blackguards are some of the most vile foes a mortal will face.
\paragraph{Hit Die:} d4\\
\paragraph{Requirements:}
To qualify to become a Metamage, a character must fulfill all the following criteria.

\subparagraph{Skills:} 
Knowledge (arcana) 8 ranks, Spellcraft 8 ranks.
\subparagraph{Feats:} 
At least two metamagic feats.
\subparagraph{Spells:}
Ability to cast 3rd-level arcane spells.

\paragraph{Class Skills}

The Metamage's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Knowledge (all skills taken individually) (Int), Profession (Wis), and Spellcraft (Int). 

\paragraph{Skill Points at Each Level} 2 + Int modifier.
\begin{table*}
\caption{The Metamage}
\label{tab:Metamage}
\makebox[\textwidth]{
\begin{tabular}{|l|l|c|c|c|l|l|}
\hline
\textbf{Level}&\textbf{BAB}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\textbf{Special}&\textbf{Spellcasting}\\
\hline
1st	&+0	&+0	&+0	&+2	&Efficient Metamagic 1/day&+1 level of existing arcane spellcasting class\\
2nd	&+1	&+0	&+0	&+3	&Share Metamagic	&+1 level of existing arcane spellcasting class\\
3rd	&+1	&+1	&+1	&+3	&			&+1 level of existing arcane spellcasting class\\
4th	&+2	&+1	&+1	&+4	&			&+1 level of existing arcane spellcasting class\\
5th	&+2	&+1	&+1	&+4	&Easy Metamagic 1/day	&+1 level of existing arcane spellcasting class\\
6th	&+3	&+2	&+2	&+5	&			&+1 level of existing arcane spellcasting class\\
7th	&+3	&+2	&+2	&+5	&			&+1 level of existing arcane spellcasting class\\
8th	&+4	&+2	&+2	&+6	&			&+1 level of existing arcane spellcasting class\\
9th	&+4	&+3	&+3	&+6	&Easy Metamagic 2/day	&+1 level of existing arcane spellcasting class\\
10th	&+5	&+3	&+3	&+7	&Metamagic Mastery	&+1 level of existing arcane spellcasting class\\
\hline
\end{tabular}}
\end{table*}
\subsubsection{Class Features}
All the following are Class Features of the Metamage prestige class.

\paragraph{Weapon and Armor Proficiency:} Metamages gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} When a new Metamage level is gained, the character gains spell points per day, an increase in caster level, and spells known as if he had also gained a level in whatever arcane spellcasting class in which he could cast 3rd-level spells before he added the prestige class level. 
He does not, however, gain any other benefit a character of that class would have gained. 
If a character had more than one arcane spellcasting class in which he could cast 3rd-level spells before he became a Metamage, he must decide to which class he adds each level of Metamage for the purpose of determining what spellcasting class gains the benefit of the spellcasting advancement.

% \paragraph{Focused Specialization (Ex):}
% A Metamage gives up some of his versatility in magic to focus on that which remains to him.
% Upon first entering the Metamage class, choose a school of magic to give up.
% From this point onward, you may never learn spells from that school of magic.

\paragraph{Efficient Metamagic (Su):}
Metamages have found that once a spell has been opened for metamagic, applying multiple modifications to the spell is not much more difficult than applying just one. 
Once per day, he can apply two metamagic feats to a spell, only paying the spell point cost increase for the metamagic feat with the higher adjustment. For example, a Metamage knowing the \nameref{Feat:EmpowerSpell} and \nameref{Feat:MaximizeSpell} feats could apply both feats to a spell, only paying the spell point adjustment for Maximize Spell, it having the higher spell point adjustment of the two feats.

\paragraph{Share Metamagic (Su):}
At 2nd level, a Metamage can share knowledge of any or all of his Metamagic feats whenever he participates in \nameref{sec:CircleMagic}, just as he can share knowledge of his spells known.

\paragraph{Easy Metamagic (Su):}
At 5th level, the Metamage gains a limited ability to apply metamagic without interrupting his concentration.
Once per day, he may apply a metamagic feat to a spell without expending his magical focus.
At 9th level, he can do so twice per day.

\paragraph{Metamagic Mastery (Su):}
At 10th level, the Metamage's ability to manipulate magic has come to its peak.
Whenever the Metamage applies a metamagic feat to a spell, he pays two less spell points for the metamagic adjustment than normal.
Metamagic feats with a cost of one or no spell points are not affected by this ability.