\newpage
\subsection{Where's my favorite spell?}
\label{sec:MissingSpells}
This conversion does not contain all the spells in the \href{http://www.wizards.com/default.asp?x=d20/article/srd35}{d20 srd}.
Some were merged into others, some were merely renamed, but some truly aren't here. 
The most common reason for a spell not being included was it being too limited in scope to justify being a spell of its own under the revised system.
This is a list of all SRD spells that do not have a converted spell with the same name.
Note that some spells might have changed levels.
{\small
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item Acid Fog: Merged into Deadly Fog.
 \item Acid Splash: See the Cantrips class feature.
 \item Analyze Dweomer: Merged into Identify.
 \item Animal Growth: Merged into Alter Animal's Size.
 \item Animal Shapes: Removed. Replace with Form of the Carnivore for item creation and other purposes.
 \item Animal Trance: Removed. Replace with Pattern for item creation and other purposes.
 \item Animate Rope: Removed. Replace with Animate objects for item creation and other purposes.
 \item Antipathy: Merged into Telepathic Beacon
 \item Antiplant Shell: Removed. Replace with Antilife Shell for item creation and other purposes.
 \item Arcane Lock: Merged into Open/Close.
 \item Arcane Mark: See the Cantrips class feature.
 \item Arcane Sight, Greater: Merged into Detect Magic.
 \item Arcane Sight: Merged into Detect Magic.
 \item Banishment: Merged into Dismissal.
 \item Bear's Endurance, Bull's Strength, Cat's Grace, Eagle's Splendor, Fox's Cunning and Owl's Wisdom, Mass: Merged into Wombat's Boost.
 \item Bear's Endurance, Bull's Strength, Cat's Grace, Eagle's Splendor, Fox's Cunning and Owl's Wisdom: Merged into Wombat's Boost.
 \item Blasphemy/Dictum/Holy Word/Word of Chaos: Merged into Word of God.
 \item Break Enchantment: Merged into Remove Curse.
 \item Burning Hands: Merged into Energized Touch.
 \item Call Lightning Storm: Merged into Call Lightning.
 \item Calm Animals: Removed. Replace with Calm Emotions for item creation and other purposes.
 \item Cause Fear: Renamed Fear.
 \item Changestaff: Merged into Liveoak.
 \item Charm Animal: Isn't this what Wild Empathy is for? Removed. Replace with Charm for item creation and other purposes.
 \item Charm Monster, Mass: Merged into Charm.
 \item Charm Monster: Merged into Charm.
 \item Charm Person: Renamed Charm.
 \item Chill Touch: Merged into Energized Touch.
 \item Circle of Death: Merged into Life and Death.
 \item Clenched Fist: Pending. Can't think of more Hand spells.
 \item Clone: Merged into Gentle Repose.
 \item Cloudkill: Merged into Noxious Vapors.
 \item Command Plants: Renamed Command Nature's Allies.
 \item Continual Flame: Merged into Light.
 \item Control Plants: Renamed Control Nature's Allies.
 \item Create Greater Undead: Merged into Create Undead.
 \item Create Water: See Water domain.
 \item Crushing Hand: Pending. Can't think of more Hand spells.
 \item Cure Critical Wounds, Mass: Merged into Cure Wounds.
 \item Cure Critical Wounds: Merged into Cure Wounds.
 \item Cure Light Wounds, Mass: Merged into Cure Wounds.
 \item Cure Light Wounds: Merged into Cure Wounds.
 \item Cure Moderate Wounds, Mass: Merged into Cure Wounds.
 \item Cure Moderate Wounds: Merged into Cure Wounds.
 \item Cure Serious Wounds, Mass: Merged into Cure Wounds.
 \item Dancing Lights: See the Cantrips class feature.
 \item Daylight: Merged into Light.
 \item Daze Monster: Merged into Daze.
 \item Deathwatch: Turned into a Healing domain ability.
 \item Deep Slumber: Merged into Sleep.
 \item Delayed Blast Fireball: Changed into a Metamagic feat. Replace with fireball for item creation and other purposes.
 \item Delay Poison: Merged into Antipoison.
 \item Demand: Removed, replaced with Scrying + the Scry and Die feat. Replace with Suggestion for item creation and other purposes.
 \item Destruction: Merged into Slay Living.
 \item Detect Animals or Plants: Removed. What is this even? Replace with 4 ranks in Spot for item creation and other purposes.
 \item Detect Chaos/Evil/Good/Law: Merged into Discern Alignment.
 \item Detect Snares and Pits: Removed. Replace with Trapfinding for item creation and other purposes.
 \item Detect Thoughts: Renamed Read Thoughts.
 \item Detect Undead: Removed. Replace with Discern Alignment
 \item Diminish Plants: Merged into Plant Growth.
 \item Discern Lies: Removed due to overlap with Zone of Truth.
 \item Discern Location: Renamed Absolute Revelation, due to me thinking that ``Discern Location'' and ``Location'' are too similar.
 \item Dispel Chaos/Evil/Good/Law: Merged into Dispel Alignment
 \item Dispel Magic, Greater: Merged into Dispel Magic.
 \item Displacement: Merged into Blur.
 \item Disrupt Undead: Removed. Replace with Align Water for item creation and other purposes.
 \item Divination: Merged into Augury.
 \item Dominate Animal: Merged into Dominate.
 \item Dominate Monster: Merged into Dominate.
 \item Dominate Person: Merged into Dominate.
 \item Doom: Merged into Fear.
 \item Energy Drain: Merged into Enervation.
 \item Enlarge Person, Mass: Merged into Alter Size.
 \item Enlarge Person: Merged into Alter Size.
 \item Enthrall: Removed. Replace with Charm for item creation and other purposes.
 \item Erase: Removed. Replace with the Cantrip class feature for item creation and other purposes.
 \item Etherealness: Merged into Ethereal Jaunt.
 \item Fabricate: Merged into Mold Material.
 \item Feather Fall: Merged into Control Fall.
 \item Find the Path: Removed, pending inspiration. Replace with Legend Lore for purposes of item creation.
 \item Find Traps: Renamed Trap Intuition.
 \item Fire Shield: Renamed Aura of Fire.
 \item Fire Trap: Replaced with Explosive Runes.
 \item Flame Arrow: Renamed Energy Arrow.
 \item Flare: Merged into Light.
 \item Flesh to Stone: Merged into Transmute Flesh and Stone
 \item Fog Cloud: Merged into Fog.
 \item Forcecage: Merged into Resilient Sphere.
 \item Forceful Hand: Pending. Can't think of more Hand spells. Replace with one of the other ''hand`` spells for item creation and other purposes.
 \item Ghost Sound: Removed. Replace with Ventriloquism for item creation and other purposes.
 \item Glyph of Warding, Greater: Merged into Glyph of Warding.
 \item Good Hope: Removed due to redundancy.
 \item Grasping Hand: Pending. Can't think of more Hand spells.
 \item Guards and Wards: Changed into a magic item.
 \item Guidance: Removed. Replace with Bless for item creation and other purposes.
 \item Hallow/Unhallow: Partially removed, rest merged into Consecrate/Desecrate.
 \item Heal, Mass: Merged into Heal.
 \item Heroism, Greater: Merged into Heroism.
 \item Hide from Animals: Renamed Shroud the Weak Mind.
 \item Hide from Undead: Changed into a Death Domain granted power. Use Invisibility for its other function.
 \item Hold Monster, Mass: Merged into Hold Person.
 \item Hold Monster: Merged into Hold Person.
 \item Hold Person, Mass: Merged into Hold Person.
 \item Hold Portal: Merged into Open/Close.
 \item Holy Sword: Renamed Aligned Sword.
 \item Hypnotic Pattern: Merged into Pattern.
 \item Hypnotism: Merged into Pattern.
 \item Illusory Script: Pending inspiration.
 \item Illusory Wall: Replaced with Image. 
 \item Incendiary Cloud: Merged into Deadly Fog.
 \item Inflict Light, Moderate, Serious, and Critical Wounds, Mass: Merged into Inflict Wounds.
 \item Inflict Light, Moderate, Serious, and Critical Wounds: Merged into Inflict Wounds.
 \item Inflict minor wounds: Removed. Replace with Inflict Wounds for item creation and other purposes.
 \item Insanity: Merged into Confusion.
 \item Invisibility Sphere: Merged into Invisibility.
 \item Invisibility, Greater: Merged into Invisibility.
 \item Invisibility, Mass: Merged into Invisibility.
 \item Iron Body: Renamed Form of the Iron Golem.
 \item Ironwood: Merged into Transmute Metal and Wood.
 \item Jump: Merged into Control Fall.
 \item Knock: Merged into Open/Close.
 \item Know Direction: Make a DC 15 Survival check instead.
 \item Lesser Confusion: Renamed Random Action.
 \item Lightning Bolt: Removed due to lack of niche. Replace with Fireball for item creation and other purposes.
 \item Locate Creature: Merged into Locate.
 \item Locate Object: Merged into Locate.
 \item Longstrider: Travel domain granted ability.
 \item Lullaby: Is now a Bard class feature.
 \item Mage Hand: See the Cantrips class feature.
 \item Mage's Faithful Hound: Removed. replace with Summon Monster for item creation and other purposes.
 \item Mage's Lucubration: Not appropriate under this ruleset. Replace with Mnemonic Enhancer for item creation and other purposes.
 \item Mage's Magnificent Mansion: Removed. Replace with Tiny Hut for item creation and other purposes.
 \item Magic Circle against Chaos/Evil/Good/Law: Merged into Aligned Protection.
 \item Magic Fang, Greater: Merged into Magic Weapon.
 \item Magic Fang: Merged into Magic Weapon.
 \item Magic Jar: Renamed Possession.
 \item Magic Mouth: Merged into Ventriloquism.
 \item Magic Weapon, Greater: Merged into Magic Weapon.
 \item Major Creation: Merged into Matter Creation.
 \item Major Image: Merged into Image.
 \item Mending: Merged into Repair.
 \item Message: Merged into Mental Link.
 \item Minor Creation: Renamed Matter Creation.
 \item Minor Image: Merged into Image.
 \item Mirage Arcana: Merged into Hallucinatory Terrain.
 \item Misdirection: Effectively merged into Magic Aura.
 \item Move Earth: To be put on the Earth domain list.
 \item Neutralize Poison: Merged into Antipoison.
 \item Nightmare: Merged into Dream.
 \item Obscure Object: Merged into Nondetection.
 \item Obscuring Mist: Renamed Fog.
 \item Overland Flight: Merged into Fly.
 \item Owl's Wisdom, Mass: Merged into Wombat's Boost.
 \item Pass without Trace: Now a Trickery domain granted power.
 \item Passwall: Removed. Replace with Mold Material for item creation and other purposes.
 \item Permanency: Removed due to changed design.
 \item Permanent Image: Merged into Image.
 \item Persistent Image: Merged into Image.
 \item Phantom Steed: Merged into Mount.
 \item Planar Binding, Greater: Merged into Planar Binding.
 \item Polymorph Any Object: Removed. Replace with Shapechange for item creation and other purposes.
 \item Power Word Kill: Merged into Power Word.
 \item Power Word Stun: Merged into Power Word.
 \item Prayer: Merged into Bless.
 \item Prestidigitation: See the Cantrips class feature.
 \item Prestidigitation: See the Cantrips class feature.
 \item Project Image: Pending inspiration.
 \item Protection from Chaos/Evil/Good/Law: Merged into Aligned Protection.
 \item Protection from Energy: Removed. Replace with Resist Energy for item creation and other purposes.
 \item Protection from Spells: Removed. Replace with Resistance for item creation and other purposes.
 \item Prying Eyes, Greater: Made redundant due to special senses now working through the eyes. Replace with Prying Eyes or True Seeing for item creation and other purposes.
 \item Quench: Removed for reasons of being too damn specific. Replace with Create Water (Water Domain ability) for item creation and other purposes.
 \item Rainbow Pattern: Merged into Pattern.
 \item Ray of Exhaustion: Merged into Touch of Fatigue
 \item Ray of Frost: See the Cantrips class feature.
 \item Read Magic: See the Cantrips class feature.
 \item Reduce Animal: Merged into Alter Animal's Size.
 \item Reduce Person, Mass: Merged into Alter Size.
 \item Reduce Person: Merged into Alter Size.
 \item Repulsion: Replaced With Antilife Shell.
 \item Rope Trick: Removed. Replace with Tiny Hut for item creation and other purposes.
 \item Scare: Merged into Fear.
 \item Scrying, Greater: Merged into Scrying.
 \item Sculpt Sound: Pending inspiration.
 \item Secret Chest: Removed. Replace with Plane Shift for item creation and other purposes.
 \item Secret Page: Pending inspiration.
 \item Secure Shelter: Merged into Tiny Hut.
 \item Seeming: Merged into Disguise.
 \item Shades: Merged into Shadow Conjuration
 \item Shadow Conjuration, Greater: Merged into Shadow Conjuration.
 \item Shadow Evocation, Greater: Merged into Shadow Evocation.
 \item Shambler: Removed. Replace with Summon Monster for item creation and other purposes.
 \item Shocking Grasp: Merged into Energized Touch.
 \item Shout, Greater: Merged into Shout.
 \item Silent Image: Renamed Image.
 \item Snare: Pending inspiration.
 \item Solid Fog: Merged into Fog.
 \item Speak with Animals: Merged into Converse with Nature
 \item Speak with Plants: Merged into Converse with Nature.
 \item Speak with Plants: Merged into Converse with Nature.
 \item Spellstaff: Removed. Replace with Shillelagh for item creation and other purposes.
 \item Spider Climb: Merged into Animal's Movement.
 \item Statue: Removed on account of me not being able to figure out how to make this stuff ever worth a spell known.
 \item Status: Renamed Life Link.
 \item Stinking Cloud: Renamed Noxious Vapors.
 \item Stone Shape: Merged into Mold Material.
 \item Stone Tell: Merged into Converse with Nature.
 \item Stone to Flesh: Merged into Transmute Flesh and Stone
 \item Suggestion, Mass: Merged into Suggestion.
 \item Summon Monster I-IX: Merged into Summon Monster.
 \item Summon Nature's Ally I-IX: Merged into Summon Monster.
 \item Sunbeam: Merged into Sunburst.
 \item Symbol of Death: Changed into a magic item.
 \item Symbol of Fear: Changed into a magic item.
 \item Symbol of Insanity: Changed into a magic item.
 \item Symbol of Pain: Now a magic item.
 \item Symbol of Persuasion: Changed into a magic item.
 \item Symbol of Sleep: Now a magic item.
 \item Symbol of Stunning: Changed into a magic item.
 \item Symbol of Weakness: Changed into a magic item.
 \item Sympathy: Merged into Telepathic Beacon.
 \item Telekinetic Sphere: Merged into Resilient Sphere.
 \item Telepathic Bond: Merged into Mental Link.
 \item Teleport Object: Merged into Teleport.
 \item Teleport, Greater: Merged into Teleport.
 \item Tongues: Merged into Comprehend Languages.
 \item Transmute Metal to Wood: Renamed Transmute Metal and Wood
 \item Transmute Mud to Rock: Merged into Transmute Rock and Mud.
 \item Transmute Rock to Mud: Merged into Transmute Rock and Mud.
 \item Trap the Soul: Removed. Replace with Soul Bind for item creation and other purposes.
 \item Tree Shape: Renamed Form of the Plant.
 \item Tree stride: Removed due to extreme similarities with Transport via Plants. Replace with Transport via Plants for purposes of item creation.
 \item Undeath to Death:Merged into Life and Death.
 \item Undetectable Alignment: Renamed Mask Alignment.
 \item Veil: Merged into Disguise.
 \item Vision: Merged into Legend Lore
 \item Warp Wood: Removed. Replace with Shatter for item creation and other purposes.
 \item Water Breathing: Merged into Animal's Movement.
 \item Waves of Exhaustion: Merged into Waves of Fatigue.
 \item Weird: Merged into Phantasmal Killer.
 \item Whispering Wind: Pending inspiration.
 \item Wood Shape: Merged into Mold Material.
 \item Zone of Silence: Merged into Silence.
\end{list}}
