\subsection{Mystic Theurge}
\begin{quote}
\emph{``I am afraid that the rest of my life would not be sufficient to share all that I have learned.''}
- Thorgeir, half-elven Mystic Theurge
\end{quote}
A Mystic Theurge is a spellcaster adept in both arcane and divine magic, sacrificing rate of advancement for unparalleled breadth of understanding.

\begin{table*}
\caption{The Mystic Theurge}
\label{tab:MysticTheurge}
\makebox[\textwidth][c]{
\begin{tabular}{|l|l|c|c|c|l|l|}
\hline
\textbf{Level}&\textbf{BAB}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\textbf{Special}&\textbf{Spells known, maximum spell level, caster level}\\
\hline
1st	&+0	&+0	&+0	&+2	&Continued Training	&+1 level of primary and secondary spellcasting class\\
2nd	&+1	&+0	&+0	&+3	&-			&+1 level of primary and secondary spellcasting class\\
3rd	&+1	&+1	&+1	&+3	&-			&+1 level of primary and secondary spellcasting class\\
4th	&+2	&+1	&+1	&+4	&-			&+1 level of primary and secondary spellcasting class\\
5th	&+2	&+1	&+1	&+4	&Combined Knowledge	&+1 level of secondary spellcasting class\\
6th	&+3	&+2	&+2	&+5	&-			&+1 level of primary and secondary spellcasting class\\
7th	&+3	&+2	&+2	&+5	&-			&+1 level of primary and secondary spellcasting class\\
8th	&+4	&+2	&+2	&+6	&-			&+1 level of primary and secondary spellcasting class\\
9th	&+4	&+3	&+3	&+6	&-			&+1 level of primary and secondary spellcasting class\\
10th	&+5	&+3	&+3	&+7	&Bonus Feat		&+1 level of primary and secondary spellcasting class\\
11th	&+5	&+3	&+3	&+7	&-			&+1 level of primary and secondary spellcasting class\\
12th	&+6	&+4	&+4	&+8	&-			&+1 level of primary and secondary spellcasting class\\
13th	&+6	&+4	&+4	&+8	&-			&+1 level of primary and secondary spellcasting class\\
14th	&+7	&+4	&+4	&+9	&-			&+1 level of primary and secondary spellcasting class\\
15th	&+7	&+5	&+5	&+9	&Spell Union		&+1 level of secondary spellcasting class\\
16th	&+8	&+5	&+5	&+10	&-			&+1 level of primary and secondary spellcasting class\\
\hline
\end{tabular}}
\end{table*}

\paragraph{Hit Die:} d6
\paragraph{Requirements:}
To qualify to become a Mystic Theurge, a character must fulfill all the following criteria.
\subparagraph{Skills:} Knowledge (arcana) 7 ranks, Knowledge (religion) 7 ranks, Spellcraft 4 ranks.
\subparagraph{Feat:} \nameref{Feat:ContinuedTraining}.
\subparagraph{Spells:} Ability to cast second-level arcane spells and first-level divine spells OR ability to cast first-level arcane spells and second-level divine spells.
\paragraph{Class Skills}
The Mystic Theurge's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Knowledge (all skills, taken individually) (Int), Profession (Wis), Sense Motive (Wis), and Spellcraft (Int).
\paragraph{Skill Points at each level:} 4 + Int modifier.

\subsubsection{Class Features}
All of the following are features of the Mystic Theurge prestige class.

\paragraph{Weapon and Armor Proficiency:} Mystic Theurges gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} In order to benefit from Mystic Theurge spellcasting advancement, the character must have levels in at least two different spellcasting classes, one arcane and one divine. One of them must be designated as the primary spellcasting class, and another as the secondary class. To be designated as a primary spellcasting class, the character must be able to cast second-level spells via that class. If the primary spellcasting class is an arcane spellcasting class, the secondary class must be a divine spellcasting class via which he can cast first level spells, and vice versa. A Mystic Theurge's primary and secondary spellcasting classes must be separate spellcasting classes. The designation must be made when taking the first level of the prestige class, and can not be changed thereafter.

At each Mystic Theurge level except at 5th and 15th, the character gains an increase in caster level, spells known, and maximum available spell level as if he had also gained a level in both his primary and secondary spellcasting classes. At Mystic Theurge levels 5th and 15th, he gains an increase in caster level, spells known, and maximum available spell level as if he had gained a level in his secondary spellcasting class only.

At every Mystic Theurge level, the character gains an increase in spell points as if he had also gained a level in his primary spellcasting class.

He does not, however, gain any other benefit a character of his primary or secondary spellcasting classes would have gained.
\paragraph{Continued Training:} A Mystic Theurge who has the \nameref{Feat:ContinuedTraining} feat for his secondary spellcasting class gains the feat for his primary spellcasting class as a bonus feat. A Mystic Theurge who has the feat for his primary spellcasting class gains the feat for his secondary spellcasting class.

\paragraph{Combined Knowledge (Ex):} At Mystic Theurge level 5th, you can use the key ability modifier of your primary spellcasting class to ddetermine the spell save DCs, ability score minimums, and bonus spell points for your secondary class, if doing so would be beneficial for you.

\paragraph{Bonus Feat:} At Mystic Theurge level 10th, you gain a bonus feat selected from the following list: \nameref{Feat:CelestialSummons}, \nameref{Feat:DomainAttunement}, \nameref{Feat:Familiar}, \nameref{Feat:FiendishSummons}, \nameref{Feat:ScribeScroll} and \nameref{Feat:TurnUndead}. You must meet the prerequisites of the feat, if any.

\paragraph{Spell Union (Su):} At Mystic Theurge level 15th, you may cast two spells as a full-round action. One of the spells must be from your primary spellcasting class, the other from your secondary class. Each spell may have a casting time no longer than one standard action. You must provide components, pay XP and spell point costs, and in all other ways follow the restrictions the spells themselves put in place, the only change is the action required to cast them. This ability can be used once per day.