\subsection{New Cleric Domains}
\label{sec:NewClericDomains}
\subsubsection{Commerce Domain}
\label{sec:CommerceDomain}
\paragraph{Granted Powers}
\subparagraph{Class Skill:}
You add Appraise to your list of Cleric class skills.
\subparagraph{Favorable Background:} A 1st-level character with this domain receives double the normal starting gold for his class. This has no effect on gold gain at subsequent levels, nor does it affect characters who gain this domain at levels other than 1st.
\subparagraph{Goldtongue (Su):}
You receive a sacred bonus equal to one-half your Cleric level (minimum 1) on Diplomacy checks made as part of haggling or mediating trades, as well as on Profession checks used to make a living.
This is a superatural ability that is continuously active.
\subparagraph{Marketing (Ex):}
Starting at Cleric level 4th, you become supremely good at finding ways to market your goods. You receive 25\% more than listed market price when selling found goods (usually gems and art objects). This does not apply to magical objects or trade goods (such as salt or silk, see the Wealth Other Than Coins table).

This is a divinely granted extraordinary ability. The powers of Commerce, while ready to support their more active paragons, do not take kindly to significant disruption of economies and will revoke this ability if abused.
\subparagraph{Market Awareness (Su):}
Starting at Cleric level 8th, you are continuously aware of ways you can do business while in a settlement.

When attempting to procure a certain type of item, you immediately sense whether that item is purchasable within the settlement.
If it is purchasable, you know where (you learn the direction and distance). If it is available in more than one location, you know the closest location.

You can not find a specific or unique item. You must be familiar with the type of item in question. You only sense items currently available for public sale, not closed auctions or items the possessor does not intend to sell (even if a sufficiently lucrative offer might persuade him to).
\subparagraph{Two for One (Ex):}
At Cleric level 12th or later, you can find the deal of a lifetime.

To use this ability, make a purchase of a magic item, as normal. Circumstances then conspire to provide you with another, functionally identical magic item upon completion of the purchase, at no cost to you.

The item must be one that can be freely purchased for gold on the open market, not an artifact or other kind of unique item. The item's cost may not exceed 20\% of the value (not market sale value) of your current possessions.

Any given character can only use this ability once in his career.
\paragraph{Commerce Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
\item[1] \nameref{Spell:Identify}: Determines properties of magic item.
\item[2] \nameref{Spell:ZoneOfTruth}: Subjects within field find it extremely hard to lie.
\item[3] \nameref{Spell:Glibness}: You gain a large bonus on Bluff checks.
\item[3] \nameref{Spell:SepiaSnakeWard}*: Creates ward that immobilizes thieves and pickpockets.
\item[4] \nameref{Spell:Goldskin}*: Taxes your attackers.
\item[5] \nameref{Spell:PrivateSanctum}: Prevents anyone from viewing or scrying an area for 24 hours.
\item[6] \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\item[7] \nameref{Spell:HandOfMidas}*: Touched creature or object turns to gold.
\item[7] \nameref{Spell:MagnificentMansion}: Door leads to extradimensional mansion.
\item[9] \nameref{Spell:TeleportationCircle}: Circle teleports any creature inside to designated spot.
\end{list}
\subsubsection[Moon Domain]{Moon Domain*}
\paragraph{Granted Powers}
\subparagraph{Class Skill:}
Add Hide to your list of Cleric class skills.
\subparagraph{Low-Light Vision:} You gain the low-light vision special quality. If you already have low-light vision, you gain superior low-light vision instead (quadruple the distance, instead of double).
\subparagraph{Hide in Plain Sight (Su):} Starting at Cleric level 12th, you can use the Hide skill even while being observed, as long as you are within the area of some sort of shadow.
This ability does not need any activation beyond making a hide check.
\subparagraph{Moonlight Weapons (Su):}
As a swift action, you can expend your magical focus to have any weapons you use bypass damage reduction as if they were made of silver for a number of rounds equal to your Cleric level.
\paragraph{Moon Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item[1] \nameref{Spell:FaerieFire}: Outlines subjects with light, canceling blur, concealment, and the like.
 \item[1] \nameref{Spell:Light}: Causes object to shine like a torch.
 \item[2] \nameref{Spell:MoonBolt}*: Blasts creature with silvery light, damaging and stunning it.
 \item[2] \nameref{Spell:Moonlust}*: You enchant a creature with visions of the moon, preventing it from acting.
 \item[2] \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
 \item[3] \nameref{Spell:CallOfTheMoon}*: Reveals lycanthropes as what they are.
 \item[3] \nameref{Spell:SummonNaturesAlly}: Summons a natural guardian to aid you.
 \item[3] \nameref{Spell:Wolfsbane}*: Deals debilitating damage to lycanthropes.
 \item[3] \nameref{Spell:Blink}: Subject randomly vanishes and reappears for 1 round/level.
 \item[4] \nameref{Spell:Confusion}: Subjects behave oddly for 1 round/level.
 \item[5] \nameref{Spell:Dream}: Contact or disturb sleeping creature.
 \item[6] \nameref{Spell:ShadowWalk}: Step into shadow to travel rapidly.
 \item[7] \nameref{Spell:CurseOfLycanthropy}*: You infect a creature with lycanthropy.
 \item[8] \nameref{Spell:IrresistibleDance}: Forces subject to dance.
 \item[9] \nameref{Spell:Starfall}*: Brings down a shower of Moon Bolts.
\end{list}

\subsection{New Cleric Spells}
\subsubsection{Death Domain}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item[7] \nameref{Spell:CorpseExplosion}*: Cause a recently dead creature to explode.
\end{list}
\subsubsection{Sun Domain}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item[4] \nameref{Spell:OrbOfLight}*: Orb deals blinds and deals damage to a creature.
\end{list}
\subsubsection{War Domain}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item[8] \nameref{Spell:BladeStorm}*: Circle of blades of force damages and stuns your enemies.
\end{list}



\subsection{New Sorcerer/Wizard Spells}
\subsubsection{1st-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:EldritchOrb}*: Create an orb of energy in your hand that you can throw or attack with in melee.
\end{list}

\subsubsection{4th-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:FeedbackOrb}*: Orb burns off spell points, dealing damage.
\end{list}


\subsection{Dread Knight Spell List}
\subsubsection{1st-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Bane}: Enemies take -1 on attack rolls and saves against fear.
\item \nameref{Spell:Blackfire}*: Fires shed light for you only.
\item \nameref{Spell:CorruptWeapon}: Weapon bypasses the defenses of good foes.
\item \nameref{Spell:CursedBlade}*: Wounds caused by weapon refuse to heal.
\item \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item \nameref{Spell:DisguiseSelf}: Changes your appearance.
\item \nameref{Spell:EldritchOrb}*: Create an orb of energy in your hand that you can throw or attack with in melee.
\item \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
\item \nameref{Spell:Fear}: One creature flees for 1d4 rounds.
\item \nameref{Spell:Hexenstrike}*: Deal additional damage to Cursed target.
\item \nameref{Spell:HideousLaughter}: Subject loses actions for 1 round/level.
\item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
\item \nameref{Spell:Mount}: Summons magical riding horse for 2 hours/level.
\item \nameref{Spell:Sleep}: Puts 4 HD of creatures into magical slumber.
\item \nameref{Spell:UncannyAccuracy}*: Your underhanded attacks are surprisingly effective.
\end{list}
\subsubsection{2nd-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Blindness}: Negates one of the subject's senses.
\item \nameref{Spell:Darkvision}: See 30 ft. in total darkness.
\item \nameref{Spell:FalseLife}: Gain 1d10 temporary hp.
\item \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
\item \nameref{Spell:MirrorImage}: Creates decoy duplicates of you.
\item \nameref{Spell:Rage}: Subjects are thrown into a fit of anger, with various effects.
\item \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
\item \nameref{Spell:SeeInvisibility}: Reveals invisible creatures or objects.
\item \nameref{Spell:Suggestion}: Compels subject to follow stated course of action.
\item \nameref{Spell:TouchOfIdiocy}: Subject takes 1d6 points of Int, Wis, or Cha damage.
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\subsubsection{3rd-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
\item \nameref{Spell:KeenEdge}: Doubles normal weapon's threat range.
\item \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
\item \nameref{Spell:Nondetection}: Masks object or creature against scrying.
\item \nameref{Spell:NoxiousVapors}: Nauseating vapors, 1 round/level.
\item \nameref{Spell:Poison}: Creates a temporary batch of poison.
\item \nameref{Spell:RemoveCurse}: Frees object or person from curse.
\item \nameref{Spell:Slow}: One creature takes only one action/round, -1 to AC, reflex saves, and attack rolls.
\item \nameref{Spell:UnnaturalEdge}*: Critical hits by weapon become more dangerous.
\item \nameref{Spell:VampiricTouch}: Touch deals 3d6 damage; caster gains damage as hp.
\end{list}
\subsubsection{4th-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Contagion}: Infects subject with chosen disease.
\item \nameref{Spell:DetectScrying}: Alerts you of magical eavesdropping.
\item \nameref{Spell:DimensionDoor}: Teleports you short distance.
\item \nameref{Spell:DenialOfDeathsEmbrace}*: Subject cannot die from hit point damage.
\item \nameref{Spell:Enervation}: Subject gains 1d4 negative levels.
\item \nameref{Spell:PhantasmalKiller}: Fearsome illusion kills subject or renders it unconscious.
\end{list}
\subsubsection{5th-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:BalefulPolymorph}: Transforms subject into harmless animal.
\item \nameref{Spell:Dominate}: Controls humanoid telepathically.
\item \nameref{Spell:Feeblemind}: Subject's Int and Cha drop to 1.
\item \nameref{Spell:FormHorror}: Subject gains the form of a tentacled monstrosity.
\item \nameref{Spell:WidowmakerBlade}*: Melee weapon culls out the weak.
\item \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\end{list}
\subsubsection{6th-Level Dread Knight Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:CrushingOnsetOfAge}*: Subject ages, withers, and dies before your eyes.
\item \nameref{Spell:DeadlyFright}*: Humanoid dies of fright.
\item \nameref{Spell:DweomerBlockade}*: You cut a creature off from all magic.
\item \nameref{Spell:InexorableOnsetOfDeath}*: Creature gains one negative level per round until it dies.
\item \nameref{Spell:PersonalMindBlank}*: You are immune to scrying and mental effects.
\item \nameref{Spell:SpellKarma}*: Spells rebound back on subject.
\end{list}

\subsection{Spellbreaker Spell List}
\subsubsection{1st-Level Spellbreaker Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
  \item \nameref{Spell:ArcaneFlux}*: Causes spellcaster to lose concentration.
  \item \nameref{Spell:Bloodhound}*: Grants one creature the scent special ability.
  \item \nameref{Spell:DiscernSpellcaster}*: Reveals whether target creature is a spellcaster.
  \item \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
  \item \nameref{Spell:InsightfulStrikes}*: Your magical insight grants you vision enough into the future to strike more effectively.
  \item \nameref{Spell:MagicAura}: Alters object's magic aura.
  \item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
  \item \nameref{Spell:Shield}: Invisible disc gives +4 to AC.
  \item \nameref{Spell:TrueStrike}: +20 on your next attack roll.
  \item \nameref{Spell:WingedWeapon}*: Allows weapon to fly for one round.
\end{list}
\subsubsection{2nd-Level Spellbreaker Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
  \item \nameref{Spell:Resistance} : Grants a Resistance bonus on saving throws.
  \item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
  \item \nameref{Spell:Silence}: Negates sound in 20-ft. radius.
  \item \nameref{Spell:SwiftFly}*: Fly for a few moments.
  \item \nameref{Spell:SwiftHaste}*: Act with increased speed for a few moments.
  \item \nameref{Spell:SwiftSeeInvisibility}*: See the invisible for a few moments.
  \item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\subsubsection{3rd-Level Spellbreaker Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
  \item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
  \item \nameref{Spell:FeedbackOrb}*: Orb burns off spell points, dealing damage.
  \item \nameref{Spell:KeenEdge}: Doubles normal weapon's threat range.
  \item \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
  \item \nameref{Spell:Nondetection}: Masks object or creature against scrying.
  \item \nameref{Spell:Piggyback}*: Latch on to a creature as it teleports, retaining your relative position.
  \item \nameref{Spell:RemoveCurse}: Frees object or person from curse.
  \item \nameref{Spell:Roguespace}*: Allows you to completely dodge certain effects that allow a reflex save.
  \item \nameref{Spell:SuppressMagic}*: Renders willing spellcaster incapable of casting spells.
\end{list}
\subsubsection{4th-Level Spellbreaker Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
  \item \nameref{Spell:DetectScrying}: Alerts you of magical eavesdropping.
  \item \nameref{Spell:DimensionDoor}: Teleports you short distance.
  \item \nameref{Spell:DimensionalAnchor}: Bars extradimensional movement.
  \item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
  \item \nameref{Spell:GlobeOfInvulnerability}: Stops low-powered spell effects.
  \item \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
\end{list}
\subsubsection{5th-Level Spellbreaker Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
  \item \nameref{Spell:AntimagicField}: Negates magic within 10 ft.
  \item \nameref{Spell:DimensionalBarrier}*: Teleportation and interplanar travel are briefly blocked in your immediate vicinity.
  \item \nameref{Spell:Dismissal}: Forces a creature to return to native plane.
  \item \nameref{Spell:DweomerBlockade}*: You cut a creature off from all magic.
  \item \nameref{Spell:SpellResistance}: Subject gains SR 12 + level.
\end{list}