\section{End notes}
\subsection{Thanks}
Thanks go to 
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item Xzoltar @ Competitor Games, who gave the system its first playtesting and me extraordinary amounts of feedback
 \item Swooper @ GitP, who has found more wording inconsistencies and \LaTeX bugs than I'd like to admit
 \item Garryl @ GitP, who gave me the first full readthrough, and as a result about 30 inconsistencies in the text
 \item Seharvepernfan and eggs @ GitP, who have repeatedly showered me with feedback and praise
 \item The players in my current (\today, 2013) campaign, who have actually bothered with reading some of this crap
 \item and everyone else who has commented on the system and listened to me prattle on about it as it was coming up.
\end{list}
\subsection{Version history}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item January 13th, 2013. Beta 1.10c. Bug fixes and updates, mostly in prestige classes (Dragon Disciple, Eldritch Knight, Loremaster and Mystic Theurge). Length 308 pages.
 \item December 29th, 2012: Beta 1.10b. High elf race added, and racial descriptions expanded. Mystic Theurge class added. The project's source code is now available on \href{https://github.com/Ernir/VancianToPsionics}{Github}, licenced under GPL version 3. Length: 308 pages.
 \item December 25th, 2012: Beta 1.10. Circle magic and magic duels added, as well as a multitude of bug fixes, mostly thanks to Seharvepernfan. Polymorph subschool changed to allow spellcasting while morphed. Font changed from Computer Modern to Times, which resulted in further document shortening. Still working on my Spellbreaker (Anti-mage) class, which is not included. Length: 308 pages.
 \item May 17, 2012: Beta 1.09. The Adept class added. Magic rings have been added. Summon Monster has undergone a paradigm change, and is now split into many, many smaller spells. Further condensation w.r.t. vertical paragraph, item list and section spacing, length now 316 pages.
 \item January 26, 2012: Beta 1.08. The Ranger class and its spell list added. The Arcane Archer, Blackguard (including its spell list), Eldritch Knight, Heirophant and Loremaster prestige classes added. Stick figure drawings (by yours truly) added at random places in the document. The Sun domain added, completing the main list of SRD domains. Many magic items updated. The document has been changed to a two-column layout, and as a result, is now down to 315 pages.
 \item September 23, 2011: Beta 1.07. The Air, Animal, Destruction, Earth, Fire, Luck, Moon, Planes, Plant, Travel, Trickery, and Vermin domains added. The Cleric class is now complete. Length: 440 pages.
 \item August 21, 2011: Beta 1.06. The Bard class added! Knowledge and Protection domains added. A line of fluff has been added to nearly all spells. An example monster (the Ogre Mage) added. The gnome race updated to take into account the changes to its SLAs. Length: 389 pages.
 \item June 12, 2011: Beta 1.05a: More domains (Death, Healing, Strength and War) added.
 Also, I've been adding fluff to spells! Length: 356 pages.
 \item May 21, 2011: Beta 1.05: The Dragon Disciple class added. Cantrips are back in. The first few domains, the alignment domains and the Magic domain, have been added.
 More spells creeping in, several minor errors fixed. Length: 338 pages.
 \item May 4, 2011: Beta 1.04. Cleric class added, although the domains are still missing.
 Assassin class added. The Sorcerer given the Wild Magic class feature. Work on Cleric spells and domains continues.
 Length: 310 pages.
 \item April 24, 2011: Beta 1.03. Paladin class added! Since the project now includes a divine class, project name changed to ``From Vancian to Psionic''
 (from ``From Arcane to Psionic''). A few more wording errors fixed. Length: 288 pages.
 \item April 17, 2011: Beta 1.02. Bug fix release, thanks to Garryl.
 \item April 13, 2011: Beta 1.01. Sorcerer class added! Wizard class slightly changed w.r.t. SP/day in response to the Sorcerer. Heroism spell inconsistency fixed.
 Preperations for the inclusion of the Cleric class have begun.
 Length: 253 pages.
 \item April 5, 2011: Beta 1. Wizard spells of levels 6, 7, 8 and 9 included. The Archmage prestige class included.
 Base system more or less finalized. Polymorph subschool changed. The ``Minion'' type of spells created.
 Length: 249 pages.
 \item January 16th, 2011: Alpha 2. Includes the reinstatement of Familiars, Wizard spells of levels 3, 4, and 5, numerous typo fixes, and more magic items.
 Lots of cleanup with regards to formatting and typos. Length: 177 pages.
 \item December 8th, 2010: Alpha 1. Includes the base system, the Wizard class, Wizard spells of levels 1 and 2, SRD feats,
 and the most basic magic items. Length: 99 pages.
 \item December 3rd, 2010: The project begins.
\end{list}
\subsection{Contact Info}
Problems, questions and concerns can be sent to
\href{mailto:e.ernir@gmail.com}{e.ernir@gmail.com}, or posted publicly at \href{http://forum.faxcelestis.net/viewtopic.php?f=1&t=186&sid=8991c93e2a863857ec84c4674df8481b}{Competitor Games}
or \href{http://www.giantitp.com/forums/showthread.php?t=194002}{Giant in the Playground}.
\subsection{OGL}
This document is made with material from the \href{http://www.wizards.com/default.asp?x=d20/article/srd35}{d20 srd},
in accordance with the Open Game License that follows.
\subsubsection{OPEN GAME LICENSE Version 1.0a}
\label{sec:OGL}
\small
The following text is the property of Wizards of the Coast, Inc. and is Copyright 2000 Wizards of the Coast, Inc ("Wizards"). All Rights Reserved.

\begin{enumerate}\item Definitions: 
\begin{enumerate}
 \item "Contributors" means the copyright and/or trademark owners who have contributed Open Game Content;
 \item "Derivative Material" means copyrighted material including derivative works and translations (including into other computer languages), potation, modification, correction, addition, extension, upgrade, improvement, compilation, abridgment or other form in which an existing work may be recast, transformed or adapted;
 \item "Distribute" means to reproduce, license, rent, lease, sell, broadcast, publicly display, transmit or otherwise distribute; 
 \item "Open Game Content" means the game mechanic and includes the methods, procedures, processes and routines to the extent such content does not embody the Product Identity and is an enhancement over the prior art and any additional content clearly identified as Open Game Content by the Contributor, and means any work covered by this License, including translations and derivative works under copyright law, but specifically excludes Product Identity.
 \item "Product Identity" means product and product line names, logos and identifying marks including trade dress; artifacts; creatures characters; stories, storylines, plots, thematic elements, dialogue, incidents, language, artwork, symbols, designs, depictions, likenesses, formats, poses, concepts, themes and graphic, photographic and other visual or audio representations; names and descriptions of characters, spells, enchantments, personalities, teams, personas, likenesses and special abilities; places, locations, environments, creatures, equipment, magical or supernatural abilities or effects, logos, symbols, or graphic designs; and any other trademark or registered trademark clearly identified as Product identity by the owner of the Product Identity, and which specifically excludes the Open Game Content;
 \item "Trademark" means the logos, names, mark, sign, motto, designs that are used by a Contributor to identify itself or its products or the associated products contributed to the Open Game License by the Contributor
 \item "Use", "Used" or "Using" means to use, Distribute, copy, edit, format, modify, translate and otherwise create Derivative Material of Open Game Content. 
 \item "You" or "Your" means the licensee in terms of this agreement.
\end{enumerate}
 \item \textbf{The License:} This License applies to any Open Game Content that contains a notice indicating that the Open Game Content may only be Used under and in terms of this License. You must affix such a notice to any Open Game Content that you Use. No terms may be added to or subtracted from this License except as described by the License itself. No other terms or conditions may be applied to any Open Game Content distributed using this License.
 \item \textbf{Offer and Acceptance:} By Using the Open Game Content You indicate Your acceptance of the terms of this License.
 \item \textbf{Grant and Consideration:} In consideration for agreeing to use this License, the Contributors grant You a perpetual, worldwide, royalty-free, non-exclusive license with the exact terms of this License to Use, the Open Game Content.
 \item \textbf{Representation of Authority to Contribute:} If You are contributing original material as Open Game Content, You represent that Your Contributions are Your original creation and/or You have sufficient rights to grant the rights conveyed by this License.
 \item \textbf{Notice of License Copyright:} You must update the COPYRIGHT NOTICE portion of this License to include the exact text of the COPYRIGHT NOTICE of any Open Game Content You are copying, modifying or distributing, and You must add the title, the copyright date, and the copyright holder's name to the COPYRIGHT NOTICE of any original Open Game Content you Distribute.
 \item \textbf{Use of Product Identity:} You agree not to Use any Product Identity, including as an indication as to compatibility, except as expressly licensed in another, independent Agreement with the owner of each element of that Product Identity. You agree not to indicate compatibility or co-adaptability with any Trademark or Registered Trademark in conjunction with a work containing Open Game Content except as expressly licensed in another, independent Agreement with the owner of such Trademark or Registered Trademark. The use of any Product Identity in Open Game Content does not constitute a challenge to the ownership of that Product Identity. The owner of any Product Identity used in Open Game Content shall retain all rights, title and interest in and to that Product Identity.
 \item \textbf{Identification:} If you distribute Open Game Content You must clearly indicate which portions of the work that you are distributing are Open Game Content.
 \item \textbf{Updating the License:} Wizards or its designated Agents may publish updated versions of this License. You may use any authorized version of this License to copy, modify and distribute any Open Game Content originally distributed under any version of this License.
 \item \textbf{Copy of this License:} You MUST include a copy of this License with every copy of the Open Game Content You Distribute.
 \item \textbf{Use of Contributor Credits:} You may not market or advertise the Open Game Content using the name of any Contributor unless You have written permission from the Contributor to do so.
 \item \textbf{Inability to Comply:} If it is impossible for You to comply with any of the terms of this License with respect to some or all of the Open Game Content due to statute, judicial order, or governmental regulation then You may not Use any Open Game Material so affected.
 \item \textbf{Termination:} This License will terminate automatically if You fail to comply with all terms herein and fail to cure such breach within 30 days of becoming aware of the breach. All sublicenses shall survive the termination of this License.
 \item \textbf{Reformation:} If any provision of this License is held to be unenforceable, such provision shall be reformed only to the extent necessary to make it enforceable.
 \item \textbf{COPYRIGHT NOTICE} Open Game License v 1.0 Copyright 2000, Wizards of the Coast, Inc.
\end{enumerate}
\subsection{Source code}
This is an \emph{open source} project, released under the \textbf{GNU General Public License, version 3} (GPL-3.0). The source (\LaTeX code and images) is accessible at \href{https://github.com/Ernir/VancianToPsionics}{Github}.
\subsubsection{GPL-3.0}
\input{LICENCE.tex}
