Seed: Energy
Evocation [Acid, Fire, Electricity, Cold, Or Sonic]
SP cost: 10
Components: V, S
Casting Time: 1 minute
Range: 300 ft. or touched creature or object of 2,000 lb. or less
Area: A bolt 5 ft. wide to 300 ft. long; or a 10-ft.-radius emanation; or a wall whose area is up to one 200-ft. square; or a sphere or hemi-sphere with a radius of up to 20 ft.
Duration: Instantaneous or 20 hours (see text)
Saving Throw: Reflex half
Spell Resistance: Yes

This seed uses whichever one of five energy types the caster chooses: acid, cold, electricity, fire, or sonic. 
The caster can cast the energy forth as a bolt, imbue an object with the energy, or create a freestanding manifestation of the energy. 
If the spell developed using the energy seed releases a bolt, that bolt instantaneously deals 20d6 points of damage of the appropriate energy type, and all in the bolt's area must make a Reflex save for half damage. 
The bolt begins at the caster's fingertips. 
%To imbue another creature with the ability to use an energy bolt as a spell-like ability at its option or when a particular condition is met, increase the Spellcraft DC by +25. 
The caster can also cause a creature or object to emanate the specific energy type out to a radius of 10 feet for 20 hours. 
The emanated energy deals 10d6 points of energy damage per round against unprotected creatures (the target creature is susceptible if not separately warded or otherwise resistant to the energy), and half that out to 20 feet. The wall deals this damage when it appears and in each round that a creature enters or remains in the area. In addition, the wall deals double (20d6) damage to any creature passing through it.

The caster can also use the energy seed to create a spell that carefully releases and balances the emanation of cold, electricity, and fire, creating specific weather effects for a period of 20 hours. 
Using the energy seed this way has a base SP cost of 13. 
The area extends to a two-mile-radius centered on the caster. Once the spell is cast, the weather takes 10 minutes to manifest. Ordinarily, a caster can't directly target a creature or object, though indirect effects are possible. This seed can create cold snaps, heat waves, thunderstorms, fogs, blizzards—even a tornado that moves randomly in the affected area. Creating targeted damaging effects requires an additional use of the energy seed.

Possible Augments: 
For a bolt, increase the seed's damage by 2d6 for every additional spell point you spend.
For a barrier, inscrease the seed's damage by 1d6 for every additional spell point you spend.