\section{Spell Lists}
\label{sec:Spells}
Spells marked with an asterisk (*) are spells that have no immediate magical ancestor in the d20 SRD.
This may be because the spell is based on a psionic counterpart, or because it is a new spell entirely.
\subsection{Bard Spells}
\label{sec:BardSpells}
\subsubsection{1st-Level Bard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Alarm}: Wards an area for 2 hours/level.
\item \nameref{Spell:Charm}: Makes one creature your friend.
\item \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
\item \nameref{Spell:ControlFall}: Objects or creatures fall slowly.
\item \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item \nameref{Spell:Daze}: Target creature loses next action.
\item \nameref{Spell:DetectMagic}: Reveals the presence, strength, and school of magical auras.
\item \nameref{Spell:DetectSecretDoors}: Become aware of all secret doors within your line of sight.
\item \nameref{Spell:DisguiseSelf}: Changes your appearance.
\item \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
\item \nameref{Spell:Fear}: One creature flees for 1d4 rounds.
\item \nameref{Spell:Grease}: Makes 10-ft. square or one object slippery.
\item \nameref{Spell:HideousLaughter}: Subject loses actions for 1 round/level.
\item \nameref{Spell:Identify}: Determines properties of magic item.
\item \nameref{Spell:Image}: Creates illusion of your design.
\item \nameref{Spell:MagicAura}: Alters object's magic aura.
\item \nameref{Spell:MentalLink}*: You forge a limited mental bond with another creature.
\item \nameref{Spell:Mount}: Summons magical riding horse for 2 hours/level.
\item \nameref{Spell:OpenClose}: Holds door shut or opens it.
\item \nameref{Spell:Repair}: Makes repairs on an object or construct.
\item \nameref{Spell:SummonInstrument}: Summons one instrument of the caster's choice.
\item \nameref{Spell:RandomAction}: Forces a creature to act randomly.
\item \nameref{Spell:RemoveFear}: Subject gains immunity to fear.
\item \nameref{Spell:Sleep}: Puts 4 HD of creatures into magical slumber.
\item \nameref{Spell:UncannyAccuracy}*: Your underhanded attacks are surprisingly effective.
\item \nameref{Spell:UnseenServant}: Invisible force obeys your commands.
\item \nameref{Spell:Ventriloquism}: Makes sounds appear out of nowhere.
\end{list}
\subsubsection{2nd-Level Bard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlterSelf}: Perform minor physical changes on yourself.
\item \nameref{Spell:AnimalMessenger}: Sends a Tiny animal to a specific place.
\item \nameref{Spell:Antipoison}: Stops poison from harming subject for 1 hour/level.
\item \nameref{Spell:Blindness}: Negates one of the subject's senses.
\item \nameref{Spell:Blur}: Attacks miss subject 20\% of the time.
\item \nameref{Spell:CalmEmotions}: Calms creatures, negating emotion effects.
\item \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
\item \nameref{Spell:Glitterdust}: Blinds creatures, outlines invisible creatures.
\item \nameref{Spell:Heroism}: Gives +2 bonus on attack rolls, saves, skill checks.
\item \nameref{Spell:HoldPerson}: Paralyzes one humanoid for 1 round/level.
\item \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
\item \nameref{Spell:Locate}: Senses direction toward object (specific or type).
\item \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item \nameref{Spell:MirrorImage}: Creates decoy duplicates of you.
\item \nameref{Spell:Pattern}: Twisting colors fascinate creatures.
%\item \nameref{Spell:Pyrotechnics}: Turns fire into blinding light or choking smoke.
\item \nameref{Spell:Rage}: Subjects are thrown into a fit of anger, with various effects.
\item \nameref{Spell:ReadThoughts}: Detect surface thoughts of creatures in range.
\item \nameref{Spell:SeeInvisibility}: Reveals invisible creatures or objects.
\item \nameref{Spell:Shatter}: Sonic vibration damages objects or crystalline creatures.
\item \nameref{Spell:Silence}: Negates sound in 20-ft. radius.
\item \nameref{Spell:SoundBurst}: Deals 1d8 sonic damage to subjects; may stun them.
\item \nameref{Spell:SummonSwarm}: Summons swarm of bats, rats, or spiders.
\item \nameref{Spell:Suggestion}: Compels subject to follow stated course of action.
\item \nameref{Spell:TwinBladeDance}: Stun opponents struck with a pair of weapons.
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\subsubsection{3rd-Level Bard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Blink}: You randomly vanish and reappear for 1 round/level.
\item \nameref{Spell:Clairvoyance}: See and hear a distant location.
\item \nameref{Spell:Confusion}: Subjects behave oddly for 1 round/level.
\item \nameref{Spell:CrushingDespair}: Subjects take -2 on attack rolls, damage rolls, saves, and checks.
\item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
\item \nameref{Spell:GaseousForm}: Subject becomes insubstantial and can fly slowly.
\item \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
\item \nameref{Spell:Glibness}: You gain a large bonus on Bluff checks.
\item \nameref{Spell:Haste}: One creature moves faster, +1 on attack rolls, AC, and Reflex saves.
\item \nameref{Spell:Nondetection}: Masks object or creature against scrying.
\item \nameref{Spell:Piggyback}*: Latch on to a creature as it teleports, retaining your relative position.
\item \nameref{Spell:RemoveCurse}: Frees object or person from curse.
\item \nameref{Spell:Scrying}: Spies on subject from a distance.
\item \nameref{Spell:SepiaSnakeSigil}: Creates text symbol that immobilizes reader.
\item \nameref{Spell:Slow}: One creature takes only one action/round, -1 to AC, reflex saves, and attack rolls.
\item \nameref{Spell:TinyHut}: Creates shelter for ten creatures.
\end{list}
\subsubsection{4th-Level Bard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:DetectScrying}: Alerts you of magical eavesdropping.
 \item \nameref{Spell:DimensionDoor}: Teleports you short distance.
 \item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
 \item \nameref{Spell:HallucinatoryTerrain}: Makes one type of terrain appear like another.
 \item \nameref{Spell:ModifyMemory}: Changes 5 minutes of subject's memories.
 \item \nameref{Spell:RepelVermin}: Insects, spiders, and other vermin stay 10 ft. away.
 \item \nameref{Spell:ShadowConjuration}: Mimics certain conjurations.
 \item \nameref{Spell:Shout}: Deafens all within cone and deals 7d6 sonic damage.
\end{list}
\subsubsection{5th-Level Bard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Dream}: Contact or disturb sleeping creature.
\item \nameref{Spell:Dominate}: Controls humanoid telepathically.
\item \nameref{Spell:FalseVision}: Fools scrying with an illusion.
\item \nameref{Spell:LegendLore}: Lets you learn tales about a person, place, or thing.
\item \nameref{Spell:MindFog}: Subjects in fog suffer increasing penalties to Will saves and Wisdom checks.
\item \nameref{Spell:Mislead}: Turns you invisible and creates illusory double.
\item \nameref{Spell:ShadowEvocation}: Mimics certain Evocations.
\item \nameref{Spell:ShadowWalk}: Step into shadow to travel rapidly.
\item \nameref{Spell:SongOfDiscord}: Forces targets to attack each other.
\end{list}
\subsubsection{6th-Level Bard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AnimateObjects}: Objects attack your foes.
\item \nameref{Spell:Eyebite}: Target becomes panicked, sickened, and/or comatose, depending on HD.
\item \nameref{Spell:HeroesFeast}: Food for four creatures cures and grants combat bonuses and immunities.
\item \nameref{Spell:IrresistibleDance}: Forces subject to dance.
\item \nameref{Spell:ProgrammedImage}: Causes Image spell to be triggered by event.
\item \nameref{Spell:SympatheticVibration}: Deals 2d10 damage/round to freestanding structure.
\end{list}
\subsection{Cleric Domains and Spells}
\label{sec:ClericDomains}
\subsubsection{Cleric Spell List}
\label{Domain:General}
Spells on this list are accessible to any Cleric, regardless of their deity and alignment. This generic spell list does not have any granted powers associated with it.
\begin{list}{\labelitemi}{\leftmargin=1em}
  \item[1] \nameref{Spell:TouchOfVitality} \textbf{(Free for Clerics)}: Cures wounds with a touch.
  \item[1] \nameref{Spell:DetectMagic}: Reveals the presence, strength, and school of magical auras.
  \item[2] \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
  \item[2] \nameref{Spell:Augury}: Learns whether an action will be good or bad.
  \item[3] \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
  \item[5] \nameref{Spell:Commune}: Deity answers three yes-or-no questions.
  \item[9] \nameref{Spell:Miracle}: Channels divine energy to produce versatile effects.
\end{list}
\subsubsection{Air Domain}
\paragraph{Granted Powers}
\subparagraph{Driven Arrows (Su):} 
You can add the lower of your Cleric level and your Wisdom modifier to ranged weapon damage rolls (but not damage caused by ranged spells, spell-like abilities, or supernatural abilities) in place of your strength modifier, if doing so is advantageous to you. 
This is a supernatural ability that functions continuously.
\subparagraph{Shield of Air (Su):} 
Starting at Cleric level 3rd, you can expend your magical focus as an immediate action to deflect a ranged weapon attack made against you so that you take no damage from it. 
Ranged attacks generated by spell effects, as well as weapons that are travelling ethereally or are composed entirely of force can't be deflected.
\subparagraph{Wind Tunnel (Su):} 
Starting at Cleric level 5th, your ranged weapons are not hampered by conditions of severe wind, including magical wind such as the one generated by the \nameref{Spell:WindWall} spell. 
\subparagraph{Elemental Shape (Su):}
Starting at Cleric level 13th, whenever you cast a \nameref{Spell:FormElemental} on yourself to assume the form of an air elemental, 
the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting the spell.
\paragraph{Air Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:EntropicShield}: Ranged attacks against you have 20\% miss chance.
\item[1] \nameref{Spell:Fog}: Fog surrounds you.
\item[1] \nameref{Spell:SummonAerialBeast}: Summons an airborne creature.
\item[2] \nameref{Spell:GustOfWind}: Blows away and knocks down creatures.
\item[3] \nameref{Spell:CallLightning}: Calls down lightning from the sky to blast your enemies.
\item[3] \nameref{Spell:GaseousForm}: Subject becomes insubstantial and can fly slowly.
\item[3] \nameref{Spell:SleetStorm}: Sleet hampers vision and movement.
\item[3] \nameref{Spell:WindWall}: Deflects arrows, knocks down creatures, blocks gases.
\item[4] \nameref{Spell:AirWalk}: Subject treads on air as if solid (climb at 45-degree angle).
\item[4] \nameref{Spell:IceStorm}: Hail deals 5d6 damage in cylinder 40 ft. across.
\item[4] \nameref{Spell:SummonAirElemental}*: Summons an elemental to do your bidding.
\item[5] \nameref{Spell:ControlWinds}: Change wind direction and speed.
\item[6] \nameref{Spell:ChainLightning}: 1d6/level damage to multiple subjects.
\item[7] \nameref{Spell:ControlWeather}: Changes weather in local area.
\item[7] \nameref{Spell:FormElemental}: Subject becomes a living creature of the elements.
\item[8] \nameref{Spell:Whirlwind}: Cyclone deals damage and can pick up creatures.
\item[9] \nameref{Spell:StormOfVengeance}: Storm rains acid, lightning, and hail.
\end{list}
\subsubsection{Animal Domain}
\label{Domain:Animal}
\paragraph{Granted Powers}
You add Handle Animal, Knowledge (nature), and Ride to your list of Cleric class skills.
\subparagraph{Wild Empathy (Ex):}
You gain the \nameref{sec:WildEmpathy} ability, as a Ranger of a level equal to your Cleric level.
If you also have levels in Ranger, use your combined number of levels in Cleric and Ranger to determine your effective level for this ability.
\subparagraph{Wild Shape (Su):}
Starting at Cleric level 5th, whenever you cast a \nameref{Spell:FormAvian}, \nameref{Spell:FormCarnivore}, 
\nameref{Spell:FormFish} or \nameref{Spell:FormScout} on yourself, 
the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting one of the listed spells.
\paragraph{Animal Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:AlterAnimalsSize}: Animal changes size.
\item[1] \nameref{Spell:ConverseWithNature}: Communicate with animals and other unlikely creatures and objects.
% \item[1] \nameref{Spell:SummonMonster}: Calls extraplanar creature to fight for you.
\item[1] \nameref{Spell:SummonExoticBeast}: Summons a creature from the distant lands.
\item[1] \nameref{Spell:SummonForestPredator}: Summons a predator of the forests.
\item[1] \nameref{Spell:SummonReptile}: Summons a scaled creature.
\item[2] \nameref{Spell:AnimalMessenger}: Sends a Tiny animal to a specific place.
\item[2] \nameref{Spell:AnimalsMovement}: Grants additional movement capabilities.
\item[2] \nameref{Spell:HoldAnimal}: Paralyzes one animal for 1 round/level.
\item[3] \nameref{Spell:FormAvian}: Subject gains the form of a bird.
\item[3] \nameref{Spell:FormFish}: Subject gains the form of a water-dwelling creature.
\item[4] \nameref{Spell:FormCarnivore}: Subject gains the form of a dangerous beast.
\item[5] \nameref{Spell:Awaken}: Animal or tree gains human intellect.
\item[5] \nameref{Spell:BalefulPolymorph}: Transforms subject into harmless animal.
\item[7] \nameref{Spell:AnimalShapes}: One ally/level polymorphs into a different form.
\item[9] \nameref{Spell:Shapechange}: Transforms you into any creature whose form you know, and change forms once per round.
\end{list}
\subsubsection{Chaos Domain}
\paragraph{Granted Powers}
\subparagraph{Anarchic Shield (Ex):}
You gain damage reduction equal to one-half your Cleric level (minimum 1).
Your damage reduction is overcome by lawful-aligned weapons.

\subparagraph{Gift of Fate (Su):}
Starting at Cleric level 5th, you can expend your magical focus when making any single attack roll, skill check, ability check, or saving throw.
You roll your d20 twice when making the check, and use the better result.
You must decide whether or not to use it before you make the roll in question.
Using this ability does not take an action of its own, its activation is done as part of the activity that requires the roll.
You can use this ability once per day. At Cleric level 10th, and again at 15th level, you gain an additional use per day.

\subparagraph{Anarchic Strike (Ex):}
Starting at Cleric level 8th, any weapons you use are considered chaotic-aligned for the purpose of overcoming damage reduction.
\paragraph{Chaos Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[1] \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item[1] \nameref{Spell:RandomAction}: Forces a creature to act randomly.
\item[2] \nameref{Spell:HideousLaughter}: Subject loses actions for 1 round/level.
\item[2] \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item[2] \nameref{Spell:Shatter}: Sonic vibration damages objects or crystalline creatures.
\item[4] \nameref{Spell:FistOfTheDeity}: Smites creatures of opposing alignment.
\item[5] \nameref{Spell:Atonement}: Removes burden of misdeeds from subject.
\item[5] \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away.
\item[5] \nameref{Spell:Reincarnate}: Creates a new, random body for a deceased creature to inhabit.
\item[6] \nameref{Spell:AnimateObjects}: Objects attack your foes.
\item[7] \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\item[8] \nameref{Spell:AlignedAura}: Protects creatures, better against creatures of an opposing alignment.
\end{list}
\subsubsection{Death Domain}
\subparagraph{Class Skill:}
You add Intimidate to your list of Cleric class skills.
\paragraph{Granted Powers}
\subparagraph{Deathtouched Presence (Ex):}
You gain a +4 bonus on Intimidate checks against living creatures, and a +4 bonus on Diplomacy checks when dealing with intelligent undead creatures.
Mindless undead creatures never attack you without provocation. Unless you attack, touch, or cast a spell at a nearby mindless undead creature, it acts as if you weren't there.
This is an ability that functions continuously, requiring no activation.
\subparagraph{Leader of the Dead (Ex):}
Your Cleric levels count more when calculating the number of creatures you can control via spells with the [\nameref{sec:MinionSpells}] descriptor.
The number of HD of creatures you can control this way becomes (2 + your charisma modifier)$\times$(2$\times$ your Cleric level + your number of other HD), rather than (2 + your charisma modifier)$\times$(Your number of HD).
This is an ability that functions continuously, requiring no activation.
\subparagraph{Animation Mastery (Ex):}
Each week, you can ignore a total number of 5 $\times$ your Cleric level points of experience cost associated with casting the spells \nameref{Spell:AnimateDead} and \nameref{Spell:CreateUndead}. This is not cumulative, if you have not cast the spells sufficiently often (or not created powerful enough undead) to put you over your limit in any given week, the excess is wasted.
This ability does not require activation, it is used as part of casting one of the referenced spells.
\paragraph{Death Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Fear}: One creature flees for 1d4 rounds.
\item[1] \nameref{Spell:LastLaugh}*: Destroy yourself in an attempt to take your enemies with you.
\item[1] \nameref{Spell:RayOfEnfeeblement}: Ray inflicts a strength penalty of 1d6.
\item[2] \nameref{Spell:CommandUndead}: Undead creature obeys your commands.
\item[2] \nameref{Spell:DeathKnell}: Kill dying creature and gain 1d8 temporary hp, and +2 to Str and your key ability score.
\item[2] \nameref{Spell:GentleRepose}: Preserves one corpse.
\item[3] \nameref{Spell:AnimateDead}: Creates undead skeletons and zombies.
\item[3] \nameref{Spell:Contagion}: Infects subject with chosen disease.
\item[3] \nameref{Spell:SpeakWithDead}: Corpse answers three questions.
\item[4] \nameref{Spell:BalefulResurrection}*: Returns subject from the dead - mostly.
\item[4] \nameref{Spell:Blight}: Withers one plant or deals 1d6/level damage to plant creature.
\item[4] \nameref{Spell:DeathWard}: Grants immunity to death spells and negative energy effects.
\item[5] \nameref{Spell:SlayLiving}: Touch attack kills subject.
\item[6] \nameref{Spell:CreateUndead}: Creates ghouls, and more powerful creatures with augment.
\item[7] \nameref{Spell:FingerOfDeath}: Kills one subject.
\item[9] \nameref{Spell:SoulBind}: Traps dead soul to prevent resurrection.
\end{list}
\subsubsection{Destruction Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skill:} 
You add Knowledge (architecture and engineering) to your list of Cleric class skills.
\subparagraph{Smite (Su):}
In order to perform a Smite, you must expend your magical focus as part of making an attack.
The attack then gains a bonus on the attack roll equal to your Charisma modifier, and a bonus on the damage roll equal to your Cleric level.
You must decide whether or not to perform a Smite before making the the attack. 
If the attack misses, you still expend your magical focus.
This is a Supernatural ability, activated as part of making an attack.
\subparagraph{Bonus Feat:}
At Cleric level 4th, you gain the Improved Sunder feat, even if you do not meet the prerequisites.
\subparagraph{Effortless Destruction (Ex):}
Your spells and attacks ignore a number of points of hardness equal to twice your Cleric level.
\paragraph{Destruction Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Bleed}*: Bleeding deals 1d3 points of Constitution damage.
\item[1] \nameref{Spell:InflictWounds}: Deals 1d8 damage +1/level.
\item[2] \nameref{Spell:Shatter}: Sonic vibration damages objects or crystalline creatures.
\item[2] \nameref{Spell:SoundBurst}: Deals 1d8 sonic damage to subjects; may stun them.
\item[3] \nameref{Spell:CallLightning}: Calls down lightning from the sky to blast your enemies.
\item[3] \nameref{Spell:Contagion}: Infects subject with chosen disease.
\item[4] \nameref{Spell:RustingGrasp}: Your touch corrodes iron and alloys.
\item[5] \nameref{Spell:DisruptingWeapon}: Melee weapon destroys undead.
\item[5] \nameref{Spell:SlayLiving}: Touch attack kills subject.
\item[6] \nameref{Spell:Harm}: Deals 110 points of damage to target.
\item[6] \nameref{Spell:Disintegrate}: Makes one creature or object vanish.
\item[7] \nameref{Spell:Earthquake}: Intense tremor shakes 80-ft.-radius.
\item[8] \nameref{Spell:TransmuteToAcid}*: Transforms a 10' cube of solid matter into acid.
\item[9] \nameref{Spell:Implosion}: Kills one creature/round.
\end{list}
\subsubsection{Earth Domain}
\paragraph{Granted Powers}
\subparagraph{Hardened Weapons (Su):}
As a swift action, you can expend your magical focus to have any weapons you use bypass damage reduction and hardness as if they were made of adamantine for a number of rounds equal to your Cleric level.
\subparagraph{Earth's Gentle Embrace (Su):}
Starting at Cleric level 3rd, you never take penalties when moving through terrain that is difficult due to natural rock or earth formations (such as loose stone rubble or slippery mud). Vegetation and artificial terrain features still count as difficult terrain as normal.
In addition, whenever you fall on to a natural rock or earth surface, all falling damage you take is nonlethal damage.
\subparagraph{Meld into Stone (Su):}
Starting at Cleric level 5th, whenever you cast a \nameref{Spell:MeldIntoStone} spell on yourself, the spell's duration becomes 1 day per caster level, rather than the spell's normal duration.
This ability is activated as part of casting the spell.
\subparagraph{Elemental Shape (Su):}
Starting at Cleric level 13th, whenever you cast a \nameref{Spell:FormElemental} on yourself to assume the form of an earth elemental, 
the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting the spell.
\paragraph{Earth Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:ConverseWithNature}: Communicate with animals and other unlikely creatures and objects.
\item[1] \nameref{Spell:MagicStone}: Launches a magical stone, dealing 1d6+1 damage.
\item[2] \nameref{Spell:SoftenEarthAndStone}: Turns stone to clay or dirt to sand or mud.
\item[3] \nameref{Spell:MeldIntoStone}: Subject and its gear merge with stone.
\item[3] \nameref{Spell:MoldMaterial}: Sculpts material into any shape.
\item[3] \nameref{Spell:SummonEarthElemental}: Summons an elemental to do your bidding.
\item[4] \nameref{Spell:StepThroughEarth}*: Travel instantaneously through the ground.
\item[4] \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
\item[4] \nameref{Spell:SpikeStones}: Creatures in area take 4d8 damage, may be slowed.
\item[5] \nameref{Spell:CommuneWithNature}: Learn about terrain for 1 mile/level.
\item[5] \nameref{Spell:TransmuteRockAndMud}: Transforms two 10-ft. cubes per level.
\item[5] \nameref{Spell:WallOfStone}: Creates a stone wall that can be shaped.
\item[6] \nameref{Spell:MoveEarth}: Digs trenches and builds hills.
\item[7] \nameref{Spell:Earthquake}: Intense tremor shakes 80-ft.-radius.
\item[7] \nameref{Spell:FormElemental}: Subject becomes a living creature of the elements.
\item[8] \nameref{Spell:RepelMetalAndStone}: Pushes away metal and stone.
\item[8] \nameref{Spell:FormIronGolem}: Subject's body changes into a creature of living iron.
%\item[9] Elemental Swarm*: Summons multiple elementals.
\end{list}
\subsubsection{Evil Domain}
\paragraph{Granted Powers}
\subparagraph{Unholy Shield (Ex):} 
You gain damage reduction equal to one-half your Cleric level (minimum 1).
Your damage reduction is overcome by good-aligned weapons.
\subparagraph{Gift of Darkness (Su):}
Starting at Cleric level 5th, whenever you drop (usually by reducing it to -1 HP or below) 
a sentient (Int 3 or higher), living creature, score a critical hit, damage a cowering or helpless opponent, 
or cast a spell with the [Evil] descriptor, you can expend your magical focus to gain a +1 profane bonus on attack and damage rolls for one minute.
Using this ability does not take an action of its own, its activation is done as part of the activity that allowed you to use it.
At Cleric level 10th, the profane bonus increases to +2. At 15th level, it increases to +3, and at 20th level to +4.
\subparagraph{Unholy Strike (Ex):}
Starting at Cleric level 8th, any weapons you use are considered evil-aligned for the purpose of overcoming damage reduction.
\paragraph{Evil Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[1] \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item[1] \nameref{Spell:Fear}: One creature flees for 1d4 rounds.
\item[2] \nameref{Spell:Blindness}: Negates one of the subject's senses.
\item[2] \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
\item[2] \nameref{Spell:Desecrate}: Fills area with negative energy, making undead stronger.
\item[2] \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item[3] \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item[3] \nameref{Spell:Poison}: Creates a temporary batch of poison.
\item[4] \nameref{Spell:FistOfTheDeity}: Smites creatures of opposing alignment.
\item[5] \nameref{Spell:Atonement}: Removes burden of misdeeds from subject.
\item[5] \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away.
\item[6] \nameref{Spell:CreateUndead}: Creates ghouls, and more powerful creatures with augment.
\item[7] \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\item[8] \nameref{Spell:AlignedAura}: Protects creatures, better against creatures of an opposing alignment.
%\item[9] \nameref{Spell:WailOfTheBanshee}: Kills multiple creatures.
\end{list}
\subsubsection{Fire Domain}
\paragraph{Granted Powers}
\subparagraph{Friendly Fire (Su):}
You gain resistance to fire equal to twice your Cleric level. This is a supernatural ability that functions continuously.
\subparagraph{Combust (Su):}
As a standard action, you can set an unattended object within 30' on fire, or deal 1d3 points of fire damage to a target within 30' by succeeding on a ranged touch attack against it.
\subparagraph{Divine Fire (Su):} 
Starting at Cleric level 5th, you can change $1/4$ of the fire damage you deal with spells that appear on the Fire domain list into divine damage, which is not subject to fire resistance or other protections from fire.
At 10th level, the ratio of damage so converted rises to $1/2$, and at 15th level to $3/4$.
This is a supernatural ability that is activated as part of casting each spell in question.
You can choose to not activate it (to deal more damage to a creature with the cold subtype, for example).
\subparagraph{Elemental Shape (Su):}
Starting at Cleric level 13th, whenever you cast a \nameref{Spell:FormElemental} on yourself to assume the form of a fire elemental, 
the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting the spell.
\paragraph{Fire Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:FaerieFire}: Outlines subjects with light, canceling blur, concealment, and the like.
\item[1] \nameref{Spell:Light}: Causes object to shine like a torch.
\item[1] \nameref{Spell:ProduceFlame}: Create a fire in your hand that you can throw or attack with in melee.
\item[2] \nameref{Spell:FlameBlade}: Creates a weapon of pure fire.
\item[2] \nameref{Spell:FlamingSphere}: Creates rolling ball of fire, 2d6 damage, lasts 1 round/level.
\item[2] \nameref{Spell:HeatChillMetal}: Makes metal extremely hot or extremely cold, damaging those who touch it.
\item[2] \nameref{Spell:Pyrotechnics}: Turns fire into blinding light or choking smoke.
\item[3] \nameref{Spell:SummonFireElemental}: Summons an elemental to do your bidding.
\item[4] \nameref{Spell:AuraOfFire}: Enemies within range take damage, more if they attack you.
\item[4] \nameref{Spell:FlameStrike}: Smite foes with divine fire, knocking them down and dealing 7d6 damage.
\item[4] \nameref{Spell:WallOfFire}: Deals 2d4 fire damage out to 10 ft. Passing through wall deals 7d6 damage.
\item[6] \nameref{Spell:DeadlyFog}: Add elemental component to fog, causing it to deal damage.
\item[6] \nameref{Spell:FireSeeds}: Acorns and berries become grenades and bombs.
\item[7] \nameref{Spell:FireStorm}: Deals 13d6 fire damage.
\item[7] \nameref{Spell:FormElemental}: Subject becomes a living creature of the elements.
\item[9] \nameref{Spell:Soulfire}*: Links your soul to that of another creature, at great peril to both of you.
\end{list}
\subsubsection{Good Domain}
\paragraph{Granted Powers}
\subparagraph{Holy Shield (Ex):}You gain damage reduction equal to one-half your Cleric level (minimum 1).
Your damage reduction is overcome by evil-aligned weapons.

\subparagraph{Gift of Compassion (Su):}
Starting at Cleric level 5th, whenever you stabilize a dying creature, take damage due to a \nameref{Spell:ShieldOther} spell you have cast, 
use the aid another action, or cast a spell with the [Good] descriptor or one that heals another creature's hit point damage, 
you can expend your magical focus to gain a +1 sacred bonus on attack and damage rolls for one minute.
Using this ability does not take an action of its own, its activation is done as part of the activity that allowed you to use it.
At Cleric level 10th, the sacred bonus increases to +2. At 15th level, it increases to +3, and at 20th level to +4.

\subparagraph{Holy Strike (Ex):}
Starting at Cleric level 8th, any weapons you use are considered good-aligned for the purpose of overcoming damage reduction.
\paragraph{Good Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[1] \nameref{Spell:Bless}: Allies gain +1 on attack rolls and +1 on saves against fear.
\item[1] \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item[2] \nameref{Spell:Aid}: +1 on attack rolls, +1 on saves against fear, 1d8 temporary hp +1/level.
\item[2] \nameref{Spell:Consecrate}: Fills area with positive energy, making undead weaker.
\item[2] \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item[2] \nameref{Spell:ShieldOther}: You take half of subject's damage.
\item[4] \nameref{Spell:FistOfTheDeity}: Smites creatures of opposing alignment.
\item[5] \nameref{Spell:Atonement}: Removes burden of misdeeds from subject.
\item[5] \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away
\item[6] \nameref{Spell:BladeBarrier}: Wall of blades deals 11d6 damage.
\item[7] \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\item[8] \nameref{Spell:AlignedAura}: Protects creatures, better against creatures of an opposing alignment.
\end{list}
\subsubsection{Healing Domain}
\paragraph{Granted Powers}
\subparagraph{Healer's Talents (Sp):}
You can use the following spells as spell-like abilities a combined number of times per day equal to your Wisdom modifier if you have the required number of ranks in the Heal skill, as indicated for each spell in question:
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \emph{6 ranks:} \nameref{Spell:RemoveFear}
 \item \emph{8 ranks:} \nameref{Spell:RemoveParalysis}
 \item \emph{10 ranks:} \nameref{Spell:RemoveBlindnessDeafness}
 \item \emph{10 ranks:} \nameref{Spell:RemoveDisease}
 \item \emph{10 ranks:} \nameref{Spell:RemoveCurse}
\end{list}
Your caster level for these spell-like abilities is equal to your character level.
\subparagraph{Positive Energy Infused Spellcasting (Su):}
Starting at Cleric level 6th, whenever you cast a divine spell, you can expend your magical focus to grant any one creature affected by the spell temporary hit points equal to your Cleric level. 
At Cleric level 12th, all creatures affected by your divine spells gain this benefit when you expend your magical focus.
Temporary hit points do not stack.
This is a supernatural ability whose activation is subsumed in casting the spell in question.
\subparagraph{Deathwatch (Su):}
You can determine the condition of all creatures within 30' of which you are aware. You instantly know whether each creature within the area is dead, near death (alive, with less than 1/4 of its hit points remaining), wounded (alive with less than 1/2 of its hit points remaining), lightly wounded (alive with less than 3/4 of its hit points remaining) or in good health (alive with more than 3/4 of its hit points remaining).
You also know if a creature is undead, or neither alive nor dead (such as a construct). You cannot learn the health of such creatures.
This is a supernatural ability that functions continuously, requiring no activation.
\paragraph{Healing Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item[1] \nameref{Spell:LifeLink}: Monitors status and position of allies.
\item[1] \nameref{Spell:RemoveFear}: Subject gains immunity to fear.
\item[2] \nameref{Spell:Antipoison}: Stops poison from harming subject for 1 hour/level.
\item[2] \nameref{Spell:RemoveParalysis}: Frees one creature from the effects of paralysis.
\item[2] \nameref{Spell:Restoration}: Dispels magical ability penalty or repairs 1d4 ability damage.
\item[3] \nameref{Spell:RemoveBlindnessDeafness}: Cures normal or magical conditions impeding senses.
\item[3] \nameref{Spell:RemoveCurse}: Frees object or person from curse.
\item[3] \nameref{Spell:RemoveDisease}: Cures all diseases affecting subject.
\item[5] \nameref{Spell:RaiseDead}: Brings a creature back from the dead.
\item[6] \nameref{Spell:Heal}: Cures great amounts of of damage, all diseases and mental conditions.
\item[7] \nameref{Spell:Regenerate}: Subject's severed limbs grow back, grants fast healing.
\end{list}
\subsubsection{Knowledge Domain}
\label{Domain:Knowledge}
\paragraph{Granted Powers}
\subparagraph{Class Skills:}
Add all Knowledge skills to your list of Cleric class skills.
\subparagraph{Lore (Ex):}
Thanks to long hours of study, you have a wide range of stray knowledge. This ability is identical to the \nameref{sec:Bard}'s Bardic Knowledge class feature, using your Cleric level in place of the Bard level. This counts as Bardic Knowledge for all purposes, including those of prerequisites. If you have Bard levels, you do not use the abilities separately, but your Cleric and Bard levels stack for purposes of determining your bonus on the check.
\subparagraph{Applied Knowledge (Ex):}
Starting at Cleric level 4th, whenever you fight a creature, you may make a knowledge check as appropriate to its type (Arcana for dragons, Local for humanoids, and so on).
This check has a DC equal to the one required to identify monsters and their special powers or vulnerabilities (10 + the monster's HD), but it is separate from that check (if you choose to also roll it).
If the check succeeds, you gain a +1 insight bonus on attack and damage rolls against that creature for the remainder of the fight.
If the check fails, you gain no bonus and may not try again.
Check separately for each creature type involved in the fight.
You must be aware of the creature you are fighting in order to roll this check.
You do not have to roll all checks at the start of the combat (although it is advantageous to do so as soon as you become aware of your combatants), you may, for example, roll again if creatures of a new type join the combat later on.

At Cleric level 8th, the insight bonus increases to +2, at 12th level it increases to +3, to +4 at 16th level, and +5 at 20th level.
\subparagraph{Gift of Knowledge (Su):}
Starting at Cleric level 5th, you can expend your magical focus when making any single Knowledge check.
You roll your d20 twice when making the check, and use the better result.
You must decide whether or not to use it before you make the roll in question.
Using this ability does not take an action of its own any more than rolling a Knowledge check usually does.
You can use this ability once per day. At Cleric level 10th, and again at 15th level, you gain an additional use per day.
\paragraph{Knowledge Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:DetectSecretDoors}: Become aware of all secret doors within your line of sight.
\item[1] \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item[1] \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
\item[2] \nameref{Spell:Clairvoyance}: See and hear a distant location.
\item[2] \nameref{Spell:Locate}: Senses direction toward object (specific or type).
\item[2] \nameref{Spell:ReadThoughts}: Detect surface thoughts of creatures in range.
\item[2] \nameref{Spell:TrapIntuition}: Notice and disable traps as a rogue does.
\item[4] \nameref{Spell:Scrying}: Spies on subject from a distance.
\item[4] \nameref{Spell:Sending}: Delivers short message anywhere, instantly.
\item[5] \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\item[6] \nameref{Spell:LegendLore}: Lets you learn tales about a person, place, or thing.
\item[8] \nameref{Spell:AbsoluteRevelation}: Reveals exact location of creature or object.
\item[8] \nameref{Spell:MomentOfPrescience}: You gain insight bonus on single attack roll, check, or save.
\item[9] \nameref{Spell:Foresight}: ``Sixth sense`` warns of impending danger.
\end{list}
\subsubsection{Law Domain}
\paragraph{Granted Powers}
\subparagraph{Axiomatic Shield (Ex):}
You gain damage reduction equal to one-half your Cleric level (minimum 1).
Your damage reduction is overcome by chaotic-aligned weapons.

\subparagraph{Gift of Order (Su):}
Starting at Cleric level 5th, you can expend your magical focus to ''take 12`` on a single attack roll, skill check, ability check, or saving throw.
Instead of rolling a d20 for the check, calculate your result as if you had rolled a 12. 
You can use this ability even under duress.
You must decide whether or not to use it before you make the roll in question.
Using this ability does not take an action of its own, its activation is done as part of the activity that requires the roll.
You can use this ability once per day. At Cleric level 10th, and again at 15th level, you gain an additional use per day.
\subparagraph{Axiomatic Strike (Ex):}
Starting at Cleric level 8th, any weapons you use are considered lawful-aligned for the purpose of overcoming damage reduction.
\paragraph{Law Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Command}: One subject obeys selected command for 1 round.
\item[1] \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[1] \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item[2] \nameref{Spell:CalmEmotions}: Calms creatures, negating emotion effects.
\item[2] \nameref{Spell:HoldPerson}: Paralyzes one humanoid for 1 round/level.
\item[2] \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item[2] \nameref{Spell:ZoneOfTruth}: Subjects within field find it extremely hard to lie.
\item[4] \nameref{Spell:FistOfTheDeity}: Smites creatures of opposing alignment.
\item[4] \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
\item[5] \nameref{Spell:Atonement}: Removes burden of misdeeds from subject. 
\item[5] \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away
\item[5] \nameref{Spell:MarkOfJustice}: Designates action that will trigger curse on subject.
\item[7] \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\item[8] \nameref{Spell:AlignedAura}: Protects creatures, better against creatures of an opposing alignment.
\end{list}
\subsubsection{Luck Domain}
\paragraph{Granted Powers}
\subparagraph{Extraordinary Luck (Ex):}
You can expend your magical focus to reroll any single attack roll, skill check, ability check, or saving throw.
You must decide whether or not to use this ability after you have rolled the original check, but before the GM has announced the results of that roll.
You must abide by the results of the second roll, even if it is worse than the original roll.
You cannot use this ability again to reroll a second time (even if you have two magical focuses to expend and have uses of the ability remaining).
Using this ability does not take an action of its own, its activation is done as part of the activity that requires the roll.
You can use this ability once per day. At Cleric level 4th, and again at levels 8, 12, and 16, you gain an additional use per day.
\subparagraph{Implausible Resilience (Ex):} 
When dying due to your hit points being reduced to -1 or below, you have a 50\% chance of becoming stable each round rather than a 10\% chance.
\subparagraph{Implausible Avoidance (Su)}: 
Starting at 5th level, falling objects never hit you, effectively making you immune to damage from such objects. This includes damage from objects that are purposefully dropped on top of you (but not normal ranged attacks), as well as traps that deal damage by dropping objects (or roofs, or similar) on you. Even if you never take damage from falling objects, you can still be affected by secondary effects, such as by being buried under rubble. This is a supernatural ability that functions continuously.
\paragraph{Luck Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Bless}: Allies gain +1 on attack rolls and +1 on saves against fear.
\item[1] \nameref{Spell:EntropicShield}: Ranged attacks against you have 20\% miss chance.
\item[1] \nameref{Spell:TrueStrike}: +20 on your next attack roll.
\item[1] \nameref{Spell:DivineFavor}: You gain a luck bonus on attack and damage rolls.
\item[2] \nameref{Spell:Aid}: +1 on attack rolls, +1 on saves against fear, 1d8 temporary hp +1/level.
\item[3] \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item[3] \nameref{Spell:RemoveCurse}: Frees object or person from curse.
\item[4] \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
\item[6] \nameref{Spell:Mislead}: Turns you invisible and creates illusory double.
\item[7] \nameref{Spell:SpellTurning}: Reflect spells back at caster.
\item[8] \nameref{Spell:MomentOfPrescience}: You gain insight bonus on single attack roll, check, or save.
\item[9] \nameref{Spell:FortuneOfTheGods}*: Make all d20 rolls twice, and choose your preferred result.
\end{list}
\subsubsection{Magic Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skill:}
You add Use Magic Device to your list of Cleric class skills.
\subparagraph{Cantrips (Su):}
You gain the \nameref{sec:Cantrips} class feature, as a Wizard.

\subparagraph{Immediate Counterspelling (Su):} 
At fourth level, you gain the ability to counterspell by expending your magical focus as an immediate action.
You do not need to take the ready action in your previous round, the entire counterspell attempt is performed as an immediate action.
Counterspell attempts are otherwise handled normally (see \nameref{sec:Counterspells}).
You can use this ability once per day. At Cleric levels 8, 12 and 16, you gain an additional daily use of this ability.
\paragraph{Magic Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:MagicAura}: Alters object's magic aura.
\item[1] \nameref{Spell:MagicMissile}: Deal 1d4+1 damage, no save, no touch attack.
\item[1] \nameref{Spell:Identify}: Determines properties of magic item.
\item[2] \nameref{Spell:DweomerRip}*: Damages creatures with active magical effects on them.
\item[3] \nameref{Spell:InvisibilityPurge}: Suppresses invisibility within 5 ft./level.
\item[3] \nameref{Spell:GlyphOfWarding}: Inscription harms those who pass it.
\item[3] \nameref{Spell:SuppressMagic}*: Renders willing spellcaster incapable of casting spells.
\item[4] \nameref{Spell:ImbueWithSpellAbility}: Transfer spells to subject.
\item[5] \nameref{Spell:SpellResistance}: Subject gains SR 12 + level.
\item[6] \nameref{Spell:AntimagicField}: Negates magic within 10 ft.
\item[7] \nameref{Spell:SpellTurning}: Reflect spells back at caster.
\item[7] \nameref{Spell:LimitedWish}: Alters reality - within spell limits.
\item[9] \nameref{Spell:Disjunction}: Dispels magic, disenchants magic items.
\end{list}
\subsubsection[Moon Domain]{Moon Domain*}
\paragraph{Granted Powers}
\subparagraph{Class Skill:}
Add Hide to your list of Cleric class skills.
\subparagraph{Low-Light Vision:} You gain the low-light vision special quality. If you already have low-light vision, you gain superior low-light vision instead (quadruple the distance, instead of double).
\subparagraph{Hide in Plain Sight (Su):} Starting at Cleric level 12th, you can use the Hide skill even while being observed, as long as you are within the area of some sort of shadow.
This ability does not need any activation beyond making a hide check.
\subparagraph{Moonlight Weapons (Su):}
As a swift action, you can expend your magical focus to have any weapons you use bypass damage reduction as if they were made of silver for a number of rounds equal to your Cleric level.
\paragraph{Moon Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item[1] \nameref{Spell:FaerieFire}: Outlines subjects with light, canceling blur, concealment, and the like.
 \item[1] \nameref{Spell:Light}: Causes object to shine like a torch.
 \item[2] \nameref{Spell:MoonBolt}*: Blasts creature with silvery light, damaging and stunning it.
 \item[2] \nameref{Spell:Moonlust}*: You enchant a creature with visions of the moon, preventing it from acting.
 \item[2] \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
 \item[3] \nameref{Spell:CallOfTheMoon}*: Reveals lycanthropes as what they are.
 \item[3] \nameref{Spell:SummonNaturesAlly}: Summons a natural guardian to aid you.
 \item[3] \nameref{Spell:Wolfsbane}*: Deals debilitating damage to lycanthropes.
 \item[3] \nameref{Spell:Blink}: Subject randomly vanishes and reappears for 1 round/level.
 \item[4] \nameref{Spell:Confusion}: Subjects behave oddly for 1 round/level.
 \item[5] \nameref{Spell:Dream}: Contact or disturb sleeping creature.
 \item[6] \nameref{Spell:ShadowWalk}: Step into shadow to travel rapidly.
 \item[7] \nameref{Spell:CurseOfLycanthropy}*: You infect a creature with lycanthropy.
 \item[8] \nameref{Spell:IrresistibleDance}: Forces subject to dance.
 \item[9] \nameref{Spell:Starfall}*: Brings down a shower of Moon Bolts.
\end{list}
\subsubsection[Planes Domain]{Planes Domain*}
\paragraph{Granted Powers:}
\subparagraph{Class Skills:} You add the Speak Language skill for any language spoken by natives of planes other than the material plane to your list of Cleric class skills.
\subparagraph{Darkvision (Ex):} 
You gain the Darkvision special quality, out to 60'. 
\subparagraph{Outsider Assumption (Ex):}
Starting at Cleric level 4th, you no longer need to eat. At Cleric level 12th, you no longer need to sleep, although you must still rest to regain spell points, as before.
\subparagraph{Planar Attunement (Ex):}
Starting at Cleric level 7th, you can selectively ignore the alignment traits of any plane you visit (treating it as a mildly neutral-aligned plane instead).
\subparagraph{Planar Ward (Su):}
Starting at Cleric level 10th, you are constantly considered to be under the influence of an \nameref{Spell:AlignedProtection} spell, warding against one alignment opposite that of your own (for example, if you are a Lawful Good Cleric, you could choose to ward against Chaos or Evil), using your Cleric level as its caster level. A true neutral Cleric gains no benefit from this granted power.
You can activate or dismiss this effect as a free action. If you can select to ward against more than one alignment, you can choose to change the alignment each time you re-activate the ability.
The effect protects only yourself. You do not gain the benefit of the Aligned Protection's augment.
% \subparagraph{Planar Navigation (Ex):}
% Starting at Cleric level 10th, any \nameref{Spell:PlaneShift} spell you cast automatically gains the benefit of its augment, with no additional spell point expenditure on your behalf.

% Evil: Poison immunity, Telepathy, acid & cold res.
% Good: Petrification immunity, Tongues.
% Law: ???
% Chaos: Electricity Immunity.
% 
% Demon Traits
% Immunity to electricity and poison.
% Resistance to acid 10, cold 10, and fire 10.
% Summon (Sp): Many demons share the ability to summon others of their kind (the success chance and type of demon summoned are noted in each monster description). Demons are often reluctant to use this power until in obvious peril or extreme circumstances.
% Telepathy.
% 
% Devil Traits
% Immunity to fire and poison.
% Resistance to acid 10 and cold 10.
% See in Darkness (Su): Some devils can see perfectly in darkness of any kind, even that created by a deeper darkness spell.
% Summon (Sp): Some devils share the ability to summon others of their kind (the success chance and type of devils summoned are noted in each monster description).
% Telepathy.
% 
% Archon Traits
% Darkvision out to 60 feet and low-light vision.
% Aura of Menace (Su): A righteous aura surrounds archons that fight or get angry. Any hostile creature within a 20-foot radius of an archon must succeed on a Will save to resist its effects. The save DC varies with the type of archon, is Charisma-based, and includes a +2 racial bonus. Those who fail take a -2 penalty on attacks, AC, and saves for 24 hours or until they successfully hit the archon that generated the aura. A creature that has resisted or broken the effect cannot be affected again by the same archon's aura for 24 hours.
% Immunity to electricity and petrification.
% +4 racial bonus on saves against poison.
% Magic Circle against Evil (Su): A magic circle against evil effect always surrounds an archon (caster level equals the archon's Hit Dice). (The defensive benefits from the circle are not included in an archon's statistics block.)
% Teleport (Su): Archons can use greater teleport at will, as the spell (caster level 14th), except that the creature can transport only itself and up to 50 pounds of objects.
% Tongues (Su): All archons can speak with any creature that has a language, as though using a tongues spell (caster level 14th). This ability is always active.
% 
% Angel Traits
% Darkvision out to 60 feet and low-light vision.
% Immunity to acid, cold, and petrification.
% Resistance to electricity 10 and fire 10.
% +4 racial bonus on saves against poison.
% Protective Aura (Su): Against attacks made or effects created by evil creatures, this ability provides a +4 deflection bonus to AC and a +4 resistance bonus on saving throws to anyone within 20 feet of the angel. Otherwise, it functions as a magic circle against evil effect and a lesser globe of invulnerability, both with a radius of 20 feet (caster level equals angel's HD). This aura can be dispelled, but the angel can create it again as a free action on its next turn. (The defensive benefits from the circle are not included in an angel's statistics block.)
% Tongues (Su): All angels can speak with any creature that has a language, as though using a tongues spell (caster level equal to angel's Hit Dice). This ability is always active.
% 
% Eladrin Traits
% Immunities: Eladrins are immune to electricity and petrification.
% Energy Resistance (Ex): Eladrins have resistance to acid 10 and cold 10.
% Tongues (Su): Eladrins can speak with any creature that has a language, as though using a tongues spell cast by a 14th-level cleric.
% This ability is always active.
\subparagraph{Ascension (Ex):}
At Cleric level 20th, you are transformed into a creature of the planes.
You are forevermore treated as an outsider rather than as a humanoid (or whatever your creature type was) for the purpose of spells and magical effects.
Unlike other outsiders, you can choose to have spells affect you as if you were a member of you previous creature type (chosen when each individual spell in question is cast).
\paragraph{Planes Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:FreeStep}*: Teleports you a very short distance.
% \item[1] \nameref{Spell:SummonMonster}: Calls extraplanar creature to fight for you.
\item[2] \nameref{Spell:SummonDevil}: Summons a devil to fight for you.
\item[3] \nameref{Spell:AstralTrap}*: Temporarily transports a creature far away.
\item[3] \nameref{Spell:Piggyback}*: Latch on to a creature as it teleports, retaining your relative position.
\item[3] \nameref{Spell:SummonDemon}: Summons a demon to fight for you.
\item[4] \nameref{Spell:DimensionalAnchor}: Bars extradimensional movement.
\item[4] \nameref{Spell:Dismissal}: Forces a creature to return to native plane.
\item[4] \nameref{Spell:PlanarAlly}: Request aid from an extraplanar creature.
\item[4] \nameref{Spell:Sending}: Delivers short message anywhere, instantly.
\item[4] \nameref{Spell:SummonCelestial}: Summons a celestial to defend you.
\item[6] \nameref{Spell:FormCelestial}*: You assume the form of a majestic celestial.
\item[6] \nameref{Spell:FormFiend}*: You assume the form of a terrifying fiend.
\item[6] \nameref{Spell:Forbiddance}: Blocks planar travel, damages creatures of selected alignments.
\item[7] \nameref{Spell:PlaneShift}: As many as eight subjects travel to another plane.
\item[8] \nameref{Spell:DimensionalLock}: Teleportation and interplanar travel blocked for one day/level within an area.
\item[9] \nameref{Spell:Gate}: Connects two planes for travel or calling.
\end{list}
\subsubsection{Plant Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skill:}
Add Knowledge (nature) to your list of Cleric class skills.
\subparagraph{Woodland Stride (Ex):}
Starting at 2nd level, you may move through any sort of undergrowth (such as natural thorns, briars, overgrown areas, and similar terrain) at her normal speed and without taking damage or suffering any other impairment. However, thorns, briars, and overgrown areas that have been magically manipulated to impede motion still affect you.
\subparagraph{Trackless Step (Ex):}
Starting at 3rd level, a you leave no trail in natural surroundings and cannot be tracked. You may choose to leave a trail if so desired.
\subparagraph{Plant Venom Immunity (Ex):}
At 9th level, you gain immunity to all plant-based poison.
\subparagraph{Plant Shape (Su):}
Starting at Cleric level 9th, whenever you cast a \nameref{Spell:FormTreant} spell on yourself, the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting the spell.
\paragraph{Plant Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:ConverseWithNature}: Communicate with animals and other unlikely creatures and objects.
\item[1] \nameref{Spell:Entangle}: Plants entangle everyone in 20-ft.-radius.
\item[1] \nameref{Spell:Woodbolt}*: Creates a spear that flies at your enemies.
\item[1] \nameref{Spell:Shillelagh}: Touched bludgeoning weapon deals damage as if it were larger than it really is.
\item[2] \nameref{Spell:Barkskin}: Grants +2 enhancement to natural armor.
\item[2] \nameref{Spell:CommandNaturesAllies}: Sway the actions of one a elemental, fey, or plant creature.
\item[2] \nameref{Spell:FormPlant}: You look exactly like a plant for 1 hour/level.
\item[3] \nameref{Spell:PlantGrowth}: You encourage or inhibit the growth of plants in a large area.
\item[3] \nameref{Spell:SpikeGrowth}: Creatures in area take 4d8 damage, may be slowed.
\item[3] \nameref{Spell:SummonNaturesAlly}: Summons a natural guardian to aid you.
\item[5] \nameref{Spell:FormTreant}: Subject gains the form of a plant creature.
\item[5] \nameref{Spell:Awaken}: Animal or tree gains human intellect.
\item[5] \nameref{Spell:WallOfThorns}: Thorns damage anyone who tries to pass.
\item[6] \nameref{Spell:AnimatePlants}: One or more trees animate and fight for you.
\item[6] \nameref{Spell:Liveoak}: Changes an oak into a treant.
\item[6] \nameref{Spell:TransportViaPlants}: Move instantly from one plant to another of the same kind.
\item[6] \nameref{Spell:RepelWood}: Pushes away wooden objects.
\item[7] \nameref{Spell:TransmuteMetalAndWood}: Transmutes a metal item to wood, and back again.
\item[7] \nameref{Spell:ControlNaturesAllies}: You link with a natural creature and make it do as you command.
\item[9] \nameref{Spell:AwakenNaturesWrath}: Animates the natural world and causes it to attack intruders.
\end{list}
\subsubsection{Protection Domain}
\paragraph{Granted Powers}
\subparagraph{Aura of Protection (Su):}
You can expend your magical focus as an immediate action to grant every ally within 30' a +2 sacred bonus to AC (when you learn this domain, an Evil or Neutral Cleric may instead choose to grant a profane bonus. Once made, this choice cannot be changed).
This bonus lasts for five rounds.
At Cleric levels 6, 12, and 18, the sacred bonus increases by +1.
\subparagraph{Retributive Ward (Su):}
Starting at 5th level, whenever a creature other than you is attacked by a creature within your threatened space, you can expend your magical focus to make an attack of opportunity against the attacker (assuming you have at least one attack of opportunity remaining to you that round).
You expend your focus as part of making the attack of opportunity, no action is required.
% You can generate a protective ward as a supernatural ability. 
% Grant someone you touch a resistance bonus equal to your Cleric level on his or her next saving throw. 
% Activating this power is a standard action. 
% The protective ward is an abjuration effect with a duration of 1 hour that is usable once per day.
\paragraph{Protection Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item[1] \nameref{Spell:Sanctuary}: Opponents can't attack you, and you can't attack.
\item[1] \nameref{Spell:ShieldOfFaith}: Creates a magical field around a creature that deflects attacks.
\item[2] \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
\item[2] \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item[2] \nameref{Spell:ShieldOther}: You take half of subject's damage.
%\item[3] Protection from Energy: Absorb 12 points/level of damage from one kind of energy.
\item[4] \nameref{Spell:DeathWard}: Grants immunity to death spells and negative energy effects.
\item[4] \nameref{Spell:SpellImmunity}: Subject is immune to two spells of 4th level or below.
\item[4] \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
\item[5] \nameref{Spell:SpellResistance}: Subject gains SR 12 + level.
\item[6] \nameref{Spell:AntimagicField}: Negates magic within 10 ft.
\item[6] \nameref{Spell:AntilifeShell}: 10-ft. field hedges out living creatures.
\item[6] \nameref{Spell:WordOfRecall}: Teleports you back to designated place.
\item[8] \nameref{Spell:MindBlank}: Subject is immune to mental/emotional magic and scrying.
\item[9] \nameref{Spell:PrismaticSphere}: As prismatic wall, but surrounds on all sides.
\end{list}
\subsubsection{Strength Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skills:}
You add Climb, Jump, and Swim to your list of Cleric class skills.
\subparagraph{Feat of Strength (Su):}
You can expend your magical focus as part of making a strength check, strength-based skill check, or a grapple check to gain a bonus on the check equal to your Cleric level.
Using this ability does not take an action of its own, its activation is done as part of the activity that requires the roll.
%You can use this ability once per day. At Cleric levels 4, 8, 12 and 16, you gain an additional daily use of this ability.
\subparagraph{Bonus feats:}
At Cleric levels 2nd, 5th, 9th, 13th and 17th, you gain a bonus feat, selected from the following list:

Athletic, Diehard, Endurance, Great Fortitude, Improved Grapple, Improved Overrun, Improved Unarmed Strike, Run, Skill Focus (Any strength-based skill), Toughness, Trample.

You must meet all prerequisites for the feats, if any.
\paragraph{Strength Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:AlterSize}: Humanoid creature changes size.
\item[1] \nameref{Spell:SurgeOfStrength}*: Gain temporary strength and hit points.
\item[1] \nameref{Spell:Virtue}: Gain 5 temporary hit points.
\item[3] \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
\item[3] \nameref{Spell:ManeuveringHand}: Hand composed of force performs combat maneuvers.
\item[4] \nameref{Spell:HandOfForce}: Hand of force manipulates items.
\item[4] \nameref{Spell:SpellImmunity}: Subject is immune to two spells of 4th level or below.
\item[4] \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
\item[5] \nameref{Spell:RighteousMight}: Your size increases, and you gain combat bonuses.
\item[6] \nameref{Spell:HeroesFeast}: Food for four creatures cures and grants combat bonuses and immunities.
\item[6] \nameref{Spell:Juggernaut}*: Subject gains the ability to easily destroy objects in its path.
\item[9] \nameref{Spell:FormTitan}: The subject takes up the shape and abilities of a powerful outsider.
\end{list}
\subsubsection{Sun Domain}
\paragraph{Granted Powers}
\subparagraph{Greater Turning (Su):} 
If you have the \nameref{Feat:TurnUndead} feat, it deals 6 points of damage per Cleric level you have, and 1d6 points of damage for every non-Cleric hit die you have.
\subparagraph{Sun-blessed Sight (Ex):}
At Cleric level 3rd, you gain immunity to the conditions of being \emph{blinded} and \emph{dazzled}.
\subparagraph{Purifying Light (Su):}
Starting at Cleric level 5th, you can elect to imbue your light spells with purifying energy that harms certain creatures. At the start of your turn, any evil outsiders, undead creatures, and natives of the plane of shadow located within the bright light radius of a spell so imbued take damage equal to your Cleric level. Only spells with the light descriptor that continuously shed light can be imbued in this way. This ability is activated as part of casting the light spell in question.
\subparagraph{Power of the Sun (Su):}
Starting at Cleric level 7th, you can expend your magical focus as part of casting a spell in order to increase its save DC by 1.
At Cleric level 14th, it instead increases by 2, and by 3 at Cleric level 20th.
This ability can only be used in an area of direct, natural sunlight.
\paragraph{Sun Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item[1] \nameref{Spell:Light}: Causes object to shine like a torch.
\item[1] \nameref{Spell:SearingLight}: Ray scorches foul creatures.
\item[2] \nameref{Spell:BladeOfTheSun}*: Weapon shines with brilliant energy for one round.
\item[3] \nameref{Spell:InvisibilityPurge}: Suppresses invisibility within 5 ft./level.
\item[3] \nameref{Spell:PlantGrowth}: You encourage or inhibit the growth of plants in a large area.
\item[4] \nameref{Spell:AuraOfFire}: Enemies within range take damage, more if they attack you.
\item[4] \nameref{Spell:FlameStrike}: Smite foes with divine fire, knocking them down and dealing 7d6 damage.
\item[4] \nameref{Spell:RepellingLight}*: Globe of light keeps foul creatures at bay.
\item[5] \nameref{Spell:BodyOfLight}*: Turn subject into pure energy, removing some vulnerabilities.
\item[6] \nameref{Spell:FireSeeds}: Acorns and berries become grenades and bombs.
\item[7] \nameref{Spell:ControlWeather}: Changes weather in local area.
\item[8] \nameref{Spell:Sunburst}: Blinds creatures and deals damage, more to undead and oozes.
\item[9] \nameref{Spell:PrismaticSphere}: As prismatic wall, but surrounds on all sides.
\end{list}
\subsubsection{Travel Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skills:} 
You add Knowledge (Geography) and Survival to your list of Cleric class skills.
\subparagraph{Longstrider (Su):}
Whenever you cast an \nameref{Spell:ExpeditiousRetreat} spell on yourself as a standard action, the spell's duration changes to 1 hour per level rather than the spell's normal duration.
This is a supernatural ability activated as part of casting the spell in question.
\subparagraph{Efficient Travel (Su):}
You and a number of travelling companions up to your Wisdom modifier add your Cleric level to the number of miles you can move in one hour of overland travel.
This has a corresponding effect on the number of miles you can travel per day.
For example, if accompanied by a 5th level Cleric with the Travel domain, a group walking at a speed of 30' could cover 8 miles per hour of overland travel, rather than 3 miles, and 64 miles per day of overland travel, rather than 24 miles.

If travelling by mount, carriage, or similar assistance, apply this bonus speed to the means of transportation in question, rather than the group's walking speed.
\subparagraph{Safe Teleportation (Su):}
Starting at Cleric level 9th, you never suffer mishaps when casting the \nameref{Spell:Teleport} spell.
Reroll all instances of ``Mishap'' on the Teleportation table until another result is obtained.
This is a supernatural ability activated as part of casting the spell.
\paragraph{Travel Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:ControlFall}: Objects or creatures fall slowly.
\item[1] \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
\item[1] \nameref{Spell:FreeStep}*: Teleports you a very short distance.
\item[2] \nameref{Spell:Locate}: Senses direction toward object (specific or type).
\item[3] \nameref{Spell:Fly}: Subject flies at speed of 40 ft.
\item[3] \nameref{Spell:HelpingHand}: Ghostly hand leads subject to you.
\item[4] \nameref{Spell:DimensionDoor}: Teleports you short distance.
\item[4] \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
\item[5] \nameref{Spell:Teleport}: Instantly transports you as far as 100 miles/level.
\item[6] \nameref{Spell:TransportViaPlants}: Move instantly from one plant to another of the same kind.
\item[6] \nameref{Spell:WordOfRecall}: Teleports you back to designated place.
\item[7] \nameref{Spell:FreeRun}*: Boosts overland travel speed to miraculous levels.
\item[7] \nameref{Spell:PhaseDoor}: Creates an invisible passage through wood or stone.
\item[7] \nameref{Spell:ReverseGravity}: Objects and creatures fall in a direction other than down for one round.
\item[9] \nameref{Spell:AstralProjection}: Projects you and companions onto Astral Plane.
\end{list}
\subsubsection{Trickery Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skills:} Add Bluff, Disguise, and Hide to your list of Cleric class skills.
\subparagraph{Master of Diversion (Ex):}
You can create a diversion to hide or feint in combat as a move action, rather than as a standard action (see the Bluff and Hide skill descriptions, respectively). 
If you already have the ability to feint in combat as a move action, you can instead feint as a free action.
\subparagraph{Pass without Trace (Ex):}
Starting at Cleric level 3rd, you can move through any type of terrain and leave neither footprints nor scent. Tracking you is impossible. You may choose to leave a trail if so desired.
\subparagraph{Poison Use (Ex):}
Starting at Cleric level 6th, you never risk accidentally poisoning yourself when applying poison to a weapon or using a poisoned weapon.
\subparagraph{Camouflage (Ex):}
Starting at 13th level, you can use the Hide skill even without having cover or concealment.
\paragraph{Trickery Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item[1] \nameref{Spell:DisguiseSelf}: Changes your appearance.
\item[1] \nameref{Spell:MagicAura}: Alters object's magic aura.
\item[1] \nameref{Spell:ShroudTheWeakMind}: Prevents creatures with limited intelligence from perceiving warded subjects.
\item[2] \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
\item[2] \nameref{Spell:Silence}: Negates sound in 20-ft. radius.
\item[3] \nameref{Spell:Nondetection}: Masks object or creature against scrying.
\item[3] \nameref{Spell:Poison}: Creates a temporary batch of poison.
\item[4] \nameref{Spell:Confusion}: Subjects behave oddly for 1 round/level.
\item[5] \nameref{Spell:FalseVision}: Fools scrying with an illusion.
\item[6] \nameref{Spell:AnimateObjects}: Objects attack your foes.
\item[6] \nameref{Spell:Mislead} : Turns you invisible and creates illusory double.
\item[7] \nameref{Spell:Screen}: Illusion hides area from vision, scrying.
\item[9] \nameref{Spell:TimeStop}: You stop time momentarily.
\end{list}
\subsubsection[Vermin Domain]{Vermin Domain*}
\paragraph{Granted Powers}
\subparagraph{Friend of Vermin (Ex):}
Vermin never attack you without provocation. Unless you attack, touch, or cast a spell at a nearby vermin, it acts as if you weren't there.
This is an ability that functions continuously, requiring no activation.
\subparagraph{Lord of Flies (Ex):}
If you have ranks in the Handle Animal skill, you can use it to handle and train monstrous vermin as if they were animals.
For this purpose, treat the vermin as if they had an Intelligence score of 1.
\subparagraph{Vermin Shape (Su):}
Starting at Cleric level 7th, whenever you cast a \nameref{Spell:FormVermin} or \nameref{Spell:FormViper} on yourself, 
the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting one of the listed spells.
\subparagraph{Vermin Venom Immunity (Ex):}
At Cleric level 9th, you gain immunity to the poison attacks of vermin, and to all poisons derived from vermin.
\paragraph{Vermin Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:WebStrand}*: You entangle a foe in sticky goo.
\item[1] \nameref{Spell:SummonVermin}: Summons a monstrous vermin to aid you in battle.
\item[2] \nameref{Spell:Arachnophobia}*: Subject believes it is covered in spiders.
\item[2] \nameref{Spell:SummonSwarm}: Summons swarm of bats, rats, or spiders.
\item[2] \nameref{Spell:Web}: Creates sticky spiderwebs between two anchor points.
\item[3] \nameref{Spell:Poison}: Creates a temporary batch of poison.
\item[4] \nameref{Spell:FormVermin}: Subject gains the form of a vermin.
\item[4] \nameref{Spell:FormViper}: Subject gains the form of a snake.
\item[4] \nameref{Spell:GiantVermin}: Turns centipedes, scorpions, or spiders into giant vermin.
\item[4] \nameref{Spell:RepelVermin}: Insects, spiders, and other vermin stay 10 ft. away.
\item[5] \nameref{Spell:JellyfishSting}*: Slimy tentacle reaches out and paralyzes one victim.
\item[7] \nameref{Spell:CreepingDoom}: Fills subject's lungs with insects, placing it in mortal danger.
\item[9] \nameref{Spell:InsectPlague}: Swarm of locusts appears, devouring everything within an area.
\end{list}
\subsubsection{War Domain}
\paragraph{Granted Powers}
\subparagraph{Heavy Armor Proficiency:}
You are proficient in heavy armor. 
\subparagraph{Martial Devotion (Ex):}
You qualify for feats and prestige classes as if the Cleric class
had the good Base Attack Bonus progression (BAB = level), rather than the medium progression (BAB = $3/4$ level).

\subparagraph{Bonus feats:}
At Cleric level 4th, you gain the Weapon Focus feat with your deity's favored weapon as a bonus feat.
At Cleric level 8th, you gain the Weapon Specialization feat with your deity's favored weapon as a bonus feat, even if you do not meet the prerequisites.
At Cleric level 12th, you gain the Greater Weapon Focus feat with your deity's favored weapon as a bonus feat, even if you do not meet the prerequisites.
At Cleric level 16th, you gain the Greater Weapon Specialization feat with your deity's favored weapon as a bonus feat, even if you do not meet the prerequisites.
\paragraph{War Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:DivineFavor}: You gain a luck bonus on attack and damage rolls.
\item[1] \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
\item[2] \nameref{Spell:SpiritualWeapon}: Magic weapon attacks on its own.
\item[3] \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
\item[4] \nameref{Spell:DivinePower}: You gain attack bonus, +6 to Str, and 1 hp/level.
\item[4] \nameref{Spell:FlameStrike}: Smite foes with divine fire, knocking them down and dealing 7d6 damage.
\item[5] \nameref{Spell:RighteousMight}: Your size increases, and you gain combat bonuses.
\item[5] \nameref{Spell:WarriorsImpetus}*: Grants speed and strength to targeted creatures.
\item[6] \nameref{Spell:BladeBarrier}: Wall of blades deals 11d6 damage.
\item[7] \nameref{Spell:PowerWord}: Overwhelms the minds of lesser creatures with a single word of power.
\item[9] \nameref{Spell:ImmortalArmy}*: Grant virtual immortality to weaker creatures.
\end{list}
\subsubsection{Water Domain}
\paragraph{Granted Powers}
\subparagraph{Class Skill:} 
You add Swim to your list of Cleric class skills.
\subparagraph[Create Water]{Create Water (Su):}
\label{sec:CreateWater}
By expending your magical focus as a standard action, you can create up to two gallons of water per Cleric level. 
The water is wholesome and drinkable, just like clean rain water.

The water appears within 30'. Water can be created in an area as small as will actually contain the liquid, or in an area three times as large - possibly creating a downpour or filling many small receptacles.

Water weighs about 8 pounds per gallon. One cubic foot of water contains roughly 8 gallons and weighs about 60 pounds.

\subparagraph{Swim Speed:}
You gain a swim speed equal to your land speed.
You can then move through water at your speed without making Swim checks.
You gain a +8 racial bonus on any Swim check to perform a special action or avoid a hazard. 
You can always can choose to take 10 on a Swim check, even if distracted or endangered when swimming. 
You can use the run action while swimming, provided that you swim in a straight line.
\subparagraph[Water Breathing]{Water Breathing (Su):}
\label{sec:WaterBreathing}
Starting at Cleric level 5th, you gain the ability to breathe water as well as you breathe air. This allows you to speak (and provide verbal components to spells) as if you were breathing air.

If you already have the ability to breathe water, but not air, you instead gain the ability to breathe air (you become amphibious). If you are already amphibious, you gain no further benefits.

This is a supernatural ability that functions continuously.
\subparagraph{Embrace of the Deep (Su):}
Starting at Cleric level 10th, you can cause any creature within 30' to lose its ability to hold its breath while in water.
A successful Fortitude save (DC 10 + $1/2$ your Cleric level + your Wisdom modifier) negates the effect.
On a failed save the creature must, if submerged in water, immediately start making Constitution checks or start drowning\footnote{Rewriting the drowning rules is left as an exercise to the reader.}.
Creatures that do not need to breathe and creatures capable of breathing water are immune to this ability.
Using this ability is a mental free action.
You cannot force this ability upon the same creature more than once per round. 
You must have line of sight and line of effect to the creature in question. 
The creature remains unable to hold its breath until you dismiss the effect (another free action) or until it moves out of range.
Its ability to actually breathe is unaffected.
\subparagraph{Elemental Shape (Su):}
Starting at Cleric level 13th, whenever you cast a \nameref{Spell:FormElemental} on yourself to assume the form of a water elemental, 
the spell's duration becomes 1 hour per caster level, rather than the spell's normal duration.
This ability is activated as part of casting the spell.
\paragraph{Water Domain Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:FoodAndWater}: Purifies food and water so it is again fit for consumption.
\item[1] \nameref{Spell:Fog}: Fog surrounds you.
\item[1] \nameref{Spell:SummonAquaticCreature}: Summons a creature of the seas.
\item[2] \nameref{Spell:AlignWater}: Vial of water is imbued with the power of an alignment.
\item[2] \nameref{Spell:Squirt}*: Line of water deals nonlethal damage.
\item[3] \nameref{Spell:AnimalsMovement}: Grants additional movement capabilities.
\item[3] \nameref{Spell:SummonWaterElemental}: Summons an elemental to do your bidding.
\item[3] \nameref{Spell:WaterWalk}: Subjects tread on water as if solid.
\item[4] \nameref{Spell:IceStorm}: Hail deals 5d6 damage in cylinder 40 ft. across.
\item[4] \nameref{Spell:RustingGrasp}: Your touch corrodes iron and alloys.
\item[5] \nameref{Spell:ConeOfCold}: 9d6 points of energy damage in a cone, and all in area must save or be slowed.
\item[5] \nameref{Spell:ControlWater}: Raises or lowers bodies of water, or slows water elemental.
\item[6] \nameref{Spell:DeadlyFog}: Add elemental component to fog, causing it to deal damage.
\item[7] \nameref{Spell:ControlWeather}: Changes weather in local area.
\item[7] \nameref{Spell:FormElemental}: Subject becomes a living creature of the elements.
\item[8] \nameref{Spell:HorridWilting}: Desiccates nearby creatures.
%\item[9] Elemental Swarm*: Summons multiple elementals.
\end{list}
\subsection{Paladin Spells}
\subsubsection{1st-Level Paladin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item \nameref{Spell:ArmamentsOfFaith}*: Arms and armor are conjured directly on to your body.
\item \nameref{Spell:Bless}: Allies gain +1 on attack rolls and +1 on saves against fear.
\item \nameref{Spell:BlessWeapon}: Weapon strikes true against evil foes.
\item \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
\item \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item \nameref{Spell:TouchOfVitality} \textbf{(Free for Paladins)}: Cures wounds with a touch.
\item \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item \nameref{Spell:DetectUndead}: Reveals the presence and strength of undead creatures.
\item \nameref{Spell:DiscernAlignment}: Reveals the subject's alignment.
\item \nameref{Spell:DivineFavor}: You gain a luck bonus on attack and damage rolls.
\item \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item \nameref{Spell:Light}: Causes object to shine like a torch.
\item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
\item \nameref{Spell:TrueStrike}: +20 on your next attack roll.
%\item \nameref{Spell:ReadMagic}: Ease reading of magical text.
\item \nameref{Spell:RemoveFear}: Subject gains immunity to fear.
\item \nameref{Spell:SummonWeapon}*: Summons bonded weapon to your hand.
\item \nameref{Spell:SurgeOfStrength}*: Gain temporary strength and hit points.
\item \nameref{Spell:Virtue}: Gain 5 temporary hit points.
\end{list}
\subsubsection{2nd-Level Paladin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Aid}: +1 on attack rolls, +1 on saves against fear, 1d8 temporary hp +1/level.
\item \nameref{Spell:AlignWater}*: Vial of water is imbued with the power of an alignment.
\item \nameref{Spell:Antipoison}: Stops poison from harming subject for 1 hour/level.
\item \nameref{Spell:BladeOfTheSun}*: Weapon shines with brilliant energy for one round.
\item \nameref{Spell:DivineFootstep}*: Tread on air for one round.
\item \nameref{Spell:LionsCharge}*: You can make full attack in same round you charge.
\item \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
\item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item \nameref{Spell:Restoration}: Dispels magical ability penalty or repairs 1d4 ability damage.
\item \nameref{Spell:SearingBlade}*: Weapon deals 3d6 extra points of damage against undead and oozes, half that against others.
\item \nameref{Spell:ShieldOther}: You take half of subject's damage.
\item \nameref{Spell:ZoneOfTruth}: Subjects within field find it extremely hard to lie.
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\subsubsection{3rd-Level Paladin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:CelestialFlight}*: Subject sprouts wings and flies at speed of 40 ft.
 \item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
 \item \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
 \item \nameref{Spell:HealMount}: As Heal on your special mount.
 \item \nameref{Spell:KeenEdge}: Doubles normal weapon's threat range.
 \item \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
 \item \nameref{Spell:Piggyback}*: Latch on to a creature as it teleports, retaining your relative position.
 \item \nameref{Spell:RemoveBlindnessDeafness}: Cures normal or magical conditions impeding senses.
 \item \nameref{Spell:RemoveCurse}: Frees object or person from curse.
 \item \nameref{Spell:RemoveDisease}: Cures all diseases affecting subject.
\end{list}
\subsubsection{4th-Level Paladin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:BodyOfLight}*: Turn subject into pure energy, removing some vulnerabilities.
 \item \nameref{Spell:DeathWard}: Grants immunity to death spells and negative energy effects.
 \item \nameref{Spell:DimensionDoor}: Teleports you short distance.
 \item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
 \item \nameref{Spell:MarkOfJustice}: Designates action that will trigger curse on subject.
\end{list}
\subsubsection{5th-Level Paladin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:AlignedSword}: Weapon becomes +5, deals +2d6 damage against one alignment.
 \item \nameref{Spell:Atonement}: Removes burden of misdeeds from subject.
 \item \nameref{Spell:BanishingWeapon}*: Melee weapon banishes outsiders.
 \item \nameref{Spell:Commune}: Deity answers three yes-or-no questions.
 \item \nameref{Spell:DispelAlignment}: Protects against creatures of the chosen alignment, discharge to drive creature away.
 \item \nameref{Spell:DisruptingWeapon}: Melee weapon destroys undead.
 \item \nameref{Spell:MaceOfTheAstralDeva}*: Creature struck twice with weapon must save or be stunned.
 \item \nameref{Spell:RighteousMight}: Your size increases, and you gain combat bonuses.
 \item \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\end{list}
\subsubsection{6th-Level Paladin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
 \item \nameref{Spell:AssaultOfTheSevenFoldHeaven}*: Creature is subjected to an array of prismatic effects.
 \item \nameref{Spell:BowOfTheSolar}*: Creature must save or be destroyed.
 \item \nameref{Spell:FormCelestial}*: You assume the form of a majestic celestial.
 \item \nameref{Spell:Heal}: Cures great amounts of of damage, all diseases and mental conditions.
 \item \nameref{Spell:PersonalMindBlank}*: You are immune to scrying and mental effects.
 \item \nameref{Spell:PlaneShift}: As many as eight subjects travel to another plane.
 \item \nameref{Spell:WordOfGod}: Kills, paralyzes, hinders, or deafens subjects not of a selected alignment.
\end{list}
\subsection{Ranger Spells}
%2nd level: Arrow ignores armor (Brilliant Energy)
%2nd level: Arrow deals damage to creatures with spells
%3rd level: Arrow splits into many
%3rd level: Arrow deals ongoing damage
%4th level: Arrow paralyzes
%4th level: Arrow hits two targets
%4th level: Arrow deals strength damage
\subsubsection{1st-Level Ranger Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Alarm}: Wards an area for 2 hours/level.
\item \nameref{Spell:AlterAnimalsSize}: Animal changes size.
\item \nameref{Spell:AnimalMessenger}: Sends a Tiny animal to a specific place.
\item \nameref{Spell:AnimalsMovement}: Grants additional movement capabilities.
\item \nameref{Spell:Bloodhound}*: Grants one creature the scent special ability.
\item \nameref{Spell:ControlFall}: Objects or creatures fall slowly.
\item \nameref{Spell:CureWounds}: Cures 1d8 damage +1/level.
\item \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item \nameref{Spell:ElementalWeapons}*: Your weapons deal an additional 1d6 points of energy damage.
\item \nameref{Spell:Elfcloak}*: You blend in with your surroundings, making it easier to hide.
\item \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item \nameref{Spell:Entangle}: Plants entangle everyone in 20-ft.-radius.
\item \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
%Longstrider?
\item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
% \item Pass without Trace: One subject/level leaves no tracks.
\item \nameref{Spell:ShroudTheWeakMind}: Prevents creatures with limited intelligence from perceiving warded subjects.
\item \nameref{Spell:SummonAerialBeast}: Summons an airborne creature.
\item \nameref{Spell:SummonAquaticCreature}: Summons a creature of the seas.
\item \nameref{Spell:SummonExoticBeast}: Summons a creature from the distant lands.
\item \nameref{Spell:SummonForestPredator}: Summons a predator of the forests.
\item \nameref{Spell:SummonReptile}: Summons a scaled creature.
\item \nameref{Spell:TrueStrike}: +20 on your next attack roll.
\item \nameref{Spell:ConverseWithNature}: Communicate with animals and other unlikely creatures and objects.
%\item \nameref{Spell:SummonMonster}: Calls extraplanar creature to fight for you.
\end{list}.
\subsubsection{2nd-Level Ranger Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Antipoison}: Stops poison from harming subject for 1 hour/level.
\item \nameref{Spell:Barkskin}: Grants +2 enhancement to natural armor.
\item \nameref{Spell:CommandNaturesAllies}: Sway the actions of one a elemental, fey, or plant creature.
\item \nameref{Spell:Darkvision}: See 30 ft. in total darkness.
\item \nameref{Spell:FormPlant}: You look exactly like a plant for 1 hour/level.
\item \nameref{Spell:HoldAnimal}: Paralyzes one animal for 1 round/level.
\item \nameref{Spell:LionsCharge}*: You can make full attack in same round you charge.
\item \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
\item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item \nameref{Spell:SpikeGrowth}: Creatures in area take 4d8 damage, may be slowed.
\item \nameref{Spell:StunningArrow}*: Imbue a single projectile with the power to stun the creature it strikes.
\item \nameref{Spell:TwinBladeDance}*: Stun opponents struck with a pair of weapons.
\item \nameref{Spell:WindWall}: Deflects arrows, knocks down creatures, blocks gases.
\end{list}
\subsubsection{3rd-Level Ranger Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:BloodlettingArrow}*: Arrow deals constitution damage.
\item \nameref{Spell:FormAvian}: Subject gains the form of a bird.
\item \nameref{Spell:FormFish}: Subject gains the form of a water-dwelling creature.
\item \nameref{Spell:HawksFlight}*: Subject grows wings and flies at speed of 40 ft.
\item \nameref{Spell:HailOfArrows}*: Fire a ranged weapon at multiple targets within range.
\item \nameref{Spell:MagicVestment}: Armor or shield gains +2 enhancement bonus.
\item \nameref{Spell:Nondetection}: Masks object or creature against scrying.
\item \nameref{Spell:Locate}: Senses direction toward object (specific or type).
\item \nameref{Spell:PlantGrowth}: You encourage or inhibit the growth of plants in a large area.
\item \nameref{Spell:RemoveDisease}: Cures all diseases affecting subject.
\item \nameref{Spell:SummonNaturesAlly}: Summons a natural guardian to aid you.
\item \nameref{Spell:WaterWalk}: Subjects tread on water as if solid.
\end{list}
\subsubsection{4th-Level Ranger Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:CommuneWithNature}: Learn about terrain for 1 mile/level.
\item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
\item \nameref{Spell:FormCarnivore}: Subject gains the form of a dangerous beast.
\item \nameref{Spell:ParalyzingArrow}*: Imbue a single projectile with the power to paralyze the creature it strikes.
\item \nameref{Spell:RepelVermin}: Insects, spiders, and other vermin stay 10 ft. away.
\item \nameref{Spell:SeekerArrow}*: Missile fired ignores line of effect.
\item \nameref{Spell:StepThroughEarth}*: Travel instantaneously through the ground.
\item \nameref{Spell:ViciousWeapons}*: Melee weapons you wield deal constitution damage.
\end{list}
\subsubsection{5th-level Ranger Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AdaptBody}*: Your body automatically adapts to hostile environments.
\item \nameref{Spell:Awaken}: Animal or tree gains human intellect.
\item \nameref{Spell:ControlWinds}: Change wind direction and speed.
\item \nameref{Spell:BalefulPolymorph}: Transforms subject into harmless animal.
\item \nameref{Spell:FormTreant}: Subject gains the form of a plant creature.
\item \nameref{Spell:PhaseArrow}*: Arrow passes through the ethereal plane on its way to its target.
\item \nameref{Spell:WallOfThorns}: Thorns damage anyone who tries to pass.
\end{list}
\subsubsection{6th-level Ranger Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AnimatePlants}: One or more trees animate and fight for you.
\item \nameref{Spell:ArrowOfDeath}*: Imbue a single projectile with the power to instantly slay the creature it strikes.
\item \nameref{Spell:FreeRun}*: Boosts overland travel speed to miraculous levels.
\item \nameref{Spell:Liveoak}: Changes an oak into a treant.
\item \nameref{Spell:RepelWood}: Pushes away wooden objects.
\item \nameref{Spell:TransportViaPlants}: Move instantly from one plant to another of the same kind.
\end{list}
\subsection{Sorcerer/Wizard Spells}
\subsubsection{1st-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Alarm}: Wards an area for 2 hours/level.
\item \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item \nameref{Spell:ColorSpray}: Knocks unconscious, blinds, and/or stuns weak creatures.
\item \nameref{Spell:ControlFall}: Objects or creatures fall slowly.
\item \nameref{Spell:Daze}: Target creature loses next action.
\item \nameref{Spell:DetectMagic}: Reveals the presence, strength, and school of magical auras.
\item \nameref{Spell:DetectSecretDoors}: Become aware of all secret doors within your line of sight.
\item \nameref{Spell:DetectUndead}: Reveals the presence and strength of undead creatures.
\item \nameref{Spell:DisguiseSelf}: Changes your appearance.
\item \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
\item \nameref{Spell:ScorchingRay}: Deal 1d6 energy damage with a ranged touch attack.
\item \nameref{Spell:ShockingGrasp}: Touch delivers 1d6 energy damage.
\item \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
\item \nameref{Spell:FloatingDisk}: Creates 3-ft.-diameter horizontal disk that holds 100 lb./level.
\item \nameref{Spell:Grease}: Makes 10-ft. square or one object slippery.
\item \nameref{Spell:Identify}: Determines properties of magic item.
\item \nameref{Spell:Light}: Causes object to shine like a torch.
\item \nameref{Spell:MagicAura}: Alters object's magic aura.
\item \nameref{Spell:MagicMissile}: Deal 1d4+1 damage, no save, no touch attack.
\item \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
\item \nameref{Spell:MentalLink}*: You forge a limited mental bond with another creature.
\item \nameref{Spell:Mount}: Summons magical riding horse for 2 hours/level.
\item \nameref{Spell:OpenClose}: Holds door shut or opens it.
\item \nameref{Spell:RayOfEnfeeblement}: Ray inflicts a strength penalty of 1d6.
\item \nameref{Spell:Repair}: Makes repairs on an object or construct.
\item \nameref{Spell:Shield}: Invisible disc gives +4 to AC.
\item \nameref{Spell:Sleep}: Puts 4 HD of creatures into magical slumber.
\item \nameref{Spell:TouchOfFatigue}: Touch fatigues subject.
\item \nameref{Spell:TrueStrike}: +20 on your next attack roll.
\item \nameref{Spell:UnseenServant}: Invisible force obeys your commands.
\item \nameref{Spell:Ventriloquism}: Makes sounds appear out of nowhere.
\end{list}
\subsubsection{2nd-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AcidArrow}: Ranged touch attack for 2d4 acid damage.
\item \nameref{Spell:AlterSelf}: Perform minor physical changes on yourself.
\item \nameref{Spell:AnimalsMovement}: Grants additional movement capabilities.
\item \nameref{Spell:Blindness}: Negates one of the subject's senses.
\item \nameref{Spell:Blur}: Attacks miss subject 20\% of the time.
\item \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
\item \nameref{Spell:Darkvision}: See 30 ft. in total darkness.
\item \nameref{Spell:FalseLife}: Gain 1d10 temporary hp.
\item \nameref{Spell:FlamingSphere}: Creates rolling ball of fire, 2d6 damage, lasts 1 round/level.
\item \nameref{Spell:GhoulTouch}: Paralyzes one subject, which exudes stench that makes those nearby sickened.
\item \nameref{Spell:Glitterdust}: Blinds creatures, outlines invisible creatures.
\item \nameref{Spell:GustOfWind}: Blows away and knocks down creatures.
\item \nameref{Spell:HideousLaughter}: Subject loses actions for 1 round/level.
\item \nameref{Spell:HoldPerson}: Paralyzes one humanoid for 1 round/level.
\item \nameref{Spell:Levitate}: Subject moves up and down at your direction.
\item \nameref{Spell:Locate}: Senses direction toward object (specific or type).
\item \nameref{Spell:Pattern}: Twisting colors fascinate creatures.
\item \nameref{Spell:PhantomTrap}: Makes item seem trapped.
\item \nameref{Spell:ProtectionFromArrows}: Subject becomes immune to most ranged attacks.
\item \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
\item \nameref{Spell:SeeInvisibility}: Reveals invisible creatures or objects.
\item \nameref{Spell:Shatter}: Sonic vibration damages objects or crystalline creatures.
\item \nameref{Spell:SpectralHand}: Creates disembodied glowing hand to deliver touch attacks.
\item \nameref{Spell:SummonSwarm}: Summons swarm of bats, rats, or spiders.
\item \nameref{Spell:TouchOfIdiocy}: Subject takes 1d6 points of Int, Wis, or Cha damage.
\item \nameref{Spell:Web}: Creates sticky spiderwebs between two anchor points.
\item \nameref{Spell:WombatsBoost}\footnote{Thanks to Fax Celestis @ Giantitp.com for this joke.}: Subject gains +4 to an ability score for 1 min./level.
\end{list}

\subsubsection{3rd-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Blindsense}*: Subject can notice things it cannot see.
\item \nameref{Spell:Blink}: Subject randomly vanishes and reappears for 1 round/level.
\item \nameref{Spell:CrisisOfBreath}*: Disrupt subject's breathing.
\item \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
\item \nameref{Spell:EnergyArrow}: Arrows deal additional energy damage.
\item \nameref{Spell:ExplosiveRunes}: Deals 6d6 damage when read.
\item \nameref{Spell:ForcedVisions}*: Useless, distracting visions flash before subject's eyes.
\item \nameref{Spell:GaseousForm}: Subject becomes insubstantial and can fly slowly.
\item \nameref{Spell:HaltUndead}: Immobilizes undead for 1 round/level.
\item \nameref{Spell:Haste}: One creature moves faster, +1 on attack rolls, AC, and Reflex saves.
\item \nameref{Spell:Heroism}: Gives +2 bonus on attack rolls, saves, skill checks.
\item \nameref{Spell:KeenEdge}: Doubles normal weapon's threat range.
\item \nameref{Spell:Piggyback}*: Latch on to a creature as it teleports, retaining your relative position.
\item \nameref{Spell:Rage}: Subjects are thrown into a fit of anger, with various effects.
\item \nameref{Spell:SepiaSnakeSigil}: Creates text symbol that immobilizes reader.
\item \nameref{Spell:ShadowWarriors}*: A group of warriors made of shadow matter appears.
\item \nameref{Spell:ShrinkItem}: Object shrinks to one-sixteenth size.
\item \nameref{Spell:SleetStorm}: Sleet hampers vision and movement.
\item \nameref{Spell:SuppressMagic}*: Renders willing spellcaster incapable of casting spells.
\item \nameref{Spell:Slow}: One creature takes only one action/round, -1 to AC, reflex saves, and attack rolls.
\item \nameref{Spell:TinyHut}: Creates shelter for ten creatures.
\item \nameref{Spell:VampiricTouch}: Touch deals 3d6 damage; caster gains damage as hp.
\item \nameref{Spell:WindWall}: Deflects arrows, knocks down creatures, blocks gases.
\end{list}
\subsubsection{4th-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:ArcaneEye}: Invisible floating eye moves 30 ft./round.
\item \nameref{Spell:AuraOfFire}: Enemies within range take damage, more if they attack you.
\item \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item \nameref{Spell:Confusion}: Subjects behave oddly for 1 round/level.
\item \nameref{Spell:Contagion}: Infects subject with chosen disease.
\item \nameref{Spell:ControlWater}: Raises or lowers bodies of water, or slows water elemental.
\item \nameref{Spell:CrushingDespair}: Subjects take -2 on attack rolls, damage rolls, saves, and checks.
\item \nameref{Spell:DetectScrying}: Alerts you of magical eavesdropping.
\item \nameref{Spell:DimensionalAnchor}: Bars extradimensional movement.
\item \nameref{Spell:HallucinatoryTerrain}: Makes one type of terrain appear like another.
\item \nameref{Spell:HandOfForce}: Hand of force manipulates items.
\item \nameref{Spell:IceStorm}: Hail deals 5d6 damage in cylinder 40 ft. across.
\item \nameref{Spell:MoldMaterial}: Sculpts material into any shape.
\item \nameref{Spell:PhantasmalKiller}: Fearsome illusion kills subject or renders it unconscious.
\item \nameref{Spell:RemoveCurse}: Frees object or person from curse.
\item \nameref{Spell:Shout}: Deafens all within cone and deals 7d6 sonic damage.
\item \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
\item \nameref{Spell:Telekinesis}: Telekinetically throw things around.
\item \nameref{Spell:WallOfFire}: Deals 2d4 fire damage out to 10 ft. Passing through wall deals 7d6 damage.
\item \nameref{Spell:WallOfIce}: Ice forms a translucent, shapeable wall.
\end{list}
\subsubsection{5th-level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em} 
\item \nameref{Spell:BalefulPolymorph}: Transforms subject into harmless animal.
\item \nameref{Spell:Blight}: Withers one plant or deals 1d6/level damage to plant creature.
\item \nameref{Spell:Dream}: Contact or disturb sleeping creature.
\item \nameref{Spell:FalseVision}: Fools scrying with an illusion.
\item \nameref{Spell:Feeblemind}: Subject's Int and Cha drop to 1.
\item \nameref{Spell:InstantSummons}: Prepared object appears in your hand.
\item \nameref{Spell:InterposingHand}: Hand provides cover against one opponent.
\item \nameref{Spell:MindFog}: Subjects in fog suffer increasing penalties to Will saves and Wisdom checks.
\item \nameref{Spell:PrivateSanctum}: Prevents anyone from viewing or scrying an area for 24 hours.
\item \nameref{Spell:PryingEyes}: Floating eyes scout for you.
\item \nameref{Spell:Sending}: Delivers short message anywhere, instantly.
\item \nameref{Spell:Teleport}: Instantly transports you as far as 100 miles/level.
\item \nameref{Spell:TransmuteRockAndMud}: Transforms two 10-ft. cubes per level.
\item \nameref{Spell:XRayVision}*: Grants you the ability to see through solid matter.
\item \nameref{Spell:WallOfForce}: Create Wall which is immune to damage.
\item \nameref{Spell:WallOfStone}: Creates a stone wall that can be shaped.
\item \nameref{Spell:WavesOfFatigue}: Several targets become fatigued.
\end{list}
\subsubsection{6th-level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AntilifeShell}: 10-ft. field hedges out living creatures.
\item \nameref{Spell:Contingency}: Allows you to store one spell to be swiftly cast when the need is dire.
\item \nameref{Spell:DeadlyFog}: Add elemental component to fog, causing it to deal damage.
\item \nameref{Spell:Disintegrate}: Makes one creature or object vanish.
\item \nameref{Spell:Eyebite}: Target becomes panicked, sickened, and/or comatose, depending on HD.
\item \nameref{Spell:FreezingSphere}: Freezes in place and deals cold damage.
\item \nameref{Spell:Hardening}: Increases an object's hardness.
\item \nameref{Spell:ShadowWalk}: Step into shadow to travel rapidly.
\item \nameref{Spell:Shun}*: Subject is forced away.
\item \nameref{Spell:Transformation}: You transform into a a hulk skilled in combat.
\item \nameref{Spell:TransmuteFleshAndStone}: Turns subject creature into statue, or the other way around.
\item \nameref{Spell:TrueSeeing}: Lets you see all things as they really are.
\end{list}
\subsubsection{7th-Level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:ControlWeather}: Changes weather in local area.
\item \nameref{Spell:EtherealJaunt}: Touched creature becomes ethereal for 1 round/level.
\item \nameref{Spell:FingerOfDeath}: Kills one subject.
\item \nameref{Spell:LimitedWish}: Alters reality - within spell limits.
\item \nameref{Spell:MagesSword}: Floating magic blade strikes opponents.
\item \nameref{Spell:PhaseDoor}: Creates an invisible passage through wood or stone.
\item \nameref{Spell:PrismaticSpray}: Rays hit subjects with variety of effects.
\item \nameref{Spell:Refuge}: Alters item to transport its possessor to you.
\item \nameref{Spell:ReverseGravity}: Objects and creatures fall in a direction other than down for one round
\item \nameref{Spell:Sequester}: Subject is invisible to sight and scrying; renders creature comatose.
\end{list}
\subsubsection{8th-level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Binding}: Utilizes an array of techniques to imprison a creature.
\item \nameref{Spell:MindBlank}: Subject is immune to mental/emotional magic and scrying.
\item \nameref{Spell:MomentOfPrescience}: You gain insight bonus on single attack roll, check, or save.
\item \nameref{Spell:PrismaticWall}: Wall's colors have array of effects.
\item \nameref{Spell:Sunburst}: Blinds creatures and deals damage, more to undead and oozes.
\item \nameref{Spell:TelepathicBeacon}: Object or location attracts or repels certain creatures.
\item \nameref{Spell:TemporalStasis}: Puts subject into suspended animation.
\end{list}
\subsubsection{9th-level Sorcerer/Wizard Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AstralProjection}: Projects you and companions onto Astral Plane.
\item \nameref{Spell:Freedom}: Releases creature from imprisonment.
\item \nameref{Spell:Genesis}: You instigate a new demiplane on the Astral Plane.
\item \nameref{Spell:Imprisonment}: Entombs subject beneath the earth.
\item \nameref{Spell:PrismaticSphere}: As prismatic wall, but surrounds on all sides.
\item \nameref{Spell:TeleportationCircle}: Circle teleports any creature inside to designated spot.
\item \nameref{Spell:TimeStop}: You stop time momentarily.
\item \nameref{Spell:WailOfTheBanshee}: Kills multiple creatures.
\item \nameref{Spell:Wish}: As limited wish, but with fewer limits.
\end{list}
\subsubsection{Abjurer Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:MageArmor}: Gives subject +4 armor bonus.
\item[2] \nameref{Spell:Resistance} : Grants a Resistance bonus on saving throws.
\item[3] \nameref{Spell:Nondetection}: Masks object or creature against scrying.
\item[4] \nameref{Spell:GlobeOfInvulnerability}: Stops low-powered spell effects.
\item[5] \nameref{Spell:Dismissal}: Forces a creature to return to native plane.
\item[6] \nameref{Spell:AntimagicField}: Negates magic within 10 ft.
\item[7] \nameref{Spell:SpellTurning}: Reflect spells back at caster.
\item[8] \nameref{Spell:DimensionalLock}: Teleportation and interplanar travel blocked for one day/level within an area.
\item[9] \nameref{Spell:Disjunction}: Dispels magic, disenchants magic items.
\end{list}
\subsubsection{Conjurer Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Fog}: Fog surrounds you.
% \item[1] \nameref{Spell:SummonMonster}: Calls extraplanar creature to fight for you.
\item[2] \nameref{Spell:MatterCreation}: Creates one cloth or wood object.
\item[2] \nameref{Spell:SummonDemon}: Summons a demon to fight for you.
\item[2] \nameref{Spell:SummonDevil}: Summons a devil to fight for you.
\item[3] \nameref{Spell:NoxiousVapors}: Nauseating vapors, 1 round/level.
\item[4] \nameref{Spell:BlackTentacles}: Tentacles grapple all within 20 ft. spread.
\item[4] \nameref{Spell:DimensionDoor}: Teleports you short distance.
\item[4] \nameref{Spell:SummonCelestial}: Summons a celestial to defend you.
\item[5] \nameref{Spell:PlanarBinding}: Traps extraplanar creature of 6 HD or less.
\item[6] \nameref{Spell:WallOfIron}: Flat iron wall appears, may topple on to foes.
\item[7] \nameref{Spell:PlaneShift}: As many as eight subjects travel to another plane.
\item[8] \nameref{Spell:Maze}: Traps subject in extradimensional maze.
\item[9] \nameref{Spell:Gate}: Connects two planes for travel or calling.
\end{list}
\subsubsection{Diviner Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
\item[2] \nameref{Spell:Clairvoyance}: See and hear a distant location.
\item[3] \nameref{Spell:MnemonicEnhancer}: You magically enhance your own ability to recall information.
\item[4] \nameref{Spell:Scrying}: Spies on subject from a distance.
\item[5] \nameref{Spell:ContactOtherPlane}: Lets you ask question of extraplanar entity.
\item[6] \nameref{Spell:LegendLore}: Lets you learn tales about a person, place, or thing.
\item[7] \nameref{Spell:Precognition}: You see the future of one creature.
\item[8] \nameref{Spell:AbsoluteRevelation}: Reveals exact location of creature or object.
\item[9] \nameref{Spell:Foresight}: ``Sixth sense`` warns of impending danger.
\end{list}
\subsubsection{Enchanter Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Charm}: Makes one creature your friend.
\item[2] \nameref{Spell:ReadThoughts}: Detect surface thoughts of creatures in range.
\item[3] \nameref{Spell:Suggestion}: Compels subject to follow stated course of action.
\item[4] \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
\item[5] \nameref{Spell:Dominate}: Controls humanoid telepathically.
\item[6] \nameref{Spell:DeadlyFright}*: Humanoid dies of fright.
\item[7] \nameref{Spell:PowerWord}: Overwhelms the minds of lesser creatures with a single word of power.
\item[8] \nameref{Spell:IrresistibleDance}: Forces subject to dance.
\item[9] \nameref{Spell:CrushingTheEssence}*: Suppresses all immunities to enchantments for one round.
\end{list}
\subsubsection{Evoker Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Burn}: Creature catches on fire if it takes fire damage.
\item[2] \nameref{Spell:Fireball}: Deal 3d6 energy damage in a burst.
\item[2] \nameref{Spell:LightningBolt}: Deal 3d6 energy damage in a line.
\item[2] \nameref{Spell:Pyrotechnics}: Turns fire into blinding light or choking smoke.
\item[3] \nameref{Spell:ManeuveringHand}: Hand composed of force performs combat maneuvers.
\item[4] \nameref{Spell:ResilientSphere}: Force globe protects but traps one subject.
\item[5] \nameref{Spell:ConeOfCold}: 9d6 points of energy damage in a cone, and all in area must save or be slowed.
\item[6] \nameref{Spell:ChainLightning}: 1d6/level damage to multiple subjects.
\item[8] \nameref{Spell:PolarRay}:: Ranged touch attack deals cold damage and immobilizes.
\item[9] \nameref{Spell:Meteor}: Sphere descends, destroys everything.
\end{list}
\subsubsection{Illusionist Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Image}: Creates illusion of your design.
\item[2] \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
\item[2] \nameref{Spell:MirrorImage}: Creates decoy duplicates of you.
\item[3] \nameref{Spell:HallOfMirrors}*: Subject's movement is randomized.
\item[4] \nameref{Spell:ShadowConjuration}: Mimics certain conjurations.
\item[5] \nameref{Spell:ShadowEvocation}: Mimics certain Evocations.
\item[6] \nameref{Spell:Mislead}: Turns you invisible and creates illusory double.
\item[6] \nameref{Spell:ProgrammedImage}: Causes Image spell to be triggered by event.
\item[7] \nameref{Spell:Simulacrum}: Creates partially real double of a creature.
\item[8] \nameref{Spell:Screen}: Illusion hides area from vision, scrying.
\item[9] \nameref{Spell:RealityVeil}*: Creatures live forevermore in world of your imagination.
\end{list}
\subsubsection{Necromancer Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:Fear}: One creature flees for 1d4 rounds.
\item[2] \nameref{Spell:CommandUndead}: Undead creature obeys your commands.
\item[3] \nameref{Spell:GentleRepose}: Preserves one corpse.
\item[4] \nameref{Spell:AnimateDead}: Creates undead skeletons and zombies.
\item[4] \nameref{Spell:Enervation}: Subject gains 1d4 negative levels.
\item[5] \nameref{Spell:BalefulResurrection}: Returns subject from the dead - mostly.
\item[5] \nameref{Spell:Possession}: You assume a spirit form and take control of another creature's body.
\item[6] \nameref{Spell:CreateUndead}: Creates ghouls, and more powerful creatures with augment.
\item[6] \nameref{Spell:LifeAndDeath}: Kills living creatures or destroys undead creatures.
\item[7] \nameref{Spell:ControlUndead}: You force an undead creature to bow to your will.
\item[8] \nameref{Spell:HorridWilting}: Dessicates nearby creatures.
\item[9] \nameref{Spell:SoulBind}: Traps dead soul to prevent resurrection.
\end{list}
\subsubsection{Transmuter Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item[1] \nameref{Spell:AlterSize}: Humanoid creature changes size.
\item[2] \nameref{Spell:FormScout}: Subject gains the form of a nimble creature.
\item[3] \nameref{Spell:Fly}: Subject flies at speed of 40 ft.
\item[3] \nameref{Spell:FormAvian}: Subject gains the form of a bird.
\item[3] \nameref{Spell:FormFish}: Subject gains the form of a water-dwelling creature.
\item[4] \nameref{Spell:FormCarnivore}: Subject gains the form of a dangerous beast.
\item[4] \nameref{Spell:FormVermin}: Subject gains the form of a vermin.
\item[4] \nameref{Spell:FormViper}: Subject gains the form of a snake.
\item[5] \nameref{Spell:FormHorror}: Subject gains the form of a tentacled monstrosity.
\item[5] \nameref{Spell:FormTreant}: Subject gains the form of a plant creature.
\item[6] \nameref{Spell:FormDragon}: Subject gains the form of a mighty dragon.
\item[7] \nameref{Spell:FormElemental}: Subject becomes a living creature of the elements.
\item[8] \nameref{Spell:FormIronGolem}: Subject's body changes into a creature of living iron.
\item[9] \nameref{Spell:Shapechange}: Transforms you into any creature whose form you know, and change forms once per round.
\end{list}







