\subsection{Background Specializations}

\subsubsection{Academic}
You are an educated individual, belonging to a school or guild of mages.
\paragraph{Specialization Features}
Add all Knowledge skills, the Decipher Script skill, Diplomacy, Gather Information and Use Magic Device to your list of class skills.
\subparagraph{Lore (Ex):}
Thanks to long hours of study, you have a wide range of stray knowledge. This ability is identical to the \nameref{sec:Bard}'s Bardic Knowledge class feature, using your Arcanist level in place of the Bard level. This counts as Bardic Knowledge for all purposes, including those of prerequisites. If you have Bard levels, you do not use the abilities separately, but your Arcanist and Bard levels stack for purposes of determining your bonus on the check.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:ComprehendLanguages}: You understand all spoken and written languages.
 \item[1] \nameref{Spell:UnseenServant}: Invisible force obeys your commands.
 \item[2] \nameref{Spell:Sending}: Delivers short message, instantly.
\end{itemize}

\subsubsection{Aristocratic}
You come from the more elevated echelons of society.
\paragraph{Specialization Features}
Add Bluff, Diplomacy, Knowledge (nobility and royalty), Ride, and Sense Motive to your list of class skills.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
 \item[1] \nameref{Spell:UnseenServant}: Invisible force obeys your commands.
 \item[1] \nameref{Spell:Command}: One subject obeys selected command for 1 round.
 \item[2] \nameref{Spell:RegalBearing}: Grants bonuses on social skills, can be discharged to issue Command
\end{itemize}

\subsubsection{Dungeoneer}
You have long known that the way to knowledge and riches is not across the surface of the earth, and have invested in the appropriate skillset.
\paragraph{Specialization Features}
Add Appraise, Climb, Escape Artist, Jump, Knowledge (dungeoneering), Search, Swim and Use Rope to your list of class skills.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:AnimateRope}: Animates a rope or wine.
 \item[1] \nameref{Spell:DetectSecretDoors}: Become aware of all secret doors within your line of sight.
 \item[1] \nameref{Spell:Light}: Causes object to shine like a torch.
 \item[2] \nameref{Spell:TrapIntuition}: Notice and disable traps as a rogue does.
\end{itemize}

\subsubsection{Nomad}
Your life has been a literal journey. You are long accustomed to spending time away from so-called civilization.
\paragraph{Specialization Features}
Add Heal, Knowledge (geography), Knowledge (nature), Ride, Spot, Survival and Swim to your list of class skills.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Alarm}: Wards an area for 2 hours/level.
 \item[1] \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
 \item[1] \nameref{Spell:FoodAndWater}: Purifies food and water so it is again fit for consumption.
 \item[1] \nameref{Spell:Mount}: Summons magical riding horse for 2 hours/level.
\end{itemize}

\subsubsection{Underworld}
Your past is best unspoken of in polite company, but it has left you with a certain set of skills.
\paragraph{Specialization Features}
Add Disguise, Forgery, Gather Information, Open Lock and Sleight of Hand to your list of class skills.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Alarm}: Wards an area for 2 hours/level.
 \item[1] \nameref{Spell:DisguiseSelf}: Changes your appearance.
 \item[1] \nameref{Spell:OpenClose}: Holds door shut or opens it.
 \item[2] \nameref{Spell:Silence}: Negates sound in 20-ft. radius.
\end{itemize}

\subsubsection{Military}
Your old commander never much cared how you got the job done, as long as the enemy platoons were blown up.
\paragraph{Specialization Features}
Add Diplomacy, Intimidate, Heal, and Knowledge (history) to your list of class skills.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:ShockingGrasp}: Touch delivers 1d8 energy damage.
 \item[1] \nameref{Spell:ScorchingRay}: Deal 1d6 energy damage with a ranged touch attack.
 \item[2] \nameref{Spell:EnergyBall}: Deal 3d6 energy damage in a burst.
 \item[2] \nameref{Spell:EnergyBolt}: Deal 3d6 energy damage in a line.
\end{itemize}

\subsection{Novice Specializations}
\subsubsection{Air, Novice}
\label{Spec:AirNovice}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Fog}: Fog surrounds you.
 \item[1] \nameref{Spell:Magewind}: Invokes a gentle wind change in a large area.
 \item[2] \nameref{Spell:GustOfWind}: Blows away and knocks down creatures.
 \item[2] \nameref{Spell:Glitterdust}: Blinds creatures, outlines invisible creatures.
\end{itemize}

\subsubsection{Artisan}
A spell is a fleeting firework, a magic item is a bonfire that can shine for ages. You know the value of taking the long road.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Repair}: Makes repairs on an object or construct.
 \item[2] \nameref{Spell:MatterCreation}: Creates one cloth or wood object.
\end{itemize}

\subsubsection{Blade Magic}
Too many Arcanists have died because they did not know which end of a weapon to hold. You won't be one of them.
\paragraph{Specialization Features}
You gain proficiency with one martial weapon of your choice, as well as with light armor, and with shields (except tower shields and exotic shields). \par
You gain a number of additional hit points equal to your Arcanist level. This number increases as you gain more Arcanist levels.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:MagicWeapon}: Weapon gains +1 bonus.
 \item[1] \nameref{Spell:TrueStrike}: +20 on your next attack roll.
 \item[1] \nameref{Spell:Virtue}: Gain 5 temporary hit points.
 \item[2] \nameref{Spell:DancingBlade}: Weapon flies out and attacks enemies within an area.
\end{itemize}
\paragraph{Synergy} 
\begin{itemize}
 \item If you also have the \nameref{Spec:Polymorphing} Specialization, add \nameref{Spell:Transformation} to this Specialization's spell list.
\end{itemize}

\subsubsection{Charming}
\label{Spec:Charming}
You understand people. You also know that magic can be very useful to help them understand you.
\paragraph{Specialization Features}
Add Bluff, Diplomacy, Gather Information and Sense Motive to your list of class skills.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Charm}: Makes one creature your friend.
 \item[2] \nameref{Spell:Enthrall}: Captivates all within 100 ft. + 10 ft./level.
 \item[2] \nameref{Spell:ReadThoughts}: Detect surface thoughts of creatures in range.
\end{itemize}

\subsubsection{Fire, Novice}
\paragraph{Specialization Features}
\subparagraph{Burning Missiles (Ex):} When you use your Magic Missile Spell-like ability, you can choose to have the missile or missiles deal fire damage instead of force damage. In addition to changing the damage type, this replaces the spell's force descriptor with the fire descriptor, and allows it to target and damage objects as well as creatures. Flammable objects may catch fire after taking damage from a burning missile.
\subparagraph{Handheld Flame (Su):} You can create a small fire in the palm of your hand at will. The fire does not burn you, but otherwise behaves as a similarly-sized non-magical fire would. It sheds light as a torch and can be used to light things on fire with a touch. Holding a Handheld Flame while striking a creature with your unarmed strike adds 1 point of fire damage to the blow. \par
Creating the flame is a standard action. It can be kept burning by concentrating on it as a free action. The fire goes out if willed out of existence (a free action) or if it is not concentrated on for one whole round.
\subparagraph{Light Up (Su):} At will as a standard action, you can set an unattended, flammable object within 30' on fire.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:EndureElements}: Exist comfortably in hot or cold environments.
 \item[1] \nameref{Spell:ProduceFlame}: Create a fire in your hand that you can throw or attack with in melee.
 \item[2] \nameref{Spell:Fireball}: Deal 3d6+3 fire damage in a burst that is hard to dodge.
 \item[2] \nameref{Spell:FlameBlade}: Creates a weapon of pure fire.
\end{itemize}

\subsubsection{Force}
\paragraph{Specialization Features}
\subparagraph{Additional Missile (Su):} When you use your Magic Missile Spell-like ability, you can fire one additional missile beyond what would normally be allowed by your caster level, at no cost. For example, a 1st level Arcanist with this Specialization could fire two missiles.
\subparagraph{Instant Shield (Ex):} You can cast your \nameref{Spell:Shield} spell as an immediate action. Doing so reduces the spell's duration to 1 round. When using Instant Shield in response to an attack, you must do so before knowing the result of the attack roll.
\subparagraph{Mage Hand (Su):} As a standard action, you can lift and move up to 5 pounds of items from a distance. Continued movement of items requires concentration, as if on a spell (a standard action). You can manipulate the moved items as if you were using one hand for the task.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:FloatingDisk}: Creates a versatile 5-ft.-diameter disk of force.
 \item[1] \nameref{Spell:MageArmor}: Gives subject +4 armor bonus.
 \item[1] \nameref{Spell:Shield}: Invisible disc gives +4 to AC.
 \item[2] \nameref{Spell:MageFist}: Perform a simple telekinetic maneuver.
\end{itemize}

\subsubsection{Ice, Novice}
\label{Spec:IceNovice}
\paragraph{Specialization Features}
\subparagraph{Freeze (Su):} At will as a standard action, you can freeze an object within 10 feet. You can freeze an object weighing up to 5 pounds. A larger object can be partially frozen.
\subparagraph{Frozen Missiles (Ex):} When you use your Magic Missile Spell-like ability, you can choose to have the missile or missiles deal cold damage instead of force damage. In addition to changing the damage type, this replaces the spell's force descriptor with the cold descriptor, and allows it to target and damage objects as well as creatures. An object damaged by a frozen missile may freeze.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:FrozenSlick}: Square is covered in slippery ice.
 \item[1] \nameref{Spell:RayOfFrost}: Deal 1d6 cold damage with a ranged touch attack, and target must save or be slowed.
 \item Ice shield?
\end{itemize}

\subsubsection{Imagery}
\paragraph{Specialization Features}
Add Hide, Move Silently and Sleight of Hand to your list of class skills.
\subparagraph{Modify Color (Su):} As a standard action at will, you can modify the color of one or more objects within a 1-foot cube. The modification lasts for one hour before it reverts to its original state.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Image}: Creates illusion of your design.
 \item[1] \nameref{Spell:Ventriloquism}: Makes sounds appear out of nowhere.
 \item[2] \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
 \item[2] \nameref{Spell:Silence}: Negates sound in 20-ft. radius.
\end{itemize}
\paragraph{Synergy} 
\begin{itemize}
 \item If you have the \nameref{Spec:Charming} Specialization, add \nameref{Spell:Pattern} to this Specialization's spell list.
 \item If you have the \nameref{Spec:Scrambling} Specialization, add \nameref{Spell:ColorSpray} to this Specialization's spell list.
\end{itemize}

\subsubsection{Light, Novice}
\paragraph{Specialization Features}
\subparagraph{Trick of the Light (Su):} You can subtly manipulate light and shadow within 5 feet. This grants you a +4 enhancement bonus on intimidate and hide skill checks.
% Intimidate as part of casting the spells?
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Light}: Causes object to shine like a torch.
 \item[1] \nameref{Spell:SearingLight}: Ray scorches foul creatures.
 \item[2] \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
 \item[2] \nameref{Spell:Darkvision}: See 30 ft. in total darkness.
\end{itemize}

\subsubsection{Negative Energy, Novice}
\label{Spec:NegativeEnergyNovice}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:RayOfEnfeeblement}: Ray inflicts a strength penalty of 1d6.
 \item[1] \nameref{Spell:TouchOfFatigue}: Touch fatigues subject.
 \item[2] \nameref{Spell:Blindness}: Negates one of the subject's senses.
 \item[2] \nameref{Spell:FalseLife}: Gain 1d10 temporary hp.
\end{itemize}

\subsubsection{Protection}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:MageArmor}: Gives subject +4 armor bonus.
 \item[2] \nameref{Spell:ProtectionFromArrows}: Subject becomes immune to most ranged attacks.
 \item[2] \nameref{Spell:ResistEnergy}: Ignores first 10 (or more) points of damage/attack from specified energy type.
 \item[2] \nameref{Spell:Resistance}: Grants a Resistance bonus on saving throws.
\end{itemize}

\subsubsection{Seeing}
\begin{itemize}
 \item[1] \nameref{Spell:DetectSecretDoors}: Become aware of all secret doors within your line of sight.
 \item[2] \nameref{Spell:SeeInvisibility}: Reveals invisible creatures or objects.
 \item[2] \nameref{Spell:Darkvision}: See 30 ft. in total darkness.
 \item[2] \nameref{Spell:Clairvoyance}: See and hear a distant location.
\end{itemize}
\paragraph{Synergy}
If you have the \nameref{Spec:NegativeEnergyNovice} Specialization, add \nameref{Spell:DetectUndead} to this Specialization's spell list.

\subsubsection{Scrambling}
\label{Spec:Scrambling}
The mind is the softest spot of every living creature, and you have the skills to take advantage of that.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:Daze}: Target creature loses next action.
 \item[1] \nameref{Spell:Sleep}: Puts 4 HD of creatures into magical slumber.
 \item[2] \nameref{Spell:HoldPerson}: Paralyzes one humanoid for 1 round/level.
 \item[2] \nameref{Spell:HideousLaughter}: Subject loses actions for 1 round/level.
\end{itemize}

\subsubsection{Spell Channeling}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:ShockingGrasp}: Touch delivers 1d8 energy damage.
\end{itemize}
\paragraph{Synergy}
\begin{itemize}
 \item If you have the \nameref{Spec:NegativeEnergyNovice} Specialization, add \nameref{Spell:GhoulTouch} to this Specialization's spell list.
 \item If you have the \nameref{Spec:NegativeEnergyAdept} Specialization, add \nameref{Spell:VampiricTouch} to this Specialization's Spell list.
 \item If you have the \nameref{Spec:Scrambling} Specializationm, add \nameref{Spell:TouchOfIdiocy} to this Specialization's spell list.
\end{itemize}

\subsubsection{Transmutation}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:AlterSize}: Humanoid creature changes size.
 \item[1] \nameref{Spell:AnimateRope}: Animates a rope or wine.
 \item[2] \nameref{Spell:AlterSelf}: Perform minor physical changes on yourself.
 \item[2] \nameref{Spell:AnimalsMovement}: Grants additional movement capabilities.
 \item[2] \nameref{Spell:FormScout}: Subject gains the form of a nimble creature.
\end{itemize}


\subsection{Adept Specializations}
\subsubsection{Air, Adept}
\paragraph{Spells}
\begin{itemize}
 \item[3] \nameref{Spell:BandsOfAir}: Traps creature in invisible bonds of air.
 \item[3] \nameref{Spell:Fly}: Subject flies at speed of 40 ft.
 \item[3] \nameref{Spell:GaseousForm}: Subject becomes insubstantial and can fly slowly.
 \item[3] \nameref{Spell:WindWall}: Deflects arrows, knocks down creatures, blocks gases.
\end{itemize}
\paragraph{Synergy}
\begin{itemize}
 \item If you have the \nameref{Spec:IceNovice} Specialization, you gain the following ability:
 \subparagraph{Arctic Gale (Su):} When casting Gust of Wind, you can choose to infuse the wind with freezing power. Any creature caught within the gust's area then takes 2d6 points of cold damage.
 \item If you have the \nameref{Spec:Compulsion} Specialization, add \nameref{Spell:MindFog} to this Specialization's spell list.
\end{itemize}

\subsubsection{Compulsion}
\label{Spec:Compulsion}
\paragraph{Spells}
\begin{itemize}
 \item[3] \nameref{Spell:Suggestion}: Compels subject to follow stated course of action.
 \item[4] \nameref{Spell:Confusion}: Subjects behave oddly for 1 round/level.
 \item[4] \nameref{Spell:GeasQuest}: Commands subject of 7 HD or less.
 \item[5] \nameref{Spell:Dominate}: Controls humanoid telepathically.
\end{itemize}

\subsubsection{Counterspelling}
\label{Spec:Counterspelling}
\paragraph{Spells}
\begin{itemize}
 \item[2] \nameref{Spell:DweomerRip}: Damages creatures with active magical effects on them.
 \item[3] \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
 \item[4] \nameref{Spell:GlobeOfInvulnerability}: Stops low-powered spell effects.
 \item[7] \nameref{Spell:SpellTurning}: Reflect spells back at caster
\end{itemize}


\subsubsection{Cursing}
\begin{itemize}
 \item[1] \nameref{Spell:LastLaugh}: Destroy yourself in an attempt to take your enemies with you.
 \item[3] \nameref{Spell:BestowCurse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
 \item[3] \nameref{Spell:RemoveCurse}: Frees object or person from curse.
 \item[6] \nameref{Spell:Eyebite}: Target becomes panicked, sickened, and/or comatose, depending on HD.
\end{itemize}

\subsubsection{Earth}
\begin{itemize}
 \item \nameref{Spell:MoldMaterial}: Sculpts material into any shape.
 \item \nameref{Spell:Stoneskin}: Ignore 7 points of damage per attack.
\end{itemize}


\subsubsection{Fire, Adept}
\begin{itemize}
 \item[4] \nameref{Spell:AuraOfFire}: Enemies within range take damage, more if they attack you.
 \item[4] \nameref{Spell:WallOfFire}: Deals 2d4 fire damage out to 10 ft. Passing through wall deals 7d6 damage.
\end{itemize}

\subsubsection{Force, Adept}
\paragraph{Spells}
\begin{itemize}
 \item[3] \nameref{Spell:ExplosiveRunes}: Deals 5d6 damage when read.
 \item[4] \nameref{Spell:ResilientSphere}: Force globe protects but traps one subject.
 \item[4] \nameref{Spell:HandOfForce}: Hand of force manipulates items.
 \item[4] \nameref{Spell:Telekinesis}: Telekinetically throw things around.
 \item[5] \nameref{Spell:WallOfForce}: Create Wall which is immune to damage.
\end{itemize}

\subsubsection{Gravity}
Defeating the earth's pull is the dream of many, but so few manage to master it.
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:ControlFall}: Objects or creatures fall slowly.
 \item[2] \nameref{Spell:Levitate}: Subject moves up and down at your direction.
 \item[3] \nameref{Spell:Fly}: Subject flies at speed of 40 ft.
 \item[4] \nameref{Spell:SpikeGravity}: Sharply and irregularly changes gravity within an area, knocking creatures down.
 \item[7] \nameref{Spell:ReverseGravity}: Objects and creatures fall in a direction other than down for one round
\end{itemize}

\subsubsection{Ice, Adept}
\begin{itemize}
 \item[4] \nameref{Spell:IceStorm}: Hail deals 5d6 damage in cylinder 40 ft. across.
 \item[4] \nameref{Spell:WallOfIce}: Ice forms a translucent, shapeable wall.
 \item[6] \nameref{Spell:FreezingSphere}: Freezes in place and deals cold damage.
\end{itemize}

\subsubsection{Light, Adept}
\begin{itemize}
 \item[4] \nameref{Spell:OrbOfLight}: Orb deals blinds and deals damage to a creature.
 \item[4] \nameref{Spell:RepellingLight}: Globe of light keeps foul creatures at bay.
\end{itemize}

\subsubsection{Metamagic}
\begin{itemize}
 \item[3] \nameref{Spell:DispelMagic}: Cancels magical spells and effects.
\end{itemize}

\subsubsection{Negative Energy, Adept}
\label{Spec:NegativeEnergyAdept}
\paragraph{Spells}
\begin{itemize}
 \item[4] \nameref{Spell:Enervation}: Subject gains 1d4 negative levels.
 \item[5] \nameref{Spell:WavesOfFatigue}: Several targets become fatigued.
 \item[6] \nameref{Spell:AntilifeShell}: 10-ft. field hedges out living creatures.
\end{itemize}

\subsubsection{Polymorphing}
\label{Spec:Polymorphing}
\paragraph{Spells}
\begin{itemize}
 \item \nameref{Spell:BalefulPolymorph}: Transforms subject into harmless animal.
\end{itemize}
\paragraph{Synergy}
\begin{itemize}
 \item If you have the \nameref{Spec:AirNovice} Specialization, add \nameref{Spell:FormAvian} to this Specialization's spell list.
 \item If you have at least 2 ranks in Swim, add \nameref{Spell:FormFish} to this Specialization's spell list.
 \item If you have at least 10 ranks in Knowledge (nature), add \nameref{Spell:FormCarnivore}, \nameref{Spell:FormVermin} or \nameref{Spell:FormViper} to this Specialization's spell list (choose one).
 \item If you have at least 12 ranks in Knowledge (dungeoneering), add \nameref{Spell:FormHorror} to this Specialization's spell list.
 \item If you have at least 12 ranks in Knowledge (nature), add \nameref{Spell:FormTreant} to this Specialization's spell list.
 \item If you have at least 14 ranks in Knowledge (arcana), add \nameref{Spell:FormDragon} to this Specialization's spell list.
 \item If you have at least 16 ranks in Knowledge (the planes), add \nameref{Spell:FormElemental} to this Specialization's spell list.
\end{itemize}

\subsubsection{Reanimation}
\begin{itemize}
 \item[2] \nameref{Spell:CommandUndead}: Undead creature obeys your commands. 
 \item[4] \nameref{Spell:AnimateDead}: Creates undead skeletons and zombies.
 \item[4] \nameref{Spell:BalefulResurrection}: Returns subject from the dead - mostly.
 \item[6] \nameref{Spell:CreateUndead}: Creates ghouls, and more powerful creatures with augment.
\end{itemize}

\subsubsection{Sonic}
\begin{itemize}
 \item[2] \nameref{Spell:Shatter}: Sonic vibration damages objects or crystalline creatures.
 \item[2] \nameref{Spell:SoundBurst}: Deals 1d8 sonic damage to subjects; may stun them.
 \item[4] \nameref{Spell:Shout}: Deafens all within cone and deals 7d6 sonic damage.
 \item[6] \nameref{Spell:SympatheticVibration}: Deals 2d10 damage/round to freestanding structure.
\end{itemize}

\subsubsection{Summoning}
\paragraph{Specialization Features}
% \subparagraph{Permanent Summons (Ex):} When casting a Conjuration (Summoning) spell, you can change its duration to Permanent (D). You can only have one such permanent spell active at a time.
\paragraph{Spells}
\begin{itemize}
 \item[2] \nameref{Spell:SummonSwarm}: Summons swarm of bats, rats, or spiders.
 \item[2] \nameref{Spell:SummonDevil}: Summons a devil to fight for you.
 \item[3] \nameref{Spell:SummonDemon}: Summons a demon to fight for you.
 \item[5] \nameref{Spell:Dismissal}: Forces a creature to return to native plane.
\end{itemize}

\subsubsection{Teleportation}
\begin{itemize}
 \item[4] \nameref{Spell:DimensionalAnchor}: Bars extradimensional movement.
 \item[4] \nameref{Spell:DimensionDoor}: Teleports you short distance.
 \item[5] \nameref{Spell:Teleport}: Instantly transports you as far as 100 miles/level.
\end{itemize}


\subsubsection{Scrying}
\begin{itemize}
 \item[2] \nameref{Spell:Clairvoyance}: See and hear a distant location.
 \item[2] \nameref{Spell:Locate}: Senses direction toward object (specific or type).
 \item[4] \nameref{Spell:ArcaneEye}: Invisible floating eye moves 30 ft./round.
 \item[4] \nameref{Spell:Scrying}: Spies on subject from a distance.
 \item[5] \nameref{Spell:PryingEyes}: Floating eyes scout for you.
\end{itemize}

\subsubsection{Speed}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:ExpeditiousRetreat}: Your speed increases by 30 ft.
 \item[3] \nameref{Spell:Haste}: One creature moves faster, +1 on attack rolls, AC, and Reflex saves.
 \item[3] \nameref{Spell:Slow}: One creature takes only one action/round, -1 to AC, reflex saves, and attack rolls.
\end{itemize}


\subsection{Master Specializations}
\subsubsection{Antimagic}
\begin{itemize}
 \item[3] \nameref{Spell:SuppressMagic}: Renders willing spellcaster incapable of casting spells.
 \item[5] \nameref{Spell:SpellResistance}: Subject gains SR 12 + level.
 \item[6] \nameref{Spell:AntimagicField}: Negates magic within 10 ft.
 \item[9] \nameref{Spell:Disjunction}: Dispels magic, disenchants magic items.
\end{itemize}

\subsubsection{Calling}
\begin{itemize}
 \item[5] \nameref{Spell:PlanarBinding}: Traps extraplanar creature of 6 HD or less.
 \item[5] \nameref{Spell:Dismissal}: Forces a creature to return to native plane.
 \item[9] \nameref{Spell:Gate}: Connects two planes for travel or calling.
\end{itemize}

\subsubsection{Death}
\begin{itemize}
 \item[7] \nameref{Spell:FingerOfDeath}: Kills one subject.
 \item[8] \nameref{Spell:HorridWilting}: Dessicates nearby creatures.
 \item[9] \nameref{Spell:SoulBind}: Traps dead soul to prevent resurrection.
\end{itemize}

\subsubsection{Entropy}
\paragraph{Spells}
\begin{itemize}
 \item[1] \nameref{Spell:EntropicShield}: Ranged attacks against you have 20\% miss chance.
 \item[6] \nameref{Spell:Disintegrate}: Makes one creature or object vanish.
\end{itemize}

\subsubsection{Lightsplitting}
\paragraph{Prerequisite:} Light
\paragraph{Spells}
\begin{itemize}
 \item[7] \nameref{Spell:PrismaticSpray}: Rays hit subjects with variety of effects.
 \item[8] \nameref{Spell:PrismaticWall}: Wall's colors have array of effects.
 \item[9] \nameref{Spell:PrismaticSphere}: As prismatic wall, but surrounds on all sides.
\end{itemize}

% \subsection{Grandmaster Specializations}
\subsubsection{Time}
\begin{itemize}
 \item[6] \nameref{Spell:CrushingOnsetOfAge}*: Subject ages, withers, and dies before your eyes.
 \item[8] \nameref{Spell:TemporalStasis}: Puts subject into suspended animation.
 \item[9] \nameref{Spell:TimeStop}: You stop time momentarily.
\end{itemize}