\subsection[Dread Knight]{The Dread Knight}
\begin{quote}
\emph{``You do not know pain! Not yet.''}
- [NAME], Minotaur Dread Knight
\end{quote}

Dread Knights are spellcasters born with the magical spark in them - but in a dark and twisted form. Some embrace it, becoming merciless killers.
Others try to turn their powers towards good, becoming dark avengers of sorts.
The thing all Dread Knights have in common is that when one shows up, things are about to go horribly wrong for someone.
\paragraph{Alignment:} Any nongood
\paragraph{Hit Die:} d10
\paragraph{Class skills:}
The Dread Knight's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Disguise (Cha), Forgery (Cha), Gather Information (Cha), Intimidate (Cha), Hide (Dex) Knowledge (Arcana) (Int), Knowledge (local) (Int), Knowledge (religion) (Int), Knowledge (the planes) (Int), Move Silently (Dex), Profession (Wis), Ride (Dex), Sense Motive (Wis), and Spellcraft (Int).

\paragraph{Skill Points at 1st Level:} (4 + Int modifier) $\times$ 4.
\paragraph{Skill Points at each additional Level:} 4 + Int modifier.
\begin{table*}
\caption{The Dread Knight}
\label{tab:DreadKnight}
\makebox[\textwidth]{
\begin{tabular}{llccclccc}
\toprule
	&	&	&	&	&				&\multicolumn{3}{c}{Spellcasting}\\ \cmidrule(r){7-9}
Level	&BAB	&Fort 	&Ref 	&Will 	&Special			&SP/day	&Known&Max level\\
\midrule
1st &+1			&+2 &+0 &+2	&Dread Knight's Curse,		&0 &1 &1st\\
    &			&&&		&Dark Grace			&&&\\
2nd &+2 		&+3 &+0 &+3 	&Dark Power 			&1 &2 &1st\\
3rd &+3 		&+3 &+1 &+3 	&-    				&3 &3 &1st\\
4th &+4 		&+4 &+1 &+4 	&-    				&5 &4 &2nd\\
5th &+5 		&+4 &+1 &+4 	&Dark Power   			&7 &5 &2nd\\
6th &+6/+1 		&+5 &+2 &+5 	&-    				&11 &6 &2nd\\
7th &+7/+2 		&+5 &+2 &+5 	&-    				&15 &7 &3rd\\
8th &+8/+3 		&+6 &+2 &+6 	&Dark Power   			&19 &8 &3rd\\
9th &+9/+4 		&+6 &+3 &+6 	&-    				&23 &9 &3rd\\
10th &+10/+5		&+7 &+3 &+7 	&-    				&27 &10 &4th\\
11th &+11/+6/+1		&+7 &+3 &+7 	&Dark Power   			&35 &11 &4th\\
12th &+12/+7/+2 	&+8 &+4 &+8 	&-    				&43 &12 &4th\\
13th &+13/+8/+3 	&+8 &+4 &+8 	&-    				&51 &13 &5th\\
14th &+14/+9/+4 	&+9 &+4 &+9 	&Dark Power   			&59 &14 &5th\\
15th &+15/+10/+5	&+9 &+5 &+9 	&-    				&67 &15 &5th\\
16th &+16/+11/+6/+1 	&+10 &+5 &+10 	&-    				&79 &16 &6th\\
17th &+17/+12/+7/+2 	&+10 &+5 &+10 	&Dark Power   			&91 &17 &6th\\
18th &+18/+13/+8/+3 	&+11 &+6 &+11 	&-    				&103 &18 &6th\\
19th &+19/+14/+9/+4 	&+11 &+6 &+11 	&-    				&115 &19 &6th\\
20th &+20/+15/+10/+5	&+12 &+6 &+12 	&Dark Power   			&127 &20 &6th\\
\bottomrule
\end{tabular}}
\end{table*}
\subsubsection{Class Features}
All the following are class features of the Dread Knight.

\paragraph{Weapon and Armor Proficiency:} 
Dread Knights are proficient with all simple and martial weapons, with light and medium armor, and with shields (except tower shields and exotic shields).

\paragraph{Spell Points/Day:} A Dread Knight's ability to cast spells is limited by the spell points he has available. 
His base daily allotment of spell points is given on \nameref{tab:DreadKnight} table. 
In addition, he receives bonus spell points per day if he has a high Charisma score.
His race may also provide bonus spell points per day, as may certain feats and items.

\paragraph{Spells Known:} A Dread Knight begins play knowing one Dread Knight spell of your choice. 
Each time he achieves a new level, he unlocks the knowledge of new spells.
Choose the spells known from the Dread Knight spell list (Exception: The feats Expanded Knowledge and Epic Expanded Knowledge do allow a Dread Knight to learn spells of other classes, even specialist Wizard spells.).
A Dread Knight can cast any spell he knows that has a spell point cost equal to or lower than his caster level.
The number of times a Dread Knight can cast spells in a day is limited only by his daily spell points. 
A Dread Knight simply knows his spells; they are ingrained in his mind, though he must get a good night's sleep each day to regain all his spent spell points.
The Difficulty Class for saving throws against Dread Knight spells is 10 + one-half the number of spell points spent on the spell (round up) + the Dread Knight's Charisma modifier. 

Spells learned via the Dread Knight class are arcane spells.

\paragraph{Maximum Spell Level Known:} A Dread Knight begins play with the ability to learn 1st-level spells. 
As he attains higher levels, a Dread Knight may gain the ability to master more complex spells, as shown on the \nameref{tab:DreadKnight} table.
To learn or cast a spell, a Dread Knight must have a Charisma score of at least 10 + the spell's level.

\paragraph[Dread Knight's Curse]{Dread Knight's Curse: (Su)}
\label{sec:DreadKnightsCurse}
By expending your magical focus as a swift action, you can call upon dark powers to target one or more creatures within 30' with a curse.
The subjects must succeed on a Will save (DC 10 + $1/2$ your character level + your Charisma modifier) or take a -2 penalty on all attack rolls, saving throws, ability checks and skill checks for one hour.
\footnote{Several of the Dread Knight's class features and available spells refer to ``Cursed'' targets. A Cursed target is any creature affected by the Dread Knight's Curse ability, or any creature under the effect of a spell with the [\nameref{sec:Curses}] descriptor.}
% any creature affected by one of the following spells: \nameref{Spell:Bane}, \nameref{Spell:BestowCurse},\nameref{Spell:Blindness}, \nameref{Spell:CrushingOnsetOfAge}, \nameref{Spell:CursedBlade}, \nameref{Spell:DenialOfDeathsEmbrace}, \nameref{Spell:Fear}, \nameref{Spell:InexorableOnsetOfDeath} and \nameref{Spell:Pox}.}

A \nameref{Spell:RemoveCurse} spell can prematurely end this curse.

\paragraph{Dark Grace: (Su)} A Dread Knight gains a bonus on all saving throws equal to his Charisma modifier or his Dread Knight level, whichever is lower.
This is a Supernatural ability that functions continuously, requiring no activation.

\paragraph{Dark Power:}
At 2nd level, the dark heritage of a Dread Knight manifests itself in a gift of new powers. He gains an additional power at Dread Knight levels 5th, 8th, 11th, 17th, and 20th. Unless otherwise noted, a power can only be selected once. Some powers have specific prerequisites.

\subparagraph{Additional Feat:}
You gain a bonus feat from the list of feats noted as Fighter bonus feats. You may also select the \nameref{Feat:Familiar} feat. You must meet the feat's prerequisites, if any.
This power may be selected more than once.

\subparagraph{Aura of Unluck (Su):} 
By expending his magical focus as a free action, a Dread Knight can create a tangible aura of bad luck to foil his enemies. 

Any melee or ranged attack made against the Dread Knight while this aura of unluck is active has a 20\% miss chance (as if the Dread Knight were concealed). The aura lasts for a number of rounds equal to 3 + the Dread Knight's Charisma bonus (if any).

\subparagraph{Bastard's Strike (Su):}
You can automatically confirm all critical threats you roll against Cursed creatures.

This is a supernatural ability that requires no special activation.

\subparagraph{Bestow Curse (Sp):}
You can use \nameref{Spell:BestowCurse} at will as a standard action. Caster level equals your number of Hit Dice.

You must be a 5th-level Dread Knight to select this power.
\subparagraph{Bleeding Edge (Su):}
You can inflict a wound cursed to bleed incessantly. 

Whenever you make a successful weapon attack (including natural attacks and ranged attacks, but not spells, spell-like abilities, or supernatural abilities) against a Cursed creature, it must make a Fortitude save (DC 10 + $1/2$ your HD + your Charisma modifier). On a failed save, the target takes one point of Constitution damage from bleeding.

If it starts bleeding, the save must be repeated once per round thereafter (with the appropriate penalties on failure) until the target receives magical healing that restores hit point damage or ceases to be Cursed.

Striking a creature that is already bleeding immediately enforces a new save.

\subparagraph{Debilitating Curse (Su):}
The penalties imposed by your Dread Knight's Curse increase to -8.

You must be a 17th-level Dread Knight and have the \nameref{sec:PowerfulCurse} power in order to select this power.

\subparagraph{Fiendish Tongue (Ex):} You gain a +4 profane bonus on Bluff, Diplomacy and Intimidate checks. Against evil outsiders, these bonuses are doubled.

You also gain knowledge of the languages Abyssal and Infernal.

\subparagraph{Lasting Doom (Su):}
As a full-round action, you can render a Dread Knight's Curse already in place on a target permanent, preventing it from running out when its usual duration is up.

At your option, the duration of the curse can be changed to something other than ``Permanent'' by using this ability, such as a year and a day, or a hundred years.

Also, you may set a certain condition that must be met to make the curse expire. This condition may be almost anything you can imagine, but is typically something extraordinarily difficult to bring about, such as slaying a particular great wyrm, scaling the world's tallest mountain, or lifting the king's castle above the clouds.

\subparagraph{Unnatural Resilience (Ex):}  
Your unearthly connections ward you from attacks against your body and soul. 

If you make a successful Will or Fortitude save against an effect that normally has a reduced effect on a successful save, you suffer no ill effects. This includes all spells that have saving throw entries of Will half, Will partial, Fortitude half or Fortitude partial.

This extraordinary ability functions continuously, requiring no special activation.

\subparagraph[Powerful Curse]{Powerful Curse (Su):}
\label{sec:PowerfulCurse}
The penalties imposed by your Dread Knight's Curse increase to -4 (from -2).

You must be an 8th-level Dread Knight to select this power.
% \subparagraph{No Survivors (Ex):}
% Whenever you reduce a foe to negative hit points, you can choose to reduce him to -10 hit points, killing him instantly.

\subsubsection{Ex-Dread Knights:}
A Dread Knight who changes to a good alignment loses his ability to cast Dread Knight spells, the Dark Grace class feature, and all supernatural Dark Powers.
The spellcasting and other abilities remain dormant until he atones (see the \nameref{Spell:Atonement} spell description).


% \subsubsection{Cerebral Disturbance}
% Touch attack, no-save slow.
% \subsubsection{Darkbolt}
% Single-target damage + stun.
% \subsubsection{Rotting Curse}
% Con damage per hour.