\subsection{Ogre Mage}
\label{sec:OgreMage}
The ogre mage is a more intelligent and dangerous variety of its mundane cousin.

An ogre mage stands about 10 feet tall and weighs up to 700 pounds. Its skin varies in color from light green to light blue, and its hair is black or very dark brown. Ogre mages favor loose, comfortable clothing and lightweight armor.

Ogre mages speak Giant and Common.
\subsubsection{Combat}
Ogre mages rely on their spells to see them through, resorting to physical combat only when necessary.
When faced with obviously superior forces, they prefer to retreat using gaseous form rather than fight a losing battle.
\begin{table*}
\label{tab:OgreMage}
\caption{Ogre Mage}
\makebox[\textwidth]{%\resizebox{\textwidth}{!}{
\begin{tabular}{|p{0.3\textwidth}|p{0.7\textwidth}|}
\hline
\textbf{Size/Type:}		&Large Giant\\
\textbf{Hit Dice}		&8d8+24 (60 HP)\\
\textbf{Initiative}		&+4\\
\textbf{Speed}			&40 ft. (8 squares), can cast \nameref{Spell:Fly}\\
\textbf{Armor Class:}		&18 (-1 size, +5 natural, +4 chain shirt), touch 9, flat-footed 18, can cast \nameref{Spell:Shield}\\
\textbf{BAB/Grapple:}		&+6/+15\\
\textbf{Attack:}		&Greatsword +10 melee (3d6+7/19-20) or longbow +5 ranged (2d6/$\times$3)\\
\textbf{Full Attack:}		&Greatsword +10/+5 melee (3d6+7/19-20) or longbow +5/+0 ranged (2d6/$\times$3)\\
\textbf{Space/Reach:}		&10 ft./10 ft.\\
\textbf{Special Attacks:}	&Spells\\
\textbf{Special Qualities:}	&Darkvision 60', low-light vision, regeneration 5, spell resistance 20\\
\textbf{Saves:}			&Fort +9, Ref +2, Will +4\\
\textbf{Abilities:}		&Str 21, Dex 10, Con 17, Int 14, Wis 14, Cha 17\\
\textbf{Skills:}		&Concentration +14, Listen +13, \nameref{sec:Spellcraft} +13, Spot +13\\
\textbf{Feats:}			&\nameref{Feat:ExpandedKnowledge}: \nameref{Spell:Invisibility}, Improved Initiative, \nameref{Feat:SilentSpell}\\
\textbf{Environment:}		&Cold hills\\
\textbf{Organization:}		&Solitary, pair, or troupe (1-2 plus 2-4 ogres)\\
\textbf{Challenge Rating}	&8\\
\textbf{Alignment:}		&Usually lawful evil\\
\textbf{Treasure:}		&Double standard\\
\textbf{Advancement:}		&By character class\\
\textbf{Level Adjustment:}	&+4\\
\hline \end{tabular}}%}
\end{table*}
\paragraph{Change Shape (Su):}
An ogre mage can assume the form of any Small, Medium, or Large humanoid or giant.
\paragraph{Regeneration (Ex):}
Fire and acid deal normal damage to an ogre mage.

An ogre mage that loses a limb or body part can reattach it by holding the severed member to the stump. Reattachment takes 1 minute. If the head or some other vital organ is severed, it must be reattached within 10 minutes or the creature dies. An ogre mage cannot regrow lost body parts.
\paragraph{Spells:} Ogre Mages cast spells as 9th-level \nameref{sec:Sorcerer}s.
They typically know the spells \nameref{Spell:ArcaneEye}, \nameref{Spell:Charm}, \nameref{Spell:ConeOfCold}, \nameref{Spell:Darkness}, \nameref{Spell:FalseLife}, \nameref{Spell:Fly}, \nameref{Spell:GaseousForm}, \nameref{Spell:HallucinatoryTerrain}, \nameref{Spell:Invisibility}, \nameref{Spell:Shield}, and \nameref{Spell:Sleep}.

They have 104 spell points (91 for casting as a 9th-level Sorcerer, 13 for their high Charisma score).
\paragraph{Ogre Mages As Characters:}
Ogre mage characters possess the following racial traits.

\begin{itemize}
 \item +10 Strength, +6 Constitution, +4 Intelligence, +4 Wisdom, +6 Charisma.
 \item Large size. -1 penalty to Armor Class, -1 penalty on attack rolls, -4 penalty on Hide checks, +4 bonus on grapple checks, lifting and carrying limits double those of Medium characters.
 \item Space/Reach: 10 feet/10 feet.
 \item An ogre mage's base land speed is 40 feet.
 \item Darkvision: Ogre mages can see in the dark up to 60 feet.
 \item Racial Hit Dice: An ogre mage begins with eight levels of giant, which provide 8d8 Hit Dice, a base attack bonus of +6, and base saving throw bonuses of Fort +6, Ref +2, and Will +2.
 \item Racial Skills: An ogre mage's giant levels give it skill points equal to 11 $\times$ (2 + Int modifier [minimum 1]). Its class skills are Concentration, Listen, Spellcraft, and Spot.
 \item Racial Feats: An ogre mage's giant levels give it three feats.
 \item +5 natural armor bonus.
 \item Spellcasting: Ogre mages cast spells as 9th-level Sorcerers.
 \item Special Qualities (see above): Regeneration 5, spell resistance equal to 12 + number of hit dice the Ogre Mage has (including both racial HD and class levels).
 \item Automatic Languages: Common, Giant. Bonus Languages: Dwarven, Goblin, Infernal, Orc.
 \item Favored Class: Sorcerer.
 \item Level adjustment +4.
\end{itemize}