\subsection[Sorcerer]{The Sorcerer}
\label{sec:Sorcerer}
\begin{quote}
\emph{It's quite simple, really. I say magic words, and magic happens.}
- Nora, human Sorceress
\end{quote}
A Sorcerer is an user of arcane magic that is born, not made.
\paragraph{Alignment:} Any
\paragraph{Hit Die:} d4
\paragraph{Class skills:}
The sorcerer's class skills (and the key ability for each skill) are 
Bluff (Cha), Concentration (Con), Craft (Int), Diplomacy (Cha), Disguise (Cha), Gather Information (Cha), Knowledge (arcana) (Int), Knowledge (the planes) (Int), Profession (Wis), Sense Motive (Wis), Speak Language (N/A) and Spellcraft (Int). 

\paragraph{Skill Points at 1st Level:} (4 + Int modifier) $\times$ 4.
\paragraph{Skill Points at each additional Level:} 4 + Int modifier.
\begin{table*}
\centering
\caption{The Sorcerer}
\label{tab:Sorcerer}
\makebox[\textwidth]{
\begin{tabular}{llccclccc}
\toprule
	&	&	&	&	&				&\multicolumn{3}{c}{Spellcasting}\\ \cmidrule(r){7-9}
Level	&BAB	&Fort 	&Ref 	&Will 	&Special			&SP/day	&Known&Max level\\
\midrule
1st	&+0	&+0	&+0	&+2	&Cantrips, Magical Intuition, 	&3	&2	&1st\\
	&	&	&	&	&Wild Magic +1			&	&	&\\
2nd	&+1	&+0	&+0	&+3	&-				&7	&3	&1st\\
3rd	&+1	&+1	&+1	&+3	&Wild Magic +2			&13	&4	&2nd\\
4th	&+2	&+1	&+1	&+4	&-				&21	&5	&2nd\\
5th	&+2	&+1	&+1	&+4	&Bonus feat			&31	&6	&3rd\\
6th	&+3	&+2	&+2	&+5	&-				&43	&7	&3rd\\
7th	&+3	&+2	&+2	&+5	&Wild Magic +3			&57	&8	&4th\\
8th	&+4	&+2	&+2	&+6	&-				&73	&9	&4th\\
9th	&+4	&+3	&+3	&+6	&-				&91	&10	&5th\\
10th	&+5	&+3	&+3	&+7	&Bonus feat			&111	&11	&5th\\
11th	&+5	&+3	&+3	&+7	&Wild Magic +4			&133	&12	&6th\\
12th	&+6/+1	&+4	&+4	&+8	&-				&157	&13	&6th\\
13th	&+6/+1	&+4	&+4	&+8	&-				&183	&14	&7th\\
14th	&+7/+2	&+4	&+4	&+9	&-				&211	&15	&7th\\
15th	&+7/+2	&+5	&+5	&+9	&Bonus feat, Wild Magic +5	&241	&16	&8th\\
16th	&+8/+3	&+5	&+5	&+10	&-				&273	&17	&8th\\
17th	&+8/+3	&+5	&+5	&+10	&-				&307	&18	&9th\\
18th	&+9/+4	&+6	&+6	&+11	&-				&343	&19	&9th\\
19th	&+9/+4	&+6	&+6	&+11	&Wild Magic +6			&381	&20	&9th\\
20th	&+10/+5	&+6	&+6	&+12	&Bonus feat			&421	&21	&9th\\
\bottomrule
\end{tabular}}
\end{table*}
\subsubsection{Class Features}
All the following are class features of the Sorcerer.

\paragraph{Weapon and Armor Proficiency:} Sorcerers are proficient with all simple weapons. 
They are not proficient with any type of armor or shield. 
Armor does not, however, interfere with the casting of spells.

\paragraph{Spell Points/Day:} 
A Sorcerer's ability to cast spells is limited by the spell points he has available. 
His base daily allotment of spell points is given on \nameref{tab:Sorcerer} table. 
In addition, he receives bonus spell points per day if he has a high Charisma score.
His race may also provide bonus spell points per day, as may certain feats and items.

\paragraph{Spells Known:} A Sorcerer begins play knowing two Sorcerer spells of your choice. 
Each time he achieves a new level, he unlocks the knowledge of new spells.
Choose the spells known from the full Sorcerer spell list.
(Exceptions: See the Magical Intuition class feature.
In addition, the feats Expanded Knowledge and Epic Expanded Knowledge 
do allow a Sorcerer to learn spells of other classes, 
including spells restricted to specialist Wizards.) 

A Sorcerer can cast any spell he knows that has a spell point cost equal to or lower than his caster level.
The number of times a Sorcerer can cast spells in a day is limited only by his daily spell points. 
A Sorcerer simply knows his spells; they are ingrained in his mind, 
though he must get a good night's sleep each day to regain all his spent spell points.
The Difficulty Class for saving throws against Sorcerer spells is 10 + one-half the number of spell points spent on the spell (round up) + the Sorcerer's Charisma modifier. 

Spells learned via the Sorcerer class are arcane spells.
\paragraph{Maximum Spell Level Known:} A Sorcerer begins play with the ability to learn 1st-level spells. 
As he attains higher levels, 
a Sorcerer may gain the ability to master more complex spells, as shown on \nameref{tab:Sorcerer} table.
To learn or cast a spell, a Sorcerer must have a Charisma score of at least 10 + the spell's level.

\paragraph{Bonus Feats:} 
A Sorcerer gains a bonus feat at 5th level, 10th level, 15th level, and 20th level. 
This feat must be a magical feat, a metamagic feat, or the Familiar feat.
These bonus feats are in addition to the feats that a character of any class gains every three levels. 

\paragraph[Cantrips]{Cantrips (Su):} 
A Sorcerer can use \nameref{sec:Cantrips} as a \nameref{sec:Wizard} can.

\paragraph{Magical Intuition:} 
A Sorcerer can select spells normally restricted to specialist Wizards as their spells known,
subject to the restriction that the number of specialist spells so selected may not exceed one-third of the Sorcerer's total number of spells known.

Example: A first level Sorcerer knows two spells. He could not select a spell restricted to specialist Wizards as one of those
two spells, since that would mean one-half of his spells consists of specialist Wizard spells.
However, he could select a specialist Wizard spell as his spell known when he reaches second level.
When he reaches 5th level (and thereby learns his 6th spell), he could learn a second specialist Wizard spell.

Spells known granted by the \nameref{Feat:ExpandedKnowledge} feat or from levels in other classes are not included - 
they do not count towards the limit of no more than one-third of the Sorcerer's spell repertoire being specialist Wizard spells,
and they do not count when determining the Sorcerer's number of spells known for this purpose.

This class feature is considered a part of the Sorcerer's Spells Known class feature. Sorcerers continue to benefit from it if their Spells Known are progressed via a prestige class.

\paragraph{Wild Magic:} A Sorcerer's intuitive understanding of magic allows him to make use of the universe's
own powerful magical eddies in ways that other spellcasters can't.
When casting a spell, a Sorcerer can choose to add +1 to the spell's save DC 
and gain a +1 bonus on the caster level check to overcome the subject's spell resistance.
(Spells that do not offer saving throws or spell resistance gain no benefit from Wild Magic.)

At 3rd level, a Sorcerer can choose to gain up to a +2 bonus on the spell's save DC and caster level check. 
At 7th level, he can gain a +3 bonus; at 11th level, a +4 bonus; at 15th level, a +5 bonus; and at 19th level, a +6 bonus.

Relinquishing control over a spell in this manner is dangerous, however.
For each +1 added to the spell's save DC and roll to overcome the subject's spell resistance, 
there is a cumulative 5\% chance of the Sorcerer suffering a magical backlash.
A Sorcerer hit by a magical backlash is \emph{staggered} for one round, and loses a number of spell points
equal to twice the bonus gained on the spell's save DC and caster level check.

For example, a 10th-level Sorcerer could choose to add +2 to the save DC and roll to overcome spell resistance of a
\nameref{Spell:Fireball} spell he is casting. He would then have a 10\% chance of suffering the magical backlash.
If the backlash strikes, he loses 4 spell points and is \emph{staggered} for one round.