\subsection{Thaumaturgist}
\begin{quote}
\emph{``This material world is but the tip of the iceberg that is the cosmos. The real battle lies far beyond.''}
- Xolon, human Thaumaturgist
\end{quote}
A Thaumaturgist is a spellcaster who is more adept than most at enlisting the aid of the outer planes.

\begin{table*}
\centering
\caption{The Thaumaturgist}
\label{tab:Thaumaturgist}
\makebox[\textwidth]{
\begin{tabular}{llcccll}
\toprule
Level	&BAB	&Fort 	&Ref 	&Will 	&Special		&Spellcasting\\
\midrule
1st	&+0	&+0	&+0	&+2	&Improved ally		&+1 level of existing class\\
2nd	&+1	&+0	&+0	&+3	&Augment Summoning	&+1 level of existing class\\
3rd	&+1	&+1	&+1	&+3	&Extended summoning	&+1 level of existing class\\
4th	&+2	&+1	&+1	&+4	&Contingent conjuration	&+1 level of existing class\\
5th	&+2	&+1	&+1	&+4	&Planar cohort		&+1 level of existing class\\
\bottomrule
\end{tabular}}
\end{table*}

\paragraph{Hit Die:} d4
\paragraph{Requirements:}
To qualify to become a Thaumaturgist, a character must fulfill all the following criteria.
\subparagraph{Skills:} Knowledge (the planes) 10 ranks 
\subparagraph{Spells:} Ability to cast \nameref{Spell:PlanarAlly}
\subparagraph{Special:} Must be a specialist Conjurer or be a Cleric with the Planes domain.
\paragraph{Class Skills}
The Thaumaturgist's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Knowledge (religion) (Int), Knowledge (the planes) (Int), Profession (Wis), Sense Motive (Wis), Speak Language (None), and Spellcraft (Int).
\paragraph{Skill Points at each level:} 4 + Int modifier.
\subsubsection{Class Features}
All the following are Class Features of the Thaumaturgist prestige class.

\paragraph{Weapon and Armor Proficiency:} Thaumaturgists gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} When a new Thaumaturgist level is gained, the character gains spell points per day, an increase in caster level, spells known and maximum available spell level as if he had also gained a level in whatever spellcasting class in which he could cast \nameref{Spell:PlanarAlly} before he added the prestige class level. 
He does not, however, gain any other benefit a character of that class would have gained. 
If a character had more than one spellcasting class in which he could cast Planar Ally before he became a Thaumaturgist, he must decide to which class he adds each level of Thaumaturgist for the purpose of determining what spellcasting class gains the benefit of the spellcasting advancement.

\paragraph{Improved Ally (Ex)}
When a Thaumaturgist casts a \nameref{Spell:PlanarAlly} spell, he, like any other caster, is entitled to making a Diplomacy check to convince the creature to aid him. If the Thaumaturgist's Diplomacy check adjusts the creature's attitude to helpful the spell's experience cost is retroactively reduced by half, as long as the task is one that is not against the creature's nature.

The Thaumaturgist's Improved ally class feature only works when the planar ally shares at least one aspect of alignment with the Thaumaturgist.

A Thaumaturgist can have only one such ally at a time, but he may negotiate tasks from other planar allies normally.

\paragraph{Augment Summoning}
At 2nd level, a Thaumaturgist gains the \nameref{Feat:AugmentSummoning} feat as a bonus feat.

\paragraph{Extended Summoning (Ex)}
At 3rd level and higher, all spells from the summoning subschool that the Thaumaturgist casts have their durations doubled, as if the \nameref{Feat:ExtendSpell} feat had been applied to them. 
The spell point cost of the summoning spells don't change and the Thaumaturgist need not expend his magical focus, however. 
This ability stacks with the effect of the Extend Spell feat (for a total duration of three times its normal duration), which does cost additional spell points.

\paragraph{Contingent Conjuration (Sp)}
Once per day, a 4th-level Thaumaturgist can use a special form of the \nameref{Spell:Contingency} spell as a spell-like ability. However, the Thaumaturgist may only cast the Contingent Conjuration spell upon himself, and he must select a Conjuration (Calling) or a Conjuration (Summoning) spell as the companion spell.

If the Thaumaturgist has the \nameref{Spell:Contingency} spell as a spell known, he can use it without interfering with his Contingent Conjuration spell-like ability.
\paragraph{Planar Cohort (Ex)}
A 5th-level Thaumaturgist can use the \nameref{Spell:PlanarAlly} spell to call a creature to act as his cohort. 

To call a planar cohort, the Thaumaturgist must cast the spell, paying the XP cost as if getting the creature to stay for one day per caster level. The improved ally class feature can't be used to reduce or eliminate this cost. 
The Thaumaturgist can then attempt to use the Diplomacy skill to persuade the creature to stay permanently. 
If it agrees, the \nameref{Spell:PlanarAlly} spell immediately ends, but the creature persists, and begins acting as the Thaumaturgist's cohort.
The planar cohort can't have more Hit Dice than the Thaumaturgist has, and must have an ECL no higher than the Thaumaturgist's character level -2.
The creature serves loyally and well as long as the Thaumaturgist continues to advance a cause important to the creature.

A Thaumaturgist can have only one planar cohort at a time, but he can continue to make agreements with other called creatures normally. 
A planar cohort replaces a Thaumaturgist's existing cohort, if he has one by virtue of the Leadership feat.