\subsection{Where's my favorite item?}
\label{sec:MissingItems}
To deal with the changes in the spell system (and for general ease of use), the item categories have been shuffled around.
\begin{itemize}
 \item \textbf{Magic Arms and Armor} work mostly as before.
 \item \textbf{Potions and Oils} have been folded into a new category of items called \emph{Matrices}, which also includes all single-use spell completion items.
 \item \textbf{Rings} have been individually updated as appropriate. The Rings of Wizardry have been removed due to incompatibility reasons.
 \item \textbf{Rods} are mostly unchanged. However, metamagic rods will not be implemented, as they are a form of free metamagic. The Rod of Lordly Might and Rod of Thunder and Lightning have not been updated at this point, due to being supremely useless anyway.
 \item \textbf{Scrolls} now serve as a way for spellcasters to increase their repertoire of spells known, rather than being one-use spell completion items.
 \item \textbf{Staffs} no longer exist in their prior form. However, see Spellstaffs.
 \item \textbf{Wondrous Items} have received individual conversions. Those that directly emulate radically changed spells have been rewritten (or will be). In addition, the following items have been removed:
 \begin{itemize}
  \item Blessed Book. Does not exist due to Wizards no longer using spellbooks.
  \item Candle of Invocation. Does not exist. Caster level increases such as those granted by the Candle of Invocation should not exist under this system.
  \item Ioun Stones. As normal, but Orange Prism Ioun Stone do not exist. Caster level increases such as those granted by the Orange Prism should not exist under this system.
  \item Prayer Beads. As normal, but Bead of Karma does not exist. Caster level increases such as those granted by the Bead of Karma should not exist under this system.
 \end{itemize}
\end{itemize}