%\subsection{Arcane Trickster}
\subsection{Assassin}
\begin{quote}
\emph{I am quite aware that the work I do isn't pretty. Take your moral preachings elsewhere.}
- Forbes, human Assassin
\end{quote}
An Assassin is a contract killer who uses stealth, spellcasting, and other supernatural abilities to make sure his victims die and stay dead.
\paragraph{Hit Die:} d6
\paragraph{Requirements:}
To qualify to become an Assassin, a character must fulfill all the following criteria.
\subparagraph{Alignment:} Any nongood.
\subparagraph{Skills:} Disguise 4 ranks, Hide 8 ranks, Move Silently 8 ranks.
% \item \textbf{Special:} The character must kill someone for no other reason than to join the Assassins.
\paragraph{Class Skills}
The Assassin's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Open Lock (Dex), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Swim (Str), Tumble (Dex), Use Magic Device (Cha), and Use Rope (Dex).
\paragraph{Skill Points at each level:} 4 + Int modifier.
\begin{table*}
\centering
\caption{The Assassin}
\label{tab:Assassin}
\makebox[\textwidth]{
\begin{tabular}{|l|c|c|c|c|l|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Level}}&\multirow{2}{*}{\textbf{BAB}}&\textbf{Fort}&\textbf{Ref}&\textbf{Will}&\multirow{2}{*}{\textbf{Special}}&\multirow{2}{*}{\textbf{SP/day}}&\textbf{Spells}&\textbf{Max}\\
&&\textbf{save}&\textbf{save}&\textbf{save}&&&\textbf{known}&\textbf{level}\\
\hline
\multirow{2}{*}{1st}	&\multirow{2}{*}{+0}	&\multirow{2}{*}{+0}	&\multirow{2}{*}{+2}	&\multirow{2}{*}{+0}	&Sneak attack +1d6, death 			&\multirow{2}{*}{1}	&\multirow{2}{*}{1}	&\multirow{2}{*}{1st}\\
	&	&	&	&	&attack, poison use				&	&	&\\
2nd	&+1	&+0	&+3	&+0	&Poison mastery					&3	&2	&1st\\
3rd	&+2	&+1	&+3	&+1	&Sneak attack +2d6				&6	&3	&2nd\\
4th	&+3	&+1	&+4	&+1	&Sure killer					&10	&4	&2nd\\
\multirow{2}{*}{5th}	&\multirow{2}{*}{+3}	&\multirow{2}{*}{+1}	&\multirow{2}{*}{+4}	&\multirow{2}{*}{+1}	&Improved uncanny dodge, 			&\multirow{2}{*}{15}	&\multirow{2}{*}{5}	&\multirow{2}{*}{3rd}\\
	&	&	&	&	&sneak attack +3d6				&	&	&\\
6th	&+4	&+2	&+5	&+2	&Venom immunity					&23	&6	&3rd\\
7th	&+5	&+2	&+5	&+2	&Sneak attack +4d6				&31	&7	&3rd\\
8th	&+6	&+2	&+6	&+2	&Hide in plain sight				&43	&8	&4th\\
9th	&+6	&+3	&+6	&+3	&Sneak attack +5d6				&55	&9	&4th\\
10th	&+7	&+3	&+7	&+3	&True death					&71	&10	&4th\\
\hline
\end{tabular}
}
\normalsize
\end{table*}
\subsubsection{Class Features}
All the following are Class Features of the Assassin prestige class.

\paragraph{Weapon and Armor Proficiency:}
Assassins are proficient with the crossbow (hand, light, or heavy), dagger (any type), dart, rapier, sap, shortbow (normal and composite), and short sword. 
Assassins are proficient with light armor but not with shields.

\paragraph{Spell Points/Day:} 
An Assassin's ability to cast spells is limited by the spell points he has available. 
His base daily allotment of spell points is given on \nameref{tab:Assassin} table. 
In addition, he receives bonus spell points per day if he has a high Intelligence score.
His race may also provide bonus spell points per day, as may certain feats and items.

\paragraph{Spells Known:} An Assassin begins play knowing an Assassin spell of your choice. 
Each time he achieves a new level, he unlocks the knowledge of new spells.
Choose the spells known from the full Assassin spell list.
(Exception: The feats Expanded Knowledge and Epic Expanded Knowledge 
do allow an Assassin to learn spells of other classes, 
including spells restricted to specialist Wizards.) 

An Assassin can cast any spell he knows that has a spell point cost equal to or lower than his caster level.
The number of times an Assassin can cast spells in a day is limited only by his daily spell points. 
An Assassin simply knows his spells; they are ingrained in his mind, 
though he must get a good night's sleep each day to regain all his spent spell points.
The Difficulty Class for saving throws against Assassin spells is 
10 + one-half the number of spell points spent on the spell (round up) + the Assassin's Intelligence modifier. 

Spells learned via the Assassin class are arcane spells.
\paragraph{Maximum Spell Level Known:} An Assassin begins play with the ability to learn 1st-level spells. 
As he attains higher levels, 
an Assassin may gain the ability to master more complex spells, as shown on \nameref{tab:Assassin} table.
To learn or cast a spell, an Assassin must have a Intelligence score of at least 10 + the spell's level.

\paragraph{Sneak Attack:}
This is exactly like the rogue ability of the same name. 
The extra damage dealt increases by +1d6 every other level (1st, 3rd, 5th, 7th, and 9th). 
If an Assassin gets a sneak attack bonus from another source the bonuses on damage stack.

\paragraph{Death Attack (Ex):}
If an Assassin studies his victim for 3 rounds and then makes a sneak attack with a weapon that successfully deals damage, 
the sneak attack has the additional effect of possibly either \emph{paralyzing} or killing the target (Assassin's choice). 
While studying the victim, the Assassin can undertake other actions so long as his attention stays focused on the target 
and the target does not detect the Assassin or recognize the Assassin as an enemy. 
If the victim of such an attack fails a Fortitude save (DC 10 + the Assassin's class level + the Assassin's Int modifier) 
against the kill effect, she dies. If the saving throw fails against the \emph{paralysis} effect, 
the victim is rendered \emph{helpless} and unable to act for 1d6 rounds plus 1 round per level of the Assassin. 
If the victim's saving throw succeeds, the attack is just a normal sneak attack. 
Once the Assassin has completed the 3 rounds of study, he must make the death attack within the next 3 rounds.

If a death attack is attempted and fails (the victim makes her save) 
or if the Assassin does not launch the attack within 3 rounds of completing the study, 
3 new rounds of study are required before he can attempt another death attack.

At the Assassin's option, he may expend his magical focus when he makes the death attack 
in order to make the attack count as a spell with the [death] descriptor for the purposes of spell interactions.
This makes it harder to raise the victim from the dead, but makes protections such as \nameref{Spell:DeathWard} effective against it.
\paragraph{Poison Use (Ex):}
Assassins are trained in the use of poison and never risk accidentally poisoning themselves when applying poison to a weapon or using a poisoned weapon.

\paragraph{Poison Mastery (Su):}
Starting at 2nd level, an Assassin can expend his magical focus when delivering poison in order to increase the poison's save DC by a number equal to $1/2$ his Assassin level.
The focus must be expended as part of the action that delivers the poison, for example when attacking with a poisoned weapon (but not when applying poison to the weapon),
throwing a vial of poisonous gas, or poisoning a drink.
\paragraph{Uncanny Dodge (Ex):}
Starting at 2nd level, an Assassin retains his Dexterity bonus to AC (if any) regardless of being caught \emph{flat-footed} or struck by an \emph{invisible} attacker. 
(He still loses any Dexterity bonus to AC if immobilized.)

If a character gains uncanny dodge from a second class the character automatically gains improved uncanny dodge (see below) instead.

\paragraph{Sure Killer (Ex):}
At 4th level, an Assassin can perform a coup de grace as a standard action that does not provoke attacks of opportunity.
His coup de graces ignore any immunity the target may have to sneak attacks or effects that require a fortitude save.
\paragraph{Improved Uncanny Dodge (Ex):}
At 5th level, an Assassin can no longer be flanked, 
since he can react to opponents on opposite sides of him as easily as he can react to a single attacker. 
This defense denies rogues the ability to use flank attacks to sneak attack the Assassin. 
The exception to this defense is that a rogue at least four levels higher than the Assassin can flank him (and thus sneak attack him).

If a character gains uncanny dodge (see above) from a second class the character automatically gains improved uncanny dodge, 
and the levels from those classes stack to determine the minimum rogue level required to flank the character.

\paragraph{Venom Immunity (Ex):}
At 6th level, an Assassin gains immunity to all poisons.

\paragraph{Hide in Plain Sight (Su):}
At 8th level, an Assassin can use the Hide skill even while being observed. 
As long as he is within 10 feet of some sort of shadow, an Assassin can hide himself from view in the open without having anything to actually hide behind. 
He cannot, however, hide in his own shadow.

\paragraph{True Death (Su):}
At 10th level, whenever an Assassin succeeds on a Death Attack, he may opt to disperse the subject's soul as part of making the attack.

Raising a creature from the dead whose soul has been dispersed requires casting a \nameref{Spell:Wish} or \nameref{Spell:Miracle} 
spell to retrieve the soul prior to casting the spell that should raise it.

\subsubsection{Assassin Spell list}
\paragraph{1st-Level Assassin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlignedProtection}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item \nameref{Spell:Blackfire}*: Fires only shed light for you.
\item \nameref{Spell:ControlFall}: Objects or creatures fall slowly.
\item \nameref{Spell:DetectPoison}: Detects poison or disease in one creature or small object.
\item \nameref{Spell:DisguiseSelf}: Changes your appearance.
\item \nameref{Spell:Fog}: Fog surrounds you.
\item \nameref{Spell:PassWithoutTrace}: One subject/level leaves no tracks.
\item \nameref{Spell:TrueStrike}: +20 on your next attack roll.
\item \nameref{Spell:Ventriloquism}: Makes sounds appear out of nowhere.
\item \nameref{Spell:Sleep}: Puts 4 HD of creatures into magical slumber.
\end{list}
\paragraph{2nd-Level Assassin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:AlterSelf}: Perform minor physical changes on yourself.
\item \nameref{Spell:AnimalsMovement}: Grants additional movement capabilities.
\item \nameref{Spell:Darkness}: 20-ft. radius of supernatural shadow.
\item \nameref{Spell:Darkvision}: See 30 ft. in total darkness.
\item \nameref{Spell:Invisibility}: Subject is invisible for 1 min./level or until it attacks.
\item \nameref{Spell:MaskAlignment}: Protects subject's alignment from being revealed via divinations.
\item \nameref{Spell:Silence}: Negates sound in 20-ft. radius.
\item \nameref{Spell:WombatsBoost}: Subject gains +4 to an ability score for 1 min./level.
\end{list}
\paragraph{3rd-Level Assassin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:Blindsense}*: Subject can notice things it cannot see.
\item \nameref{Spell:Clairvoyance}: See and hear a distant location.
\item \nameref{Spell:FalseLife}: Gain 1d10 temporary hp.
\item \nameref{Spell:GaseousForm}: Subject becomes insubstantial and can fly slowly.
\item \nameref{Spell:Locate}: Senses direction toward object (specific or type).
\item \nameref{Spell:Nondetection}: Masks object or creature against scrying.
\end{list}
\paragraph{4th-Level Assassin Spells}
\begin{list}{\labelitemi}{\leftmargin=1em}
\item \nameref{Spell:ArcaneEye}: Invisible floating eye moves 30 ft./round.
\item \nameref{Spell:DimensionalAnchor}: Bars extradimensional movement.
\item \nameref{Spell:DimensionDoor}: Teleports you short distance.
\item \nameref{Spell:FreedomOfMovement}: Subject moves normally despite impediments.
\item \nameref{Spell:Glibness}: You gain a large bonus on Bluff checks.
\end{list}
