\subsection{Hierophant}
\begin{quote}
\emph{``Do not blindly place your faith in the higher powers. Understand them.''}
- Avatar, elven Hierophant
\end{quote}
A Hierophant is a divine spellcaster who has begun to understand the bonds between himself and his power source on a more fundamental level than most.

\begin{table*}
\centering
\caption{The Hierophant}
\label{tab:Hierophant}
\makebox[\textwidth]{
\begin{tabular}{llcccll}
\toprule
Level	&BAB	&Fort 	&Ref 	&Will 	&Special		&Spellcasting\\
\midrule
1st	&+0	&+0	&+0	&+2	&Special Ability	&+1 level of existing class\\
2nd	&+1	&+0	&+0	&+3	&Special Ability	&+1 level of existing class\\
3rd	&+1	&+1	&+1	&+3	&Special Ability	&+1 level of existing class\\
4th	&+2	&+1	&+1	&+4	&Special Ability	&+1 level of existing class\\
5th	&+2	&+1	&+1	&+4	&Special Ability	&+1 level of existing class\\
\bottomrule
\end{tabular}}
\end{table*}
\paragraph{Hit Die:} d8
\paragraph{Requirements:}
To qualify to become a Hierophant, a character must fulfill all the following criteria.
\subparagraph{Skills:} Knowledge (religion) 15 ranks 
\subparagraph{Feats:} Any metamagic feat.
\subparagraph{Spells:} Ability to cast 7th-level divine spells
\paragraph{Class Skills}
The Hierophant's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Heal (Wis), Knowledge (arcana) (Int), Knowledge (religion) (Int), Profession (Wis), and Spellcraft (Int).
\paragraph{Skill Points at each level:} 4 + Int modifier.

\subsubsection{Class Features}
All the following are Class Features of the Hierophant prestige class.

\paragraph{Weapon and Armor Proficiency:} Hierophants gain no proficiency with any weapon or armor.

\paragraph{Spellcasting:} When a new Hierophant level is gained, the character gains spell points per day, an increase in caster level, spells known and maximum available spell level as if he had also gained a level in whatever divine spellcasting class in which he could cast 7th-level spells before he added the prestige class level. 
He does not, however, gain any other benefit a character of that class would have gained. 
If a character had more than one divine spellcasting class in which he could cast 7th-level spells before he became a Hierophant, he must decide to which class he adds each level of Hierophant for the purpose of determining what spellcasting class gains the benefit of the spellcasting advancement.

\paragraph{Special Ability:}
A Hierophant gains the opportunity to select a special ability from among those described below by permanently eliminating a specific number of Spell Points.
These spell points are subtracted from the final number of spell points he Hierophant would otherwise have.
Effectively, these spell points are spent on ``fueling'' the Special Ability.
%When a Special Ability refers to a Hierophant's ``caster level'', it means his highest caster level.

\subparagraph{Blast Infidel (Su):}
A Hierophant can use negative energy spells to their maximum effect on creatures with an alignment opposed to the Hierophant. (See the table below for a list of which alignments are opposed to each alignment.) 
Any spell with a description that involves inflicting or channeling negative energy cast on a creature of the opposed alignment works as if under the effects of a \nameref{Feat:MaximizeSpell} feat (without using additional spell points or requiring the expenditure of the Hierophant's magical focus).

\begin{tableonecolumn}
\caption{Blast Infidel}
\label{tab:BlastInfidel}
\begin{tabular}{p{2.4cm}p{4cm}}
\toprule
Hierophant Alignment&Opposed Alignment\\
\midrule
Lawful good&		Chaotic evil\\
Neutral good&		Neutral evil\\
Chaotic good&		Lawful evil\\
Lawful neutral&		Chaotic neutral\\
Neutral&		Lawful good, chaotic good, lawful evil, chaotic evil$^1$\\
Chaotic neutral&	Lawful neutral\\
Lawful evil&		Chaotic good\\
Neutral evil&		Neutral good\\
Chaotic evil&		Lawful good\\
\bottomrule
\end{tabular}
{\scriptsize
\begin{enumerate}
 \item A neutral Hierophant chooses one of these alignments to be the one that he opposes for the purposes of this special ability.
\end{enumerate}
}
\end{tableonecolumn}

Learning this Special Ability removes 11 spell points from the Hierophant's pool.

\subparagraph{Divine Reach (Su):}
The Hierophant can use spells with a range of touch on a target up to 30 feet away. 
In the case of a spell that would ordinarily require a touch attack, the Hierophant must make a ranged touch attack instead.
Divine reach can be selected a second time as a Special Ability (paying the cost again), in which case the range increases to 60 feet. 
Learning this Special Ability removes 13 spell points from the Hierophant's pool.

\subparagraph{Faith Healing (Su):}
A Hierophant can use healing spells to their maximum effect on creatures of the same alignment as the Hierophant (including the Hierophant himself). 
Any spell of the Healing subschool cast on such creatures works as if under the effects of a \nameref{Feat:MaximizeSpell} feat (without using additional spell points or requiring the expenditure of the Hierophant's magical focus).
Learning this Special Ability removes 11 spell points from the Hierophant's pool.

\subparagraph{Gift of the Divine (Su):}
Available only to Hierophants with the \nameref{Feat:TurnUndead} feat, this ability allows a Hierophant to share the feat with another willing creature.
The creature must be touched for the transfer to take place.
The recipient can then use the feat as if he had selected the feats as one of his feats known.
The recipient does not have to meet the feat's class level requirement, but he must have a non-evil alignment and be capable of obtaining a Magical Focus.
The recipient turns undead as a creature of the Hierophant's level, but uses his own Charisma modifier.
The transfer lasts anywhere from 24 hours to one week (chosen at the time of transfer). 
Once shared, the Hierophant cannot share his ability to Turn Undead with another creature until the previous use of this ability has expired.
Learning this Special Ability removes 5 spell points from the Hierophant's pool.

\subparagraph{Metamagic Feat:}
A Hierophant can choose a metamagic feat in place of one of the Special Abilities described here if desired.
Doing so removes 17 spell points from the Hierophant's pool.

\subparagraph{Power of Nature (Su):}
Available only to Hierophants with access to at least one of the domains of Air, Animal, Earth, Fire, Plant, and Water, this ability allows a Hierophant to temporarily transfer one or more of the granted abilities of the aforementioned domains to a willing creature. 
The creature must be touched for the transfer to take place.
The transfer lasts anywhere from 24 hours to one week (chosen at the time of transfer), and while the transfer is in effect, the Hierophant cannot use the transferred granted powers.
Spellcasting and spells known are not granted powers of the domains, and can thus not be transferred.
The recipient cannot use the granted powers to fulfil prerequisites.
All transferred powers use the Hierophant's level, but otherwise use the recipient's statistics (for example, the bonus given by the Driven Arrows granted power of the Air domain would use the Hierophant's Cleric level, but the recipient's Strength and Wisdom modifiers).
Some granted powers may not be of any use to a recipient, such as an Elemental Shape ability on a recipient without spellcasting.
Learning this Special Ability removes 5 spell points from the Hierophant's pool.

\subparagraph{Spell Power:}
This ability provides the Hierophant with a +1 inherent bonus to one of his mental ability scores. 
Spell Power can be selected more than once as a Special Ability (paying the cost each time). 
Each additional time it is selected, he gains a +1 inherent bonus to another mental ability score, or one of his existing inherent bonuses to a mental ability score increases by one.
However, an inherent bonus may not exceed +5 for a single ability score.
Learning this Special Ability removes 9 spell points from the Hierophant's pool.

\subparagraph{Spell-Like Ability (Sp):}
A Hierophant who selects this Special Ability can use one of his spells known as a spell-like ability twice per day.
The caster level for this spell-like ability is equal to the Hierophant's hit dice.
The activation of the spell-like ability requires the same action as casting the spell itself.
If this Special Ability is selected more than once, it can apply to the same spell chosen the first time (increasing the number of times per day it can be used) or to a different spell.
Learning this Special Ability removes a number of spell points equal to the minimum amount required to cast the spell in question from the Hierophant's pool.
