\subsection{Angel}
\label{sec:Angel}
Angels are a race of celestials, beings who live on the good-aligned Outer Planes.

Angels can be of any good alignment. Regardless of their alignment, angels never lie, cheat, or steal. They are impeccably honorable in all their dealings and often prove the most trustworthy and diplomatic of all the celestials.

All angels are blessed with comely looks, though their actual appearances vary widely.

Angels speak Celestial, Infernal, and Draconic, though they can speak with almost any creature because of their tongues ability. 
\subsubsection{Astral Deva}
An astral deva is about 7 $1/2$ feet tall and weighs about 250 pounds. 

An astral deva is not afraid to enter melee combat. It takes a fierce joy in bashing evil foes with its powerful mace, which it has invariably made more powerful by using its \nameref{Spell:MagicWeapon} spell. 

An astral deva's natural weapons, as well as any weapons it wields, are treated as good-aligned for the purpose of overcoming damage reduction. 
\begin{table*}
\label{tab:AstralDeva}
\caption{Astral Deva}
\makebox[\textwidth]{%\resizebox{\textwidth}{!}{
\begin{tabular}{p{0.3\textwidth}p{0.7\textwidth}}
\toprule
\textbf{Size/Type:}		&Medium Outsider (Angel, Extraplanar, Good)\\
\textbf{Hit Dice}		&12d8+48 (102 hp)\\
\textbf{Initiative}		&+8\\
\textbf{Speed}			&50 ft. (10 squares), fly 100 ft. (good)\\
\textbf{Armor Class:}		&29 (+4 Dex, +15 natural), touch 14, flat-footed 25\\
\textbf{BAB/Grapple:}		&+12/+18\\
\textbf{Attack:}		&Heavy mace +22 melee (1d8+12 plus stun, includes \nameref{Spell:MagicWeapon} augmented to provide a +4 bonus) or slam +18 melee (1d8+9)\\
\textbf{Full Attack:}		&Heavy mace +22/+17/+12 melee (1d8+12 plus stun, includes \nameref{Spell:MagicWeapon} augmented to provide a +4 bonus) or slam +18 melee (1d8+9)\\
\textbf{Space/Reach:}		&5 ft./5 ft.\\
\textbf{Special Attacks:}	&Spells, stun\\
\textbf{Special Qualities:}	&Change shape, damage reduction 10/evil, darkvision 60 ft., low-light vision, immunity to acid, cold, and petrification, protective aura, resistance to electricity 10 and fire 10, spell resistance 30, tongues, uncanny dodge\\
\textbf{Saves:}			&Fort +12 (+16 against poison), Ref +12, Will +12\\
\textbf{Abilities:}		&Str 22, Dex 18, Con 18, Int 18, Wis 18, Cha 20\\
\textbf{Skills:}		&Concentration +19, Craft or Knowledge (any three) +19, Diplomacy +22, Escape Artist +19, Hide +19, Intimidate +20, Listen +23, Move Silently +19, Sense Motive +19, Spot +23, Use Rope +4 (+6 with bindings)\\
\textbf{Feats:}			&\nameref{Feat:ExpandedKnowledge}: \nameref{Spell:FistOfTheDeity}, \nameref{Feat:ExpandedKnowledge}: \nameref{Spell:Invisibility}, Improved Initiative, \nameref{Feat:QuickenSpell}, Power Attack\\
\textbf{Environment:}		&Any good-aligned plane\\
\textbf{Organization:}		&Solitary, pair, or squad (3-5)\\
\textbf{Challenge Rating}	&14\\
\textbf{Treasure:}		&No coins; double goods; standard items\\
\textbf{Alignment:}		&Always good (any)\\
\textbf{Advancement:}		&By character class\\
\textbf{Level Adjustment:}	&+8\\
\bottomrule 
\end{tabular}}%}
\end{table*}
\paragraph{Spells:} Astral Devas cast spells as 17th-level \nameref{sec:Paladin}s. A typical astral deva might know the following spells:

% \nameref{Spell:Aid}, \nameref{Spell:DeathWard}, \nameref{Spell:DiscernAlignment}, \nameref{Spell:DispelAlignment}, \nameref{Spell:DispelMagic}, \nameref{Spell:DisruptingWeapon}, \nameref{Spell:FistOfTheDeity}, \nameref{Spell:Heal}, \nameref{Spell:Light}, \nameref{Spell:MagicWeapon}, \nameref{Spell:MarkOfJustice}, \nameref{Spell:PlaneShift}, \nameref{Spell:RemoveCurse}, \nameref{Spell:RemoveDisease}, \nameref{Spell:RemoveFear}, \nameref{Spell:TouchOfVitality}, \nameref{Spell:TrueSeeing}, and \nameref{Spell:ZoneOfTruth}.
1st - \nameref{Spell:DiscernAlignment}, \nameref{Spell:Light}, \nameref{Spell:MagicWeapon}, \nameref{Spell:RemoveFear}, \nameref{Spell:TouchOfVitality};
2nd - \nameref{Spell:Aid}, \nameref{Spell:ZoneOfTruth};
3rd - \nameref{Spell:DispelMagic} \nameref{Spell:RemoveDisease}, \nameref{Spell:RemoveCurse};
4th - \nameref{Spell:DeathWard}, \nameref{Spell:FistOfTheDeity}, \nameref{Spell:MarkOfJustice};
5th - \nameref{Spell:DispelAlignment}, \nameref{Spell:DisruptingWeapon}, \nameref{Spell:TrueSeeing};
6th - \nameref{Spell:Heal}, \nameref{Spell:PlaneShift};

They have 117 spell points when encountered (91 for casting as a 17th-level Paladin, 42 for their high Charisma score, 16 spent on casting \nameref{Spell:MagicWeapon} at the start of the day).
\paragraph{Change Shape (Su):}
An astral deva can assume the form of any Small or Medium humanoid.

\paragraph{Stun (Su):}
If an astral deva strikes an opponent twice in one round with its mace, that creature must succeed on a DC 22 Fortitude save or be stunned for 1d6 rounds. The save DC is Strength-based. The \nameref{Spell:MaceOfTheAstralDeva} spell is a mortal's imitation of this ability - Astral Devas gain no further benefit even if wielding a weapon under the influence of this spell.
\paragraph{Uncanny Dodge (Ex)}
An astral deva retains its Dexterity bonus to AC when flat-footed, and it cannot be flanked except by a rogue of at least 16th level. It can flank characters with the uncanny dodge ability as if it were a 12th-level rogue. 

\subsubsection{Planetar}
A planetar is nearly 9 feet tall and weighs about 500 pounds. Despite their vast array of magical powers, planetars are likely to wade into melee with their magically enhanced greatswords. They particularly enjoy fighting fiends.

A planetar's natural weapons, as well as any weapons it wields, are treated as good-aligned for the purpose of overcoming damage reduction.
\begin{table*}
\label{tab:Planetar}
\caption{Planetar}
\makebox[\textwidth]{%\resizebox{\textwidth}{!}{
\begin{tabular}{p{0.3\textwidth}p{0.7\textwidth}}
\toprule
\textbf{Size/Type:}		&Large Outsider (Angel, Extraplanar, Good)\\
\textbf{Hit Dice}		&14d8+70 (133 hp)\\
\textbf{Initiative}		&+8\\
\textbf{Speed}			&30 ft. (6 squares), fly 90 ft. (good)\\
\textbf{Armor Class:}		&36 (-1 size, +4 Dex, +19 natural, \nameref{Spell:MagicVestment} augmented to provide a +4 bonus), touch 13, flat-footed 28\\
\textbf{BAB/Grapple:}		&+14/+25\\
\textbf{Attack:}		&Greatsword +24 melee (3d6+14/19-20, includes \nameref{Spell:MagicWeapon} augmented to provide a +4 bonus) or slam +20 melee (2d8+10)\\
\textbf{Full Attack:}		&Greatsword +24/+19/+14 melee (3d6+14/19-20, includes \nameref{Spell:MagicWeapon} augmented to provide a +4 bonus) or slam +20 melee (2d8+10)\\
\textbf{Space/Reach:}		&10 ft./10 ft.\\
\textbf{Special Attacks:}	&Spells\\
\textbf{Special Qualities:}	&Change shape, damage reduction 10/evil, darkvision 60 ft., low-light vision, immunity to acid, cold, and petrification, protective aura, regeneration 10, resistance to electricity 10 and fire 10, spell resistance 30, tongues\\
\textbf{Saves:}			&Fort +14 (+18 against poison), Ref +13, Will +15\\
\textbf{Abilities:}		&Str 25, Dex 19, Con 20, Int 22, Wis 23, Cha 22\\
\textbf{Skills:}		&Concentration +22, Craft or Knowledge (any four) +23, Diplomacy +25, Escape Artist +21, Hide +17, Intimidate +23, Listen +23, Move Silently +21, Sense Motive +23, Search +23, Spot +23, Use Rope +4 (+6 with bindings)\\
\textbf{Feats:}			&\nameref{Feat:ExpandedKnowledge}:\nameref{Spell:CureWounds},\nameref{Feat:ExpandedKnowledge}:\nameref{Spell:RaiseDead}, Improved Initiative, \nameref{Feat:QuickenSpell}, Power Attack\\
\textbf{Environment:}		&Any good-aligned plane\\
\textbf{Organization:}		&Solitary or pair\\
\textbf{Challenge Rating}	&16\\
\textbf{Treasure:}		&No coins; double goods; standard items\\
\textbf{Alignment:}		&Always good (any)\\
\textbf{Advancement:}		&15-21 HD (Large); 22-42 HD (Huge)\\
\textbf{Level Adjustment:}	&-\\
\bottomrule
\end{tabular}}
\end{table*}
\paragraph{Spell-like Abilities:}
At will: \nameref{Spell:DiscernAlignment}, \nameref{Spell:DispelMagic}, \nameref{Spell:Light}.

In addition, the following abilities are always active on the planetar's person, as the spells (caster level 17th): \nameref{Spell:SeeInvisibility}, and \nameref{Spell:TrueSeeing}. They can be dispelled, but the planetar can reactivate them as a free action.
\paragraph{Spells:} Planetars can cast divine spells as 17th-level clerics. A planetar selects his spells known from the domains of Air, Destruction, Good, Law, or War, but does not gain their granted powers. A typical Planetar might know the following spells:

1st - \nameref{Spell:AlignedProtection}, \nameref{Spell:Bless}, \nameref{Spell:CureWounds}, \nameref{Spell:DivineFavor}, \nameref{Spell:InflictWounds},\nameref{Spell:MagicWeapon}, \nameref{Spell:TouchOfVitality};
2nd - \nameref{Spell:Aid}, \nameref{Spell:Consecrate}, \nameref{Spell:MaskAlignment};
3rd - \nameref{Spell:Contagion}, \nameref{Spell:MagicVestment}, \nameref{Spell:WindWall};
4th - \nameref{Spell:FistOfTheDeity}, \nameref{Spell:FlameStrike};
5th - \nameref{Spell:DispelAlignment}, \nameref{Spell:MarkOfJustice}, \nameref{Spell:RaiseDead}, \nameref{Spell:RighteousMight}, \nameref{Spell:WarriorsImpetus};
6th - \nameref{Spell:Disintegrate}, \nameref{Spell:Harm};
7th - \nameref{Spell:PowerWord}, \nameref{Spell:WordOfGod};
8th - \nameref{Spell:AlignedAura}, \nameref{Spell:Whirlwind};
9th - \nameref{Spell:Implosion};

They have 250 spell points when encountered (231 for casting as a 17th-level Cleric, 51 for their high Wisdom score, 16 and 16 spent on casting \nameref{Spell:MagicWeapon} and \nameref{Spell:MagicVestment} at the start of the day).
\paragraph{Change Shape (Su):}
A planetar can assume the form of any Small or Medium humanoid.
\paragraph{Regeneration (Ex):} A planetar takes damage from evil-aligned weapons and from spells and effects with the evil descriptor.