\subsection{Nymph}
A Nymph is about the height and weight of a female elf.

Nymphs speak Sylvan and Common.

\begin{table*}
\label{tab:Nymph}
\caption{Nymph}
\makebox[\textwidth]{%\resizebox{\textwidth}{!}{
\begin{tabular}{p{0.3\textwidth}p{0.7\textwidth}}
\toprule
\textbf{Size/Type:}		&Medium Fey\\
\textbf{Hit Dice}		&6d6+6 (27 hp)\\
\textbf{Initiative}		&+3\\
\textbf{Speed}			&30 ft. (6 squares), swim 20 ft.\\
\textbf{Armor Class:}		&17 (+3 Dex, +4 deflection), touch 17, flat-footed 14\\
\textbf{BAB/Grapple:}		&+3/+3\\
\textbf{Attack:}		&Dagger +3 melee (1d4/19-20)\\
\textbf{Full Attack:}		&Dagger +3 melee (1d4/19-20)\\
\textbf{Space/Reach:}		&5 ft./5 ft.\\
\textbf{Special Attacks:}	&Blinding beauty, spells, spell-like abilities, stunning glance\\
\textbf{Special Qualities:}	&Damage reduction 10/cold iron, low-light vision, unearthly grace, wild empathy\\
\textbf{Saves:}			&Fort +7, Ref +12, Will +12\\
\textbf{Abilities:}		&Str 10, Dex 17, Con 12, Int 16, Wis 17, Cha 19\\
\textbf{Skills:}		&Concentration +10, Diplomacy +6, Escape Artist +12, Handle Animal +13, Heal +12, Hide +12, Listen +12, Move Silently +12, Ride +5, Sense Motive +12, Spot +12, Swim +8, Use Rope +3 (+5 with bindings)\\
\textbf{Feats:}			&\nameref{Feat:ExpandedKnowledge}:\nameref{Spell:CureWounds}, \nameref{Feat:ExtendSpell}, \nameref{Feat:SplitRay}\\
\textbf{Environment:}		&Temperate forests\\
\textbf{Organization:}		&Solitary\\
\textbf{Challenge Rating}	&7\\
\textbf{Treasure:}		&Standard\\
\textbf{Alignment:}		&Usually Chaotic Good\\
\textbf{Advancement:}		&7-12 HD (Medium)\\
\textbf{Level Adjustment:}	&+7\\
\bottomrule 
\end{tabular}}
\end{table*}

\subsubsection{Combat}
\paragraph{Blinding Beauty (Su):}
This ability affects all humanoids within 30 feet of a Nymph. 
Those who look directly at a Nymph must succeed on a DC 17 Fortitude save or be blinded permanently as though by the blindness spell. 
A Nymph can suppress or resume this ability as a free action.

The save DC is Charisma-based.

\paragraph{Spell-Like Abilities:}
1/day - \nameref{Spell:StepThroughEarth}. Caster level 7th.

\paragraph{Spells:}
Nymphs can cast divine spells as 7th-level Clerics.
A Nymph selects her spells known from the domains of Air, Plant, and Water, but does not gain their granted powers. A typical Nymph might know the following spells:

1st - \nameref{Spell:ConverseWithNature}, \nameref{Spell:TouchOfVitality}, \nameref{Spell:Entangle}, \nameref{Spell:Fog}, \nameref{Spell:Woodbolt};
2nd - \nameref{Spell:Barkskin}, \nameref{Spell:CommandNaturesAllies}, \nameref{Spell:FormPlant};
3rd - \nameref{Spell:CallLightning}, \nameref{Spell:SpikeGrowth}, \nameref{Spell:SummonWaterElemental};
4th - \nameref{Spell:RustingGrasp};

They have 53 spell points when encountered (43 for casting as a 7th-level Cleric, and 10 for their high Wisdom score).

\paragraph{Stunning Glance (Su):}
As a standard action, a wrathful Nymph can stun a creature within 30 feet with a look. The target creature must succeed on a DC 17 Fortitude save or be stunned for 2d4 rounds. The save DC is Charisma-based.

\paragraph{Unearthly Grace (Su):}
A Nymph adds her Charisma modifier as a bonus on all her saving throws, and as a deflection bonus to her Armor Class. (The statistics block already reflects these bonuses).

\paragraph{Wild Empathy (Ex):}
This power works like the \nameref{sec:WildEmpathy} ability, using the Nymph's number of HD as her Ranger level. A Nymph has a +6 racial bonus on the check.

\paragraph{Skills:}
A Nymph has a +8 racial bonus on any Swim check to perform some special action or avoid a hazard. She can always choose to take 10 on a Swim check, even if distracted or endangered. She can use the run action while swimming, provided she swims in a straight line.